### 2024-11-03 paper/paper.qmd
appendix - pollster methodology overview and evaluation

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}
## Pollster methodology overview and evaluation
The Quinnipiac University Poll conducts independent polling in swing states - to analyze their methodology, we look specifically into their October 2024 Pennsylvania polls.

Their target population is likely voters aged 18 and older in Pennsylvania. To reach this population, they use likely voters aged 18 and older with phone numbers (both landline and cell) as their sampling frame, i.e. the frame of possible subjects that they sample observations from. Quinnipiac University employed Random Digit Dialing (RDD) to generate their sample of 2,186 respondents. This dual-frame approach reflects modern communication patterns, with 1,644 cell phone and 542 landline completions. However, using phones as a sampling frame means they cannot reach voters without phone access, introducing potential coverage bias.

Their sampling approach uses stratification by Census division according to area code, meaning that they divide Pennsylvania into geographic regions before using RDD to sample within each region. This strategy ensures even geographic representation but adds complexity to the sampling process. For each selected number, they attempt contact at least three times before marking it as non-responsive. For landline calls, they ask to speak with the household member who has the next birthday, a simple but effective randomization technique. Afterwards, a series of screening questions confirm that the subject is indeed a likely voter, after which the subject's responses are then formally taken as part of the sample.

After collecting responses, Quinnipiac adjusts their data through post-stratification weighting. In this weighting, they compare their sample's demographic composition to known population benchmarks from the Census (like age, gender, education, and race distributions in Pennsylvania) and adjust the weight given to each response to match these benchmarks. For example, if their sample has too few young voters compared to Census data, responses from young voters would be weighted more heavily. While this helps correct for sampling imbalances, it can increase the variance in their estimates if the weights vary substantially.

The survey administration addresses measurement issues through its design. Live interviewers conduct all interviews, enabling question clarification and generating higher response rates compared to automated systems. However, live interviewers may introduce social desirability bias, where respondents might modify their answers to appear more socially acceptable. This becomes particularly relevant in political polling, where respondents might hesitate to express unpopular political views.

Several types of bias affect the poll's results. Self-selection bias occurs because certain types of people (typically those more politically engaged or with stronger views) are more likely to agree to participate in the survey. Non-response bias arises when people who respond differ systematically from those who don't - for instance, busier people might be less likely to answer calls, potentially underrepresenting certain occupational groups. Coverage bias means some groups (like those without phones) have no chance of being included in the sample.

Finally, the poll also faces common challenges in political polls such as this one - the five-day field period (October 24-28) may miss opinion changes close to election day, and while weighting adjustments help correct for demographic imbalances, they may increase variance in the estimates if some groups need to be weighted heavily to match population benchmarks, for example.

Overall, Quinnipiac's methodology represents a balanced approach to managing practical constraints and statistical rigor in modern political polling - while some common biases are still likely to skew the poll results off the true support levels for Harris, for example, the poll uses methods such as post-stratification weighting to tradeoff biases at the cost of model variance. Using live interviewers unavoidably introduces social desirability bias, however, and significantly increases poll costs per quota. Modifying the methodology to remove this aspect of the survey would potentially reduce bias and allow for larger samples to be taken, in turn opening up possibilities for cross-validation and the such, which then reduces the effect of increased model variance on the final results.
# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-11-03 scripts/03-clean_data.R
updated code

@@ -49,7 +49,8 @@ just_trump_high_quality <- current_polls_data |>
   mutate(
     state = if_else(is.na(state), "National", state),
     end_date = mdy(end_date)
-  )
+  ) |>
+  filter(end_date >= as.Date("2024-07-21"))
 
 # repeat for historical data
 biden_past_high_quality <- past_polls_data |>
@@ -123,7 +124,8 @@ just_trump_lower_quality <- current_polls_data |>
   mutate(
     state = if_else(is.na(state), "National", state),
     end_date = mdy(end_date)
-  )
+  ) |>
+  filter(end_date >= as.Date("2024-07-21"))
 
 just_harris_lower_quality <- just_harris_lower_quality %>%
   distinct(poll_id, pollster_id, state, end_date, sample_size, race_id,

### 2024-11-03 scripts/05-exploratory_data_analysis.R

@@ -16,6 +16,8 @@ library(caret)
 library(glmnet)
 library(nnet)
 library(lubridate)
+library(pROC)
+library(stringr)
 
 
 #### Read data ####
@@ -72,6 +74,16 @@ harris_2024_national_adj <- harris_2024_national %>%
   select(-Biden_bias) %>%
   drop_na(end_date, has_sponsor, pollscore, transparency_score, sample_size)
 
+# also mutate has_sponsor variable for non-adjusted datasets
+trump_2024_national <- trump_2024_national %>% mutate(
+  has_sponsor = if_else(is.na(sponsors), 0, 1)
+) %>%
+  drop_na(end_date, has_sponsor, pollscore, transparency_score, sample_size)
+
+harris_2024_national <- harris_2024_national %>% mutate(
+  has_sponsor = if_else(is.na(sponsors), 0, 1)
+) %>%
+  drop_na(end_date, has_sponsor, pollscore, transparency_score, sample_size)
 
 # model adjusted support percentage by time and control variables
 # first split training and testing dataset using an 80/20 split
@@ -136,7 +148,7 @@ ggplot(combined_data, aes(x = end_date, y = pct_adj, color = candidate_name)) +
   geom_point(alpha = 0.6) +
   # Regression lines
   geom_line(aes(y = fitted_date), size = 0.5) +
-  xlim(as.Date("2024-07-01"), as.Date("2024-10-25")) +
+  xlim(as.Date("2024-07-19"), as.Date("2024-10-25")) +
   # Assign specific colors
   scale_color_manual(values = 
       c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
@@ -197,7 +209,6 @@ combined_regional <- left_join(
 combined_regional <- combined_regional %>%
   mutate(across(everything(), ~ replace(.x, is.nan(.x), NA)))
 
-# Trump has data in 43 states, while Harris only has data in 33 states
 # Mutate expected winner column, determined by the confidence intervals
 # If confidence intervals are missing, compare average support levels instead
 combined_regional <- combined_regional %>% mutate(
@@ -319,20 +330,84 @@ state_evs <- tibble::tribble(
 combined_regional <- combined_regional %>%
   left_join(state_evs, by = "state")
 
-#################################################################
-# potential changes area
-prediction_harris <- data.frame(end_date = end_date_seq) %>%
+#### Logistic regression for national support ####
+
[…]

### 2024-11-03 scripts/00-simulate_data.R
updated simulation code

@@ -11,42 +11,65 @@
 
 #### Workspace setup ####
 library(tidyverse)
-set.seed(853)
-
+library(lubridate)
 
 #### Simulate data ####
-# State names
-states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
+set.seed(114514)
+
+# define the range of pollsters
+pollster_options <- c(
+  "Siena/NYT", 
+  "YouGov", 
+  "CES / YouGov", 
+  "Marquette Law School", 
+  "The Washington Post", 
+  "McCourtney Institute/YouGov"
 )
 
-# Political parties
-parties <- c("Labor", "Liberal", "Greens", "National", "Other")
+# Define US states
+us_states <- state.name
 
-# Create a dataset by randomly assigning states and parties to divisions
-analysis_data <- tibble(
-  division = paste("Division", 1:151),  # Add "Division" to make it a character
-  state = sample(
-    states,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.25, 0.25, 0.15, 0.1, 0.1, 0.1, 0.025, 0.025) # Rough state population distribution
+# Define number of rows
+n <- 300
+
+# For the state variable, have half of the values "National"
+n_national <- n / 2  # 50
+n_states <- n - n_national  # 50
+# Create a vector with 50 "National" and 50 random state names
+state_vector <- c(
+  rep("National", n_national),
+  sample(us_states, n_states, replace = TRUE)
+)
+# Shuffle the state_vector to randomize the order
+state_vector <- sample(state_vector, n, replace = FALSE)
+
+# Generate national simulated dataset
+simulated_data <- tibble(
+  # pollster randomly assigned from the pollsters with 3.0 numeric grade
+  pollster = sample(pollster_options, n, replace = TRUE),
+  # has_sponsor is either 0 or 1
+  has_sponsor = sample(0:1, n, replace = TRUE),
+  # pollscore between -1.1 and -1.5 to mimic the actual dataset
+  pollscore = round(runif(n, min = -1.5, max = -1.1), 1),
+  # transparency_score between 6.5 and 10.0 with 0.5 increments
+  # to mimic the actual dataset
+  transparency_score = sample(seq(6.5, 10.0, by = 0.5), n, replace = TRUE),
[…]

### 2024-11-03 scripts/01-test_simulated_data.R
updated tests for simulated data

@@ -13,77 +13,114 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(testthat)
+library(lubridate)
 
-analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
+simulated_data <- read_csv("data/00-simulated_data/simulated_polls.csv")
 
-# Test if the data was successfully loaded
-if (exists("analysis_data")) {
-  message("Test Passed: The dataset was successfully loaded.")
-} else {
-  stop("Test Failed: The dataset could not be loaded.")
-}
+# Define the test context
+context("Sanity Checks for Simulated Datasets")
+
+#### Data structure tests ####
+
+test_that("Simulated Dataset has correct structure", {
+  expect_true(is.data.frame(simulated_data))
+  expect_true(50 <= nrow(simulated_data))
+  expect_true(1000 >= nrow(simulated_data))
+  expect_equal(ncol(simulated_data), 8)
+})
+
+test_that("Simulated Dataset has all required columns with correct types", {
+  required_cols <- c("pollster", "has_sponsor", "pollscore", 
+                     "transparency_score", "sample_size", "end_date", "pct_support")
+  expect_true(all(required_cols %in% colnames(simulated_data)))
+  
+  # Check data types
+  expect_type(simulated_data$pollster, "character")
+  expect_type(simulated_data$has_sponsor, "double") 
+  expect_type(simulated_data$pollscore, "double") 
+  expect_type(simulated_data$transparency_score, "double")
+  expect_type(simulated_data$sample_size, "double")
+  expect_s3_class(simulated_data$end_date, "Date")
+  expect_type(simulated_data$pct_support, "double")  
+})
 
 
-#### Test data ####
+#### Value Ranges and Constraints ####
 
-# Check if the dataset has 151 rows
-if (nrow(analysis_data) == 151) {
-  message("Test Passed: The dataset has 151 rows.")
-} else {
-  stop("Test Failed: The dataset does not have 151 rows.")
-}
+test_that("pollster column contains only valid pollster names", {
+  valid_pollsters <- c(
+    "Siena/NYT", 
+    "YouGov", 
+    "CES / YouGov", 
+    "Marquette Law School", 
+    "The Washington Post", 
+    "McCourtney Institute/YouGov"
+  )
+  expect_true(all(simulated_data$pollster %in% valid_pollsters))
+})
 
-# Check if the dataset has 3 columns
-if (ncol(analysis_data) == 3) {
-  message("Test Passed: The dataset has 3 columns.")
-} else {
[…]

### 2024-11-03 paper/paper.qmd
Update paper.qmd

@@
 Modifying the methodology to remove this aspect of the survey would potentially reduce bias and allow for larger samples to be taken, in turn opening up possibilities for cross-validation and the such, which then reduces the effect of increased model variance on the final results.
+
+## Idealised methodology
+With a $100,000 budget, our approach focuses on producing accurate state-level estimates in key battleground states, which would then inform our national forecast.
+We prioritize Pennsylvania, Michigan, Wisconsin, Georgia, Arizona, and Nevada, allocating resources proportionally based on each state's electoral importance and expected margin of victory.
+
+Our sampling strategy employs both probability and non-probability methods.
+Probability sampling (60% of budget) means every member of our target population has a known, non-zero chance of being selected - this allows us to calculate proper margins of error and make statistical inferences about the population.
+For this, we use dual-frame random digit dialing (RDD) for phone surveys and address-based sampling (ABS) for mail-to-web recruitment.
+RDD involves generating random phone numbers within active area codes, while ABS uses the U.S.
+Postal Service's delivery database as a sampling frame.
+The ABS approach helps reach households without reliable phone access.
+We stratify our sample by geography, demographics, and previous voting patterns to ensure representation across key subgroups - meaning we divide the population into these subgroups and sample from each independently.
+
+For non-probability sampling (40% of budget), where respondents' selection probabilities are unknown and not everyone has a chance of being selected, we recruit through multiple online panel vendors and use targeted social media advertising to reach traditionally underrepresented groups.
+While this approach introduces potential selection bias because participants self-select into the sample, it helps reach younger voters who are less responsive to traditional survey methods.
+We implement quota sampling within these non-probability samples to match key demographic targets - for example, stopping collection from certain demographic groups once their quota is filled.
+
+Respondent recruitment uses multiple contact methods - mail, email, text, and phone - with attempts made at different times and days to maximize response rates.
+We offer a $10 gift card incentive for completed surveys and provide both English and Spanish language options.
+This mixed-mode contact strategy helps reduce non-response bias by providing multiple ways to participate.
+
+Data validation is crucial for maintaining quality.
+We cross-reference responses with voter files where available - meaning we check if respondents' self-reported registration status matches official records.
+We screen for duplicate responses using IP addresses and phone numbers, and implement attention checks within the survey (questions with known correct answers to ensure respondents are reading carefully).
+Speed checks identify rushed responses that might indicate low-quality data by flagging completions that fall below a minimum reasonable completion time, while consistency checks across related questions help identify potentially fraudulent responses by looking for logical contradictions in answers.
+
+Our weighting approach uses post-stratification to known population benchmarks - this means we adjust the weight given to each response so that our sample matches known population characteristics.
+For example, if our sample has 30% college graduates but the population has 40%, we would give more weight to responses from college graduates.
+We include demographics (age, race, education, gender), geographic location, past voting behavior, and party registration in our weighting scheme.
+We produce daily estimates using a 7-day rolling average, which helps smooth out daily fluctuations while remaining responsive to real changes in voter preferences.
+
+The survey instrument itself focuses on six key areas: screening questions to identify likely voters, voting intentions (including direct questions about Trump vs.
+Harris preferences), political preferences, demographics, issue priorities, and media consumption patterns.
+We've implemented this survey design in Google Forms, which can be found here: [Link to be added]
+
+This methodology balances statistical rigor with practical constraints, while acknowledging and attempting to address the key challenges in modern political polling: declining response rates, coverage bias, and the increasing difficulty of reaching a representative sample of likely voters.
+
+## Idealised survey
+The survey, made using Google Forms, is linked here:
+Note that the questions are identical for both the phone and online surveys bar q6.
+A copy of the survey that is identical to the one implemented in the Google Forms above is presented below:
+Thank you for participating in this survey about the 2024 U.S.
+Presidential Election.
+This survey is part of a research project at the University of Toronto studying voting intentions and political attitudes.
+
+Estimated completion time: 8-10 minutes
+
+Your responses will be kept confidential and used only for research purposes. You may skip any questions you prefer not to answer, though complete responses are most helpful for our research.
+
+For questions or concerns about this survey, please contact: andrew.goh@mail.utoronto.ca
+
+SCREENING SECTION:
+Q1. Are you 18 years of age or older?
+
+Yes
+No [END SURVEY]
+
+Q2. Are you a U.S. citizen?
+
+Yes
+No [END SURVEY]
+
+Q3. Are you registered to vote at your current address?
+
+Yes
+No
+Not sure
+[If No or Not sure: Do you plan to register before the November 2024 election?]
+
+VOTING INTENTION:
+Q4. How likely are you to vote in the 2024 presidential election?
+
+Definitely will vote
+Probably will vote
+Might or might not vote
+Probably will not vote
+Definitely will not vote
+
+Q5. If the 2024 presidential election were held today, and the candidates were Donald Trump (Republican) and Kamala Harris (Democrat), who would you vote for?
+
+Donald Trump
+Kamala Harris
+Another candidate (please specify)
+Would not vote
+Not sure
+
+ATTENTION CHECK:
+Q6. To ensure you're reading carefully, please select "Somewhat disagree" for this question: "I enjoy following political news."
+
+Strongly agree
+Somewhat agree
+Somewhat disagree
+Strongly disagree
+No opinion
+
+POLITICAL PREFERENCES:
+Q7. Generally speaking, do you consider yourself a:
+
+Republican
+Democrat
+Independent
+Something else (please specify)
+
+Q8. How would you rate the current state of the U.S. economy?
+
+Excellent
+Good
+Fair
+Poor
+Very poor
+
+ISSUE PRIORITIES:
+Q9. Which ONE of the following issues is most important to you when deciding how to vote?
+
+Economy and jobs
+Immigration
+Healthcare
+Climate change
+Crime and public safety
+Education
+National security
+Abortion rights
+Gun policy
+Something else (please specify)
+
+For each of the following issues, please indicate whether you think Donald Trump or Kamala Harris would do a better job handling it:
+
+Q10. Economy and jobs:
+
+Donald Trump would do better
+Kamala Harris would do better
+No difference
+Not sure
+
+Q11. Immigration:
+[Same options]
+Q12. National security:
+[Same options]
+Q13. Healthcare:
+[Same options]
+
+MEDIA CONSUMPTION:
+Q14. Where do you most often get your news about politics? (Select all that apply)
+
+Network TV news (ABC, CBS, NBC)
+Cable TV news (CNN, Fox News, MSNBC)
+Local TV news
+Radio
+Print newspapers
+News websites
+Social media
+Friends and family
+Other (please specify)
+
+Q15. How many hours per day do you typically spend following news about politics?
+
+Less than 1 hour
+1-2 hours
+2-4 hours
+More than 4 hours
+
+DEMOGRAPHICS:
+Q16. What is your age?
+
+18-24
+25-34
+35-44
+45-54
+55-64
+65 or older
+
+Q17. What is your gender?
+
+Male
+Female
+Non-binary/Other
+Prefer not to say
+
+Q18. What is your race/ethnicity? (Select all that apply)
+
+White
+Black or African American
+Hispanic or Latino
+Asian
+Native American
+Other (please specify)
+Prefer not to say
+
+Q19. What is the highest level of education you have completed?
+
+Less than high school
+High school graduate
+Some college
+Associate's degree
+Bachelor's degree
+Graduate degree
+Prefer not to say
+
+Q20. What was your total household income before taxes in 2023?
+
+Under $25,000
+$25,000-$49,999
+$50,000-$74,999
+$75,000-$99,999
+$100,000-$149,999
+$150,000 or more
+Prefer not to say
+
+CONSISTENCY CHECK:
+Q21. Looking ahead to November 2024, if Donald Trump is the Republican nominee and Kamala Harris is the Democratic nominee, how do you think you will vote?
+
+Donald Trump
+Kamala Harris
+Another candidate (please specify)
+Would not vote
+Not sure
+
+[END OF SURVEY]
+
+Thank you for completing this survey about the 2024 U.S. Presidential Election. Your responses will help us better understand voter preferences and political attitudes across the country.
+If you have any questions about this research or would like to be informed about the results, please contact andrew.goh@mail.utoronto.ca.
+Your time and participation is greatly appreciated.
 # Additional data details

### 2024-11-03 paper/paper.qmd
Update appendix - idealised methodology and survey
more minor updates to the appendix sections

@@
 Our sampling strategy employs both probability and non-probability methods.
-Probability sampling (60% of budget) means every member of our target population has a known, non-zero chance of being selected - this allows us to calculate proper margins of error and make statistical inferences about the population.
+Probability sampling (60% of budget, i.e.
+$60k) means every member of our target population has a known, non-zero chance of being selected - this allows us to calculate proper margins of error and make statistical inferences about the population.
 For this, we use dual-frame random digit dialing (RDD) for phone surveys and address-based sampling (ABS) for mail-to-web recruitment.
@@
 
-For non-probability sampling (40% of budget), where respondents' selection probabilities are unknown and not everyone has a chance of being selected, we recruit through multiple online panel vendors and use targeted social media advertising to reach traditionally underrepresented groups.
+For non-probability sampling (40% of budget, i.e.
+$40k), where respondents' selection probabilities are unknown and not everyone has a chance of being selected, we recruit through multiple online panel vendors and use targeted social media advertising to reach traditionally underrepresented groups.
 While this approach introduces potential selection bias because participants self-select into the sample, it helps reach younger voters who are less responsive to traditional survey methods.
@@
 [END OF SURVEY]
-
 Thank you for completing this survey about the 2024 U.S. Presidential Election. Your responses will help us better understand voter preferences and political attitudes across the country.

### 2024-11-03 paper/paper.qmd
Implemented survey in Google Forms and added link to qmd

@@
 Harris preferences), political preferences, demographics, issue priorities, and media consumption patterns.
-We've implemented this survey design in Google Forms, which can be found here: [Link to be added]
+We've implemented this survey design in Google Forms, which can be found here: https://forms.gle/pk7vDiMHwEGLMK849
 
@@
 ## Idealised survey
-The survey, made using Google Forms, is linked here:
+The survey, made using Google Forms, is linked here: https://forms.gle/pk7vDiMHwEGLMK849
 Note that the questions are identical for both the phone and online surveys bar q6.
@@
 
-Your responses will be kept confidential and used only for research purposes. You may skip any questions you prefer not to answer, though complete responses are most helpful for our research.
+Your responses will be kept confidential and used only for research purposes.
+Email information, and any other information that may personally identify you, is not gathered.
+You may skip any questions you prefer not to answer, though complete responses are most helpful for our research.
 
@@
 
-Q5. If the 2024 presidential election were held today, and the candidates were Donald Trump (Republican) and Kamala Harris (Democrat), who would you vote for?
+Q5. If the 2024 presidential election were held today, and the candidates were Kamala Harris (Democrat) and Donald Trump (Republican), who would you vote for?
 
+Kamala Harris
 Donald Trump
-Kamala Harris
 Another candidate (please specify)
@@
 POLITICAL PREFERENCES:
-Q7. Generally speaking, do you consider yourself a:
+Q7. Generally speaking, you consider yourself a:
 
+Democrat
 Republican
-Democrat
 Independent
@@
 
+Very poor
+Poor
+Fair
+Good
 Excellent
-Good
-Fair
-Poor
-Very poor
 
@@
 
-For each of the following issues, please indicate whether you think Donald Trump or Kamala Harris would do a better job handling it:
+For each of the following issues, please indicate whether you think Kamala Harris or Donald Trump would do a better job handling it:
 
@@
 
+Kamala Harris would do better
 Donald Trump would do better
-Kamala Harris would do better
 No difference
@@
 
-Q11. Immigration:
+Q11. Human rights and freedom of speech:
 [Same options]
-Q12. National security:
+Q12. Abortion:
 [Same options]
@@
 [Same options]
+Q14. Immigration:
+[Same options]
+Q15. National security:
+[Same options]
 
 MEDIA CONSUMPTION:
-Q14. Where do you most often get your news about politics? (Select all that apply)
+Q16. Where do you most often get your news about politics? (Select all that apply)
 
@@
 
-Q15. How many hours per day do you typically spend following news about politics?
+Q17. How many hours per day do you typically spend following news about politics?
 
@@
 DEMOGRAPHICS:
-Q16. What is your age?
+Q18. What is your age?
 
@@
 
-Q17. What is your gender?
+Q19. What is your gender?
 
@@
 
-Q18. What is your race/ethnicity? (Select all that apply)
+Q20. What is your race/ethnicity? (Select all that apply)
 
@@
 
-Q19. What is the highest level of education you have completed?
+Q21. What is the highest level of education you have completed?
 
@@
 
-Q20. What was your total household income before taxes in 2023?
+Q22. What was your total household income before taxes in 2023?
 
@@
 CONSISTENCY CHECK:
-Q21. Looking ahead to November 2024, if Donald Trump is the Republican nominee and Kamala Harris is the Democratic nominee, how do you think you will vote?
+Q23. Looking ahead to November 2024, if Kamala Harris is the Democratic nominee and Donald Trump is the Republican nominee, how do you think you will vote?
 
+Kamala Harris
 Donald Trump
-Kamala Harris
 Another candidate (please specify)
@@
 Your time and participation is greatly appreciated.
+
 # Additional data details

### 2024-11-03 paper/paper.qmd
ethics

@@
 
+Ethics-wise, the survey does a good job of informing individuals of the details of the survey, such as its purpose and how participants' data is to be used.
+Personally-identifiable data (i.e.
+name, phone number, etc.) is not collected during the survey other than to ensure that repeat numbers are not drawn, and the usage of live interviewers to conduct the survey ensures that concerns about the ethics of the survey can be voiced and answered on-the-spot.
+Combined with the lack of financial incentive for participants, which suggests that all participants participate of their complete free will and intention, this is an ethically sound methodology for conducting a political survey.
+
 Finally, the poll also faces common challenges in political polls such as this one - the five-day field period (October 24-28) may miss opinion changes close to election day, and while weighting adjustments help correct for demographic imbalances, they may increase variance in the estimates if some groups need to be weighted heavily to match population benchmarks, for example.
@@
 We produce daily estimates using a 7-day rolling average, which helps smooth out daily fluctuations while remaining responsive to real changes in voter preferences.
+
+Finally, how ethics are handled is a crucial part of any survey methodology.
+In this idealised methodology, consent will be asked for at the beginning of the survey, full disclosure of how information is used will be given beforehand and no self-identifiable information will be recorded (so no names, phone numbers, etc.).
+The $10 incentive is enough to hopefully make it worthwile for participants' time, but also not ideally not significant enough of an incentive to make individuals suppress otherwise deal-breaking concerns with the survey purely for the sake of the incentive.
 

### 2024-11-03 scripts/03-clean_data.R
deleted excess files

@@ -1,163 +1,0 @@
-#### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
-#### Workspace setup ####
-
-# Load libraries
-library(tidyverse)
-library(janitor)
-library(lubridate)
-library(broom)
-library(modelsummary)
-library(rstanarm)
-library(splines)
-
-
-#### Read data ####
-current_polls_data <- read_csv("data/01-raw_data/president_polls.csv") |>
-  clean_names()
-past_polls_data <- 
-  read_csv("data/01-raw_data/president_polls_historical.csv") |>
-  clean_names()
-
-# Filter data to Harris estimates based on high-quality polls after she declared
-just_harris_high_quality <- current_polls_data |>
-  filter(
-    candidate_name == "Kamala Harris",
-    numeric_grade >= 3.0,
-    population == 'lv' # keep likely voters only to be more predictive
-  ) |>
-  mutate(
-    state = if_else(is.na(state), "National", state),
-    end_date = mdy(end_date)
-  ) |>
-  filter(end_date >= as.Date("2024-07-21"))
-
-# Filter data to Trump estimates based on high-quality polls
-just_trump_high_quality <- current_polls_data |>
-  filter(
-    candidate_name == "Donald Trump",
-    numeric_grade >= 3.0,
-    population == 'lv' # keep likely voters only to be more predictive
-  ) |>
-  mutate(
-    state = if_else(is.na(state), "National", state),
-    end_date = mdy(end_date)
-  ) |>
-  filter(end_date >= as.Date("2024-07-21"))
-
-# repeat for historical data
-biden_past_high_quality <- past_polls_data |>
-  filter(
-    candidate_name == "Joe Biden",
-    numeric_grade >= 3.0,
-    population == 'lv' # keep likely voters only to be more predictive
-  ) |>
-  mutate(
-    state = if_else(is.na(state), "National", state),
-    end_date = mdy(end_date)
-  )
-
-trump_past_high_quality <- past_polls_data |>
-  filter(
-    candidate_name == "Donald Trump",
[…]

### 2024-11-03 scripts/05-exploratory_data_analysis.R

@@ -1,413 +1,0 @@
-#### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
-
-#### Workspace setup ####
-
-# Load libraries
-library(tidyverse)
-library(caret)
-library(glmnet)
-library(nnet)
-library(lubridate)
-library(pROC)
-library(stringr)
-
-
-#### Read data ####
-trump_2024 <- read_csv("data/02-analysis_data/trump_2024_analysis_data.csv")
-harris_2024 <- read_csv("data/02-analysis_data/harris_2024_analysis_data.csv")
-trump_2024_lower <- 
-  read_csv("data/02-analysis_data/trump_2024_analysis_data_lower.csv")
-harris_2024_lower <- 
-  read_csv("data/02-analysis_data/harris_2024_analysis_data_lower.csv")
-trump_2020 <- read_csv("data/02-analysis_data/trump_2020_analysis_data.csv")
-biden_2020 <- read_csv("data/02-analysis_data/biden_2020_analysis_data.csv")
-
-# find biases of pollsters from 2020 national polls data
-# filter out national polls from the datasets
-trump_2024_national <- trump_2024 %>% filter(state == "National")
-harris_2024_national <- harris_2024 %>% filter(state == "National")
-trump_2020_national <- trump_2020 %>% filter(state == "National")
-biden_2020_national <- biden_2020 %>% filter(state == "National")
-
-# Define actual results
-actual_results_2020 <- list(Trump_pct = 47, Biden_pct = 51)
-
-# Calculate bias per pollster
-rep_pollster_bias <- trump_2020_national %>%
-  group_by(pollster) %>%
-  summarize(
-    Trump_bias = mean(pct - actual_results_2020$Trump_pct, na.rm = TRUE)
-  )
-
-dem_pollster_bias <- biden_2020_national %>%
-  group_by(pollster) %>%
-    summarize(
-      Biden_bias = mean(pct - actual_results_2020$Biden_pct, na.rm = TRUE)
-  )
-
[…]

### 2024-11-03 scripts/02-clean_data.R
updated code for data cleaning

@@ -1,0 +1,174 @@
+#### Preamble ####
+# Purpose: Cleans the raw US presidential election polls data from FiveThirtyEight
+# Author: Andrew Goh, Yisu Hou
+# Date: 3 November 2024
+# Contact: rohan.alexander@utoronto.ca
+# License: MIT
+# Pre-requisites:
+
+#### Workspace setup ####
+
+# Load libraries
+library(tidyverse)
+library(janitor)
+library(lubridate)
+library(broom)
+library(modelsummary)
+library(rstanarm)
+library(splines)
+
+
+#### Read data ####
+current_polls_data <- read_csv("data/01-raw_data/president_polls.csv") |>
+  clean_names()
+past_polls_data <- 
+  read_csv("data/01-raw_data/president_polls_historical.csv") |>
+  clean_names()
+
+# Filter data to Harris estimates based on high-quality polls after she declared
+just_harris_high_quality <- current_polls_data |>
+  filter(
+    candidate_name == "Kamala Harris",
+    numeric_grade >= 3.0,
+    population == 'lv' # keep likely voters only to be more predictive
+  ) |>
+  mutate(
+    state = if_else(is.na(state), "National", state),
+    end_date = mdy(end_date),
+    has_sponsor = if_else(is.na(sponsors), 0, 1)
+  ) |>
+  filter(end_date >= as.Date("2024-07-21"))
+
+# Filter data to Trump estimates based on high-quality polls
+just_trump_high_quality <- current_polls_data |>
+  filter(
+    candidate_name == "Donald Trump",
+    numeric_grade >= 3.0,
+    population == 'lv' # keep likely voters only to be more predictive
+  ) |>
+  mutate(
+    state = if_else(is.na(state), "National", state),
+    end_date = mdy(end_date),
+    has_sponsor = if_else(is.na(sponsors), 0, 1)
+  ) |>
+  filter(end_date >= as.Date("2024-07-21"))
+
+# repeat for historical data
+biden_past_high_quality <- past_polls_data |>
+  filter(
+    candidate_name == "Joe Biden",
+    numeric_grade >= 3.0,
+    population == 'lv' # keep likely voters only to be more predictive
+  ) |>
+  mutate(
+    state = if_else(is.na(state), "National", state),
+    end_date = mdy(end_date),
+    has_sponsor = if_else(is.na(sponsors), 0, 1)
+  )
+
+trump_past_high_quality <- past_polls_data |>
+  filter(
[…]

### 2024-11-03 scripts/03-test_analysis_data.R
updated code for tests

@@ -1,0 +1,289 @@
+#### Preamble ####
+# Purpose: Tests... [...UPDATE THIS...]
+# Author: Andrew Goh, Yisu Hou
+# Date: 3 November 2024
+# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: [...UPDATE THIS...]
+# Any other information needed? [...UPDATE THIS...]
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(testthat)
+
+biden_2020 <- read_csv("data/02-analysis_data/biden_2020_analysis_data.csv")
+trump_2020 <- read_csv("data/02-analysis_data/trump_2020_analysis_data.csv")
+harris_2024 <- read_csv("data/02-analysis_data/harris_2024_analysis_data.csv")
+trump_2024 <- read_csv("data/02-analysis_data/trump_2024_analysis_data.csv")
+harris_2024_low <- read_csv("data/02-analysis_data/harris_2024_analysis_data_lower.csv")
+trump_2024_low <- read_csv("data/02-analysis_data/trump_2024_analysis_data_lower.csv")
+
+
+# Create a named list of datasets
+datasets_list <- list(
+  biden_2020 = biden_2020,
+  trump_2020 = trump_2020,
+  harris_2024 = harris_2024,
+  trump_2024 = trump_2024
+)
+
+datasets_list_low <- list(
+  harris_2024_low = harris_2024_low,
+  trump_2024_low = trump_2024_low
+)
+
+
+# Define the helper function to run tests
+run_sanity_checks <- function(data, dataset_name) {
+  
+  test_that(paste("Sanity Checks for", dataset_name), {
+    
+    #### Data Structure Tests ####
+    
+    # Check if the dataset is a dataframe
+    expect_true(is.data.frame(data), info = paste(dataset_name, "is not a dataframe"))
+    
+    # Check number of rows
+    expect_true(nrow(data) >= 50 && nrow(data) <= 1000, 
+                info = paste(dataset_name, "does not have between 50 and 1000 rows"))
+    
+    # Check number of columns (11)
+    expect_equal(ncol(data), 11, 
+                 info = paste(dataset_name, "does not have exactly 11 columns"))
+    
+    # Check for required columns
+    required_cols <- c("pollster", "has_sponsor", "numeric_grade", "pollscore", 
+                       "transparency_score", "sample_size", "end_date",
+                       "state", "candidate_name", "pct", "cycle")
[…]

### 2024-11-03 scripts/04-exploratory_data_analysis.R
renamed scripts

@@ -1,0 +1,399 @@
+#### Preamble ####
+# Purpose: Models... [...UPDATE THIS...]
+# Author: Andrew Goh, Yisu Hou
+# Date: 3 November 2024
+# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: [...UPDATE THIS...]
+# Any other information needed? [...UPDATE THIS...]
+
+
+#### Workspace setup ####
+
+# Load libraries
+library(tidyverse)
+library(caret)
+library(glmnet)
+library(nnet)
+library(lubridate)
+library(pROC)
+library(stringr)
+
+
+#### Read data ####
+trump_2024 <- read_csv("data/02-analysis_data/trump_2024_analysis_data.csv")
+harris_2024 <- read_csv("data/02-analysis_data/harris_2024_analysis_data.csv")
+trump_2024_lower <- 
+  read_csv("data/02-analysis_data/trump_2024_analysis_data_lower.csv")
+harris_2024_lower <- 
+  read_csv("data/02-analysis_data/harris_2024_analysis_data_lower.csv")
+trump_2020 <- read_csv("data/02-analysis_data/trump_2020_analysis_data.csv")
+biden_2020 <- read_csv("data/02-analysis_data/biden_2020_analysis_data.csv")
+
+# find biases of pollsters from 2020 national polls data
+# filter out national polls from the datasets
+trump_2024_national <- trump_2024 %>% filter(state == "National")
+harris_2024_national <- harris_2024 %>% filter(state == "National")
+trump_2020_national <- trump_2020 %>% filter(state == "National")
+biden_2020_national <- biden_2020 %>% filter(state == "National")
+
+# Define actual results
+actual_results_2020 <- list(Trump_pct = 47, Biden_pct = 51)
+
+# Calculate bias per pollster
+rep_pollster_bias <- trump_2020_national %>%
+  group_by(pollster) %>%
+  summarize(
+    Trump_bias = mean(pct - actual_results_2020$Trump_pct, na.rm = TRUE)
+  )
+
+dem_pollster_bias <- biden_2020_national %>%
+  group_by(pollster) %>%
+    summarize(
+      Biden_bias = mean(pct - actual_results_2020$Biden_pct, na.rm = TRUE)
+  )
+
+# adjust 2024 national polls percentages by the average pollster biases
[…]

### 2024-11-03 scripts/00-simulate_data.R
updated preamble

@@ -1,12 +1,10 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of Australian electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
+# Purpose: Simulates a dataset of US presidential election polls
+# Author: Andrew Goh, Yisu Hou
+# Date: 3 November 2024
 # Contact: rohan.alexander@utoronto.ca
 # License: MIT
-# Pre-requisites: The `tidyverse` package must be installed
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Pre-requisites: Packages `tidyverse` and `lubridate` must be installed
 
 
 #### Workspace setup ####

### 2024-11-03 scripts/01-test_simulated_data.R

@@ -1,14 +1,13 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
+# Purpose: Tests the structure and validity of the simulated US 
+  # electoral polls dataset.
+# Author: Andrew Goh, Yisu Hou
+# Date: 3 November 2024
 # Contact: rohan.alexander@utoronto.ca
 # License: MIT
 # Pre-requisites: 
-  # - The `tidyverse` package must be installed and loaded
+  # - Packages `tidyverse`, `lubridate`, and `testthat` must be installed
   # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
 
 
 #### Workspace setup ####

### 2024-11-03 scripts/04-exploratory_data_analysis.R
updated code

@@ -30,127 +30,7 @@ harris_2024_lower <-
 trump_2020 <- read_csv("data/02-analysis_data/trump_2020_analysis_data.csv")
 biden_2020 <- read_csv("data/02-analysis_data/biden_2020_analysis_data.csv")
 
-# find biases of pollsters from 2020 national polls data
-# filter out national polls from the datasets
-trump_2024_national <- trump_2024 %>% filter(state == "National")
-harris_2024_national <- harris_2024 %>% filter(state == "National")
-trump_2020_national <- trump_2020 %>% filter(state == "National")
-biden_2020_national <- biden_2020 %>% filter(state == "National")
-
-# Define actual results
-actual_results_2020 <- list(Trump_pct = 47, Biden_pct = 51)
-
-# Calculate bias per pollster
-rep_pollster_bias <- trump_2020_national %>%
-  group_by(pollster) %>%
-  summarize(
-    Trump_bias = mean(pct - actual_results_2020$Trump_pct, na.rm = TRUE)
-  )
-
-dem_pollster_bias <- biden_2020_national %>%
-  group_by(pollster) %>%
-    summarize(
-      Biden_bias = mean(pct - actual_results_2020$Biden_pct, na.rm = TRUE)
-  )
-
-# adjust 2024 national polls percentages by the average pollster biases
-# also mutate has_sponsor variable into dummy variable and remove NA's
-trump_2024_national_adj <- trump_2024_national %>%
-  left_join(rep_pollster_bias, by = "pollster") %>%
-  mutate(
-    pct_adj = pct - ifelse(!is.na(Trump_bias), Trump_bias, 0)
-  ) %>%
-  select(-Trump_bias)
-
-# Adjust Harris 2024 National Polls
-harris_2024_national_adj <- harris_2024_national %>%
-  left_join(dem_pollster_bias, by = "pollster") %>%
-  mutate(
-    pct_adj = pct - ifelse(!is.na(Biden_bias), Biden_bias, 0)
-  ) %>%
-  select(-Biden_bias)
-
-
-# model adjusted support percentage by time and control variables
-# first split training and testing dataset using an 80/20 split
-set.seed(11451)
-trainIndex_trump <- createDataPartition(trump_2024_national_adj$pct_adj, 
-      p = 0.8, list = FALSE)
-data_train_trump <- trump_2024_national_adj[trainIndex_trump, ]
-data_test_trump  <- trump_2024_national_adj[-trainIndex_trump, ]
-
[…]

### 2024-11-03 scripts/05-model_data.R

@@ -9,23 +9,467 @@
 
 
 #### Workspace setup ####
+
+# Load libraries
 library(tidyverse)
-library(rstanarm)
+library(caret)
+library(glmnet)
+library(nnet)
+library(lubridate)
+library(pROC)
+library(stringr)
+
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+trump_2024 <- read_csv("data/02-analysis_data/trump_2024_analysis_data.csv")
+harris_2024 <- read_csv("data/02-analysis_data/harris_2024_analysis_data.csv")
+trump_2024_lower <- 
+  read_csv("data/02-analysis_data/trump_2024_analysis_data_lower.csv")
+harris_2024_lower <- 
+  read_csv("data/02-analysis_data/harris_2024_analysis_data_lower.csv")
+trump_2020 <- read_csv("data/02-analysis_data/trump_2020_analysis_data.csv")
+biden_2020 <- read_csv("data/02-analysis_data/biden_2020_analysis_data.csv")
 
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
+# find biases of pollsters from 2020 national polls data
+# filter out national polls from the datasets
+trump_2024_national <- trump_2024 %>% filter(state == "National")
+harris_2024_national <- harris_2024 %>% filter(state == "National")
+trump_2020_national <- trump_2020 %>% filter(state == "National")
+biden_2020_national <- biden_2020 %>% filter(state == "National")
+
+# Define actual results
+actual_results_2020 <- list(Trump_pct = 47, Biden_pct = 51)
+
+# Calculate bias per pollster
+rep_pollster_bias <- trump_2020_national %>%
+  group_by(pollster) %>%
+  summarize(
+    Trump_bias = mean(pct - actual_results_2020$Trump_pct, na.rm = TRUE)
   )
+
+dem_pollster_bias <- biden_2020_national %>%
+  group_by(pollster) %>%
+  summarize(
+    Biden_bias = mean(pct - actual_results_2020$Biden_pct, na.rm = TRUE)
+  )
+
[…]

### 2024-11-03 scripts/05-model_data.R
updated code

@@ -224,169 +224,7 @@ ggplot(combined_data, aes(x = end_date, y = pct, color = candidate_name)) +
   )
 
 
-# Regional polls analysis
-trump_2024_regional <- trump_2024_lower %>% filter(state != "National")
-harris_2024_regional <- harris_2024_lower %>% filter(state != "National")
 
-trump_by_state <- trump_2024_regional %>%
-  group_by(state) %>%
-  summarize(
-    Trump_State_Support = mean(pct, na.rm = TRUE),
-    Trump_SD_support = sd(pct, na.rm = TRUE),
-    Trump_n = n()
-  ) %>%
-  mutate(
-    Trump_SE = Trump_SD_support / sqrt(Trump_n),                
-    Trump_t = qt(0.975, df = Trump_n - 1),                       
-    Trump_CI_lower = Trump_State_Support - Trump_t * Trump_SE,   
-    Trump_CI_upper = Trump_State_Support + Trump_t * Trump_SE      
-  )
-harris_by_state <- harris_2024_regional %>%
-  group_by(state) %>%
-  summarize(
-    Harris_State_Support = mean(pct, na.rm = TRUE),
-    Harris_SD_support = sd(pct, na.rm = TRUE),
-    Harris_n = n()
-  ) %>%
-  mutate(
-    Harris_SE = Harris_SD_support / sqrt(Harris_n),                
-    Harris_t = qt(0.975, df = Harris_n - 1),                       
-    Harris_CI_lower = Harris_State_Support - Harris_t * Harris_SE,   
-    Harris_CI_upper = Harris_State_Support + Harris_t * Harris_SE      
-  )
-
-
-# combine the two data frames for comparison
-combined_regional <- left_join(
-  trump_by_state,
-  harris_by_state,
-  by = "state"
-)
-
-# change all NaN values to NA
-combined_regional <- combined_regional %>%
-  mutate(across(everything(), ~ replace(.x, is.nan(.x), NA)))
-
-# Mutate expected winner column, determined by the confidence intervals
-# If confidence intervals are missing, compare average support levels instead
-combined_regional <- combined_regional %>% mutate(
[…]

### 2024-11-04 paper/paper.qmd
updated paper

@@
   - First author
-  - Another author
+  - Yisu Hou
 thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
@@
 format: pdf
+header-includes:
+  - \usepackage{float}
+  - \usepackage{placeins}
 number-sections: true
@@
 library(tidyverse)
-library(palmerpenguins)
+library(caret)
+library(glmnet)
+library(nnet)
+library(lubridate)
+library(pROC)
+library(stringr)
 ```
@@
 Overview paragraph
+
+note: For the literature review/why our thing matters section talk about how other predictions don't consider the biases in polls.
+Our thing is something new because we attempt to account for the bias in historical predictions for our 2024 prediction.
+(basically, for all models and predictions, I have an adjusted version that adjusts the support percentage using the difference between 2020 polls and real election outcomes, and a normal version that just uses the percentages from 2024 polls)
+
+There's essentially 3 different levels of analysis: using multiple linear regression to look at the candidates' support over time on the national level, using logistic regression to predict the chance of winning on the national level, using state polls data to see who is ahead in electoral college votes.
 
@@
 
-## Outcome variables
+## Outcome variable
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
-
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+The outcome variable is the level of support for the two leading US presidential candidates, Vice President Kamala Harris and Former President Donald Trump, recorded as a percentage of likely voters.
+For the national-level analysis, the support percentage represents the percentage of polled individuals who responded in favor of a specific candidate to a question that asked about their preferred presidential candidate in a national-level poll.
+For the regional datasets, the support percentage represents the percentage of likely voters who preferred a specific candidate in a poll that targets a specific state or congressional district of the United States.
+@fig-outcome shows the distribution of support percentages in the aggregated polling data from 2020 and 2024 presidential elections.
 
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
 #| echo: false
+#| message: false
+#| warning: false
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+trump_2024 <- read_csv(here::here("data/02-analysis_data/trump_2024_analysis_data.csv"))
+harris_2024 <- read_csv(here::here("data/02-analysis_data/harris_2024_analysis_data.csv"))
+trump_2024_lower <- 
+  read_csv(here::here("data/02-analysis_data/trump_2024_analysis_data_lower.csv"))
+harris_2024_lower <- 
+  read_csv(here::here("data/02-analysis_data/harris_2024_analysis_data_lower.csv"))
+trump_2020 <- read_csv(here::here("data/02-analysis_data/trump_2020_analysis_data.csv"))
+biden_2020 <- read_csv(here::here("data/02-analysis_data/biden_2020_analysis_data.csv"))
+
+# aggregated dataset for summary statistics
+# datasets with lower numeric scores already includes polls with a score of 3.0
+all_combined <- bind_rows(harris_2024_lower, trump_2024_lower,
+    biden_2020, trump_2020)
+
 ```
 
-Talk more about it.
+```{r}
+#| label: fig-outcome
+#| fig-cap: Percentage Support in US Presidential Polls
+#| echo: false
+#| message: false
+#| warning: false
 
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+ggplot(all_combined, aes(x = pct)) +
+  geom_histogram(
+    binwidth = 1,                # Adjust bin width for granularity
+    fill = "#2c7bb6",            # Aesthetic fill color (steel blue)
+    color = "white",             # Border color for bins
+    alpha = 0.8                   # Transparency of the fill
+  ) +
+  labs(
+    x = "Percentage Support",
+    y = "Number of Polls"
+  ) +
+  theme_minimal(base_size = 14) +   # Minimal theme with increased base font size
+  theme(
+    plot.title = element_text(
+      size = 16, 
+      face = "bold", 
+      hjust = 0.5,                # Center the title
+      margin = margin(b = 10)     # Add space below the title
+    ),
+    plot.subtitle = element_text(
+      size = 12, 
+      hjust = 0.5, 
+      margin = margin(b = 20)     # Add space below the subtitle
+    ),
+    axis.title = element_text(face = "bold"), # Bold axis titles
+    axis.text = element_text(color = "gray30"), # Dark gray axis text
+    panel.grid.major = element_line(color = "gray80"), # Light gray major grid lines
+    panel.grid.minor = element_blank()                 # Remove minor grid lines
+  ) +
+  # Add a vertical line for the mean percentage support
+  geom_vline(
+    aes(xintercept = mean(pct, na.rm = TRUE)),
+    color = "#d73027",           # Aesthetic color (red)
+    linetype = "dashed", 
+    size = 1
+  ) +
+  # Annotate the mean value on the plot
+  annotate(
+    "text",
+    x = mean(all_combined$pct, na.rm = TRUE) - 7, # Position text slightly to the right of the mean line
+    y = Inf,                                     # Position text at the top of the plot
+    label = paste("Mean:", round(mean(all_combined$pct, na.rm = TRUE), 1), "%"),
+    vjust = 2,                                   # Vertical adjustment
+    color = "#d73027",
+    size = 5,
+    fontface = "bold"
+  )
 
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
 ```
 
-Talk way more about it.
+\FloatBarrier
+
+The aggregated polling data includes support percentages of different presidential candidates in polls with different FiveThirtyEight ratings [CITATION HERE https://abcnews.go.com/538/best-pollsters-america/story?id=105563951] across two elections.
+Please view [UPDATE APPENDIX] for summary statistics of sub-datasets.
+
+As displayed by @fig-outcome, the distribution of support percentages is close to a normal distribution, with most data points between 45 and 52 percent.
 
@@
 
-Add graphs, tables and text.
+### End Date
+```{r}
+#| label: fig-dates-past
+#| fig-cap: Distribution of Poll End Date, 2020 Cycle
+#| echo: false
+#| message: false
+#| warning: false
 
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+ggplot(all_combined %>% filter(cycle == 2020), aes(x = end_date)) +
+  geom_histogram(binwidth = 7, fill = "#1f78b4", color = "white", alpha = 0.7) +
+  labs(
+    x = "End Date",
+    y = "Number of Polls"
+  ) +
+  scale_x_date(date_labels = "%b %d, %Y", date_breaks = "1 month") +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 14, face = "bold"),
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  )
+
+```
+\vspace{1em}
+\FloatBarrier
+
+```{r}
+#| label: fig-dates-current
+#| fig-cap: Distribution of Poll End Date, 2024 Cycle
+#| echo: false
+#| message: false
+#| warning: false
+
+ggplot(all_combined %>% filter(cycle == 2024), aes(x = end_date)) +
+  geom_histogram(binwidth = 7, fill = "#1f78b4", color = "white", alpha = 0.7) +
+  labs(
+    x = "End Date",
+    y = "Number of Polls"
+  ) +
+  scale_x_date(date_labels = "%b %d, %Y", date_breaks = "1 month") +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 14, face = "bold"),
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  )
+
+```
+\FloatBarrier
+
+### Sponsored
+
+```{r}
+#| label: fig-sponsored
+#| fig-cap: Number of Polls with and without Sponsors
+#| echo: false
+#| message: false
+#| warning: false
+
+ggplot(all_combined, aes(x = factor(has_sponsor, levels = c(0,1), labels = c("No Sponsor", "Has Sponsor")))) +
+  geom_bar(fill = "#1f78b4", color = "white", alpha = 0.7) +
+  labs(
+    x = "Has Sponsor",
+    y = "Number of Polls"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 14, face = "bold")
+  )
+
+```
+
+\FloatBarrier
+
+### Transparency Score
+
+```{r}
+#| label: fig-transparency
+#| fig-cap: Distribution of Transparency Scores
+#| echo: false
+#| message: false
+#| warning: false
+
+ggplot(all_combined, aes(x = factor(transparency_score))) +
+  geom_bar(fill = "#1f78b4", color = "white", alpha = 0.7) +
+  labs(
+    x = "Transparency Score",
+    y = "Number of Polls"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 14, face = "bold")
+  )
+
+```
+
+\FloatBarrier
+
+### Sample Size
+
+```{r}
+#| label: fig-sample
+#| fig-cap: Distribution of Sample Sizes
+#| echo: false
+#| message: false
+#| warning: false
+
+ggplot(all_combined, aes(x = sample_size)) +
+  geom_histogram(binwidth = 500, fill = "#1f78b4", color = "white", alpha = 0.7) +
+  labs(
+    x = "Sample Size",
+    y = "Number of Polls"
+  ) +
+  scale_x_continuous(labels = scales::comma) +
+  coord_cartesian(xlim = c(0, 6000)) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 14, face = "bold")
+  )
+
+```
+
+\FloatBarrier
 
@@
 ```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
 
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
 ```
@@
 ```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
 
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
 ```
@@
 ```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
 
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
 ```
@@
 ```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
 
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
 ```

### 2024-11-04 paper/paper.qmd
updated paper

@@
 #| label: fig-transparency
-#| fig-cap: Distribution of Transparency Scores
+#| fig-cap: Distribution of Poll Transparency Scores
 #| echo: false
@@
 #| label: fig-sample
-#| fig-cap: Distribution of Sample Sizes
+#| fig-cap: Distribution of Poll Sample Sizes
 #| echo: false

### 2024-11-04 paper/paper.qmd
data, appendices, citations

@@
 
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
+We use the statistical programming language R [@R] for the graphing, analysis and presentation of the project as a whole.
+Caret [@caret], glmnet [@glmnet; @glmnet2; @glmnet3], nnet [@nnet], lubridate [@lubridate] and pROC [@pROC] were used directly in the analysis of the data.
+Tidyverse [@tidyverse], stringr [@stringr], dplyr [@dplyr], and styler [@styler] were used in the presentation and/or styling of the data, graphs, and paper as a whole.
 
-Overview text
+In order to build a model that predicts the results of the 2024 election, we use survey/poll data on likely voters to inform our insights regarding likely election results, an approach widely accepted in political contexts [@politicalpolling].
+We use a poll-of-polls dataset from 538 [@538data], consisting of aggregated polling data from FiveThirtyEight's 2024 presidential election polling database from various national and state-level polls from pollsters all around the country, recording information such as the date when the poll concluded, the entity conducting the poll, and the estimated support rate of the candidate as given by the poll.
+The data spans national and state-level polls, with particular focus on key battleground states that could determine the Electoral College outcome.
+This dataset was chosen over alternatives like RealClearPolitics because of 538's comprehensive methodological adjustments and transparent quality standards for included polls.
+
+After cleaning the data to split results by candidate, remove polls with N/A values and ratings lower than 2.5, and further selecting polls polling likely voters as opposed to the whole population, we are left with 746 data points with the variables pollster, has_sponsor, numeric_grade, pollscore, transparency_score, sample_size, end_date, state, candidate_name, pct (support rate in percentage), and cycle (election cycle, i.e.
+2020/2024).
 
@@
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+The "from-voter-to-data" process for the 538 dataset involves three processes: measurement, where voter responses are collected and adjusted to best provide insight into a true support percentage population parameter, data collection, where data from polls is obtained and cleaned by 538 to only include polls adhering to their set of standards, and aggregation, where additional scores/variables are given to each poll to reflect their accuracy, transparency and bias levels with regards to polling scores [@5381; @5382; @5383].
+
+The measurement process involves several sequential steps, beginning with initial data collection where pollsters conduct surveys using various modes such as phone, online, or mixed-mode approaches to gather voter preferences.
+Sample processing follows, involving likely voter screens to identify probable voters, demographic weighting to match population benchmarks, and various adjustments to ensure representativeness.
+
+The data collection process involves obtaining data from various election polls from around the country, given that they meet specific methodological criteria.
+Each included poll must provide clear documentation of pollster identity, survey dates, and sampled population, maintain a minimum sample size of 100 respondents, and demonstrate transparent methodology including polling mode, sample source, and weighting procedures.
+Scientific sampling methods attempting to achieve representative samples are mandatory, as is the disclosure of poll sponsorship and funding sources.
+The dataset explicitly excludes non-scientific polls lacking representative sampling, MRP-smoothed data, recontact surveys, DIY polls from nonprofessional sources, polls with leading questions or hypothetical matchups, and subsamples from multi-state polls without geographic verification.
+
+The aggregation phase, finally, involves rating polls by pollster polling quality (ranging from 0.5 to 3.0 stars), with polls with higher historical accuracy, lower consistent partisan biases, and higher transparency of methodology boasting higher ratings.
+FiveThirtyEight then applies quality adjustments, including house effects corrections for systematic pollster biases, mode effects adjustments for sampling method biases, population adjustments between likely and registered voters, third-party candidate inclusion effects, and partisan poll adjustments.
+
+Several important measurement limitations to FiveThirtyEight's methodology must be acknowledged.
+These include temporal gaps between polls creating discontinuous measurement of voter sentiment, response rates and participation biases potentially skewing samples, and varying geographic coverage with swing states being overrepresented.
+Additionally, third-party candidate treatment varies across polls, while house effects and mode effects corrections rely on historical patterns that may not hold true in current contexts.
 
@@
 
-The aggregated polling data includes support percentages of different presidential candidates in polls with different FiveThirtyEight ratings [CITATION HERE https://abcnews.go.com/538/best-pollsters-america/story?id=105563951] across two elections.
+The aggregated polling data includes support percentages of different presidential candidates in polls with different FiveThirtyEight ratings [@5382] across two elections.
 Please view [UPDATE APPENDIX] for summary statistics of sub-datasets.
@@
 ## Predictor variables
+
+The predictor variables that we ended up using in our final logistic regression model were the poll end dates, transparency score, and sample sizes of the polls, as well as whether or not a poll was sponsored.
+The distributions of the variables is as follows:
 
@@
 \FloatBarrier
+The end date indicates the date that a poll ends on.
+The dates are graphed separately between the 2020 and 2024 cycles for ease of viewing.
+Notice how there is a disproportionately large uptick in the number of polls that end on the end of a month.
 
-### Sponsored
+### Sponsors
 
@@
 ```
+
+Has_sponsor is a categorical variable that keeps track of whether the poll is sponsored by a third party other than the one conducting the poll itself.
+This is distributed roughly 60-40, with the larger portion of polls being independently funded (i.e.
+no sponsors).
 
@@
 ```
+
+The transparency score is a metric given to a poll/pollster by 538 that measures the transparency of the methodology with which the poll is conducted.
+This is done through a 10-question yes/no checklist on how much of the methodology is available to the public - note how this is completely separate from the quality of the methodology itself.
+Each question is graded on a 0/0.5/1 scale, for a combined transparency score that ranges from 0 to 10 [@5383].
+Most polls in our dataset miss the mark on one or two criteron, netting a final transparency score of 9 - this is partially due to the data cleaning process removing many relatively worsely conducted polls.
 
@@
 ```
+
+Sample size, finally, is a measure of the number of participants in each poll.
+Around 1000 participants seems to overwhelmingly be the final survey size that pollsters decide on, with only single-digit numbers of polls (with rating >= 2.5) boasting more than four thousand respondents.
 
@@
 ## Pollster methodology overview and evaluation
-The Quinnipiac University Poll conducts independent polling in swing states - to analyze their methodology, we look specifically into their October 2024 Pennsylvania polls.
+The Quinnipiac University Poll conducts independent polling in swing states. To analyze their methodology, we look specifically into their October 2024 Pennsylvania polls [@quinnipiac].
 
-Their target population is likely voters aged 18 and older in Pennsylvania.
+Their target population is likely voters aged 18 and older in Pennsylvania [@quinnipiacmethodology].
 To reach this population, they use likely voters aged 18 and older with phone numbers (both landline and cell) as their sampling frame, i.e.
@@
 Their sampling approach uses stratification by Census division according to area code, meaning that they divide Pennsylvania into geographic regions before using RDD to sample within each region.
-This strategy ensures even geographic representation but adds complexity to the sampling process.
+This strategy ensures even geographic representation but adds complexity to the sampling process [@pollofpolls].
 For each selected number, they attempt contact at least three times before marking it as non-responsive.
@@
 For example, if their sample has too few young voters compared to Census data, responses from young voters would be weighted more heavily.
-While this helps correct for sampling imbalances, it can increase the variance in their estimates if the weights vary substantially.
+While this helps correct for sampling imbalances, it can increase the variance in their estimates if the weights vary substantially [@poststratification].
 
@@
 However, live interviewers may introduce social desirability bias, where respondents might modify their answers to appear more socially acceptable.
-This becomes particularly relevant in political polling, where respondents might hesitate to express unpopular political views.
+This becomes particularly relevant in political polling, where respondents might hesitate to express unpopular political views [@politicalpolling].
 
@@
 Self-selection bias occurs because certain types of people (typically those more politically engaged or with stronger views) are more likely to agree to participate in the survey.
-Non-response bias arises when people who respond differ systematically from those who don't - for instance, busier people might be less likely to answer calls, potentially underrepresenting certain occupational groups.
+Non-response bias arises when people who respond differ systematically from those who don't - for instance, busier people might be less likely to answer calls, potentially underrepresenting certain occupational groups [@nonresponse].
 Coverage bias means some groups (like those without phones) have no chance of being included in the sample.
@@
 
-Overall, Quinnipiac's methodology represents a balanced approach to managing practical constraints and statistical rigor in modern political polling - while some common biases are still likely to skew the poll results off the true support levels for Harris, for example, the poll uses methods such as post-stratification weighting to tradeoff biases at the cost of model variance.
+Overall, Quinnipiac's methodology represents a balanced approach to managing practical constraints and statistical rigor in modern political polling - while some common biases are still likely to skew the poll results off the true support levels for Harris, for example, the poll uses methods such as post-stratification weighting to tradeoff biases at the cost of model variance [@weighting].
 Using live interviewers unavoidably introduces social desirability bias, however, and significantly increases poll costs per quota.
@@
 RDD involves generating random phone numbers within active area codes, while ABS uses the U.S.
-Postal Service's delivery database as a sampling frame.
+Postal Service's delivery database as a sampling frame, both proven methods of sampling [@cummings].
 The ABS approach helps reach households without reliable phone access.
@@
 $40k), where respondents' selection probabilities are unknown and not everyone has a chance of being selected, we recruit through multiple online panel vendors and use targeted social media advertising to reach traditionally underrepresented groups.
-While this approach introduces potential selection bias because participants self-select into the sample, it helps reach younger voters who are less responsive to traditional survey methods.
+While this approach introduces potential selection bias because participants self-select into the sample, it helps reach younger voters who are less responsive to traditional survey methods [@nonprobabilitysampling].
 We implement quota sampling within these non-probability samples to match key demographic targets - for example, stopping collection from certain demographic groups once their quota is filled.
@@
 We include demographics (age, race, education, gender), geographic location, past voting behavior, and party registration in our weighting scheme.
-We produce daily estimates using a 7-day rolling average, which helps smooth out daily fluctuations while remaining responsive to real changes in voter preferences.
+We produce daily estimates using a 7-day rolling average, which helps smooth out daily fluctuations while remaining responsive to real changes in voter preferences [@weighting2].
 
@@
 In this idealised methodology, consent will be asked for at the beginning of the survey, full disclosure of how information is used will be given beforehand and no self-identifiable information will be recorded (so no names, phone numbers, etc.).
-The $10 incentive is enough to hopefully make it worthwile for participants' time, but also not ideally not significant enough of an incentive to make individuals suppress otherwise deal-breaking concerns with the survey purely for the sake of the incentive.
+The $10 incentive is enough to hopefully make it wortile for participants' time, but also not ideally not significant enough of an incentive to make individuals suppress otherwise deal-breaking concerns with the survey purely for the sake of the incentive.
 

### 2024-11-04 scripts/04-exploratory_data_analysis.R
updated code

@@ -30,169 +30,117 @@ harris_2024_lower <-
 trump_2020 <- read_csv("data/02-analysis_data/trump_2020_analysis_data.csv")
 biden_2020 <- read_csv("data/02-analysis_data/biden_2020_analysis_data.csv")
 
-# Summary statistics of datasets [to be updated]
+# Distribution of variables in the dataset
+all_combined <- bind_rows(harris_2024_lower, trump_2024_lower,
+                          biden_2020, trump_2020)
 
-# Regional polls analysis
-trump_2024_regional <- trump_2024_lower %>% filter(state != "National")
-harris_2024_regional <- harris_2024_lower %>% filter(state != "National")
-
-trump_by_state <- trump_2024_regional %>%
-  group_by(state) %>%
-  summarize(
-    Trump_State_Support = mean(pct, na.rm = TRUE),
-    Trump_SD_support = sd(pct, na.rm = TRUE),
-    Trump_n = n()
-  ) %>%
-  mutate(
-    Trump_SE = Trump_SD_support / sqrt(Trump_n),                
-    Trump_t = qt(0.975, df = Trump_n - 1),                       
-    Trump_CI_lower = Trump_State_Support - Trump_t * Trump_SE,   
-    Trump_CI_upper = Trump_State_Support + Trump_t * Trump_SE      
-  )
-harris_by_state <- harris_2024_regional %>%
-  group_by(state) %>%
-  summarize(
-    Harris_State_Support = mean(pct, na.rm = TRUE),
-    Harris_SD_support = sd(pct, na.rm = TRUE),
-    Harris_n = n()
-  ) %>%
-  mutate(
-    Harris_SE = Harris_SD_support / sqrt(Harris_n),                
-    Harris_t = qt(0.975, df = Harris_n - 1),                       
-    Harris_CI_lower = Harris_State_Support - Harris_t * Harris_SE,   
-    Harris_CI_upper = Harris_State_Support + Harris_t * Harris_SE      
-  )
-
-
-# combine the two data frames for comparison
-combined_regional <- left_join(
-  trump_by_state,
-  harris_by_state,
-  by = "state"
-)
-
-# change all NaN values to NA
-combined_regional <- combined_regional %>%
-  mutate(across(everything(), ~ replace(.x, is.nan(.x), NA)))
-
[…]

### 2024-11-04 scripts/05-model_data.R

@@ -225,7 +225,6 @@ ggplot(combined_data, aes(x = end_date, y = pct, color = candidate_name)) +
 
 
 
-
 #### Logistic regression for national support ####
 
 combined_national <- full_join(
@@ -294,7 +293,6 @@ roc_obj <- roc(combined_national$harris_win,
                combined_national$harris_win_prob)
 plot(roc_obj, main = "ROC Curve for Harris Win Prediction")
 auc_value <- auc(roc_obj)
-print(paste("AUC:", auc_value))
 
 # note: roc curve above diagonal line is good
 # auc value closer to 1 is good, closer to 0 is bad
@@ -307,7 +305,248 @@ cor_matrix <- combined_national %>%
 
 print(cor_matrix)
 
+# Regional polls analysis
+trump_2024_regional <- trump_2024_lower %>% filter(state != "National")
+harris_2024_regional <- harris_2024_lower %>% filter(state != "National")
 
+
+trump_Pennsylvania <- trump_2024_regional %>% filter(state == "Pennsylvania")
+trump_Georgia <- trump_2024_regional %>% filter(state == "Georgia")
+trump_North_Carolina <- trump_2024_regional %>% filter(state == "North Carolina")
+trump_Michigan <- trump_2024_regional %>% filter(state == "Michigan")
+trump_Arizona <- trump_2024_regional %>% filter(state == "Arizona")
+trump_Wisconsin <- trump_2024_regional %>% filter(state == "Wisconsin")
+trump_Nevada <- trump_2024_regional %>% filter(state == "Nevada")
+
+harris_Pennsylvania <- harris_2024_regional %>% filter(state == "Pennsylvania")
+harris_Georgia <- harris_2024_regional %>% filter(state == "Georgia")
+harris_North_Carolina <- harris_2024_regional %>% filter(state == "North Carolina")
+harris_Michigan <- harris_2024_regional %>% filter(state == "Michigan")
+harris_Arizona <- harris_2024_regional %>% filter(state == "Arizona")
+harris_Wisconsin <- harris_2024_regional %>% filter(state == "Wisconsin")
+harris_Nevada <- harris_2024_regional %>% filter(state == "Nevada")
+
+combined_Pennsylvania <- full_join(
+  trump_Pennsylvania,
+  harris_Pennsylvania,
+  by = c("pollster", "has_sponsor", "pollscore", 
[…]

### 2024-11-04 paper/paper.qmd
minor edits

@@
 author: 
-  - First author
+  - Andrew Goh
   - Yisu Hou
@@
 
-After cleaning the data to split results by candidate, remove polls with N/A values and ratings lower than 2.5, and further selecting polls polling likely voters as opposed to the whole population, we are left with 746 data points with the variables pollster, has_sponsor, numeric_grade, pollscore, transparency_score, sample_size, end_date, state, candidate_name, pct (support rate in percentage), and cycle (election cycle, i.e.
+After cleaning the data to split results by candidate, removing polls with N/A values and ratings lower than 2.5, and further selecting polls polling likely voters as opposed to the whole population, we are left with 746 data points with the variables pollster, has_sponsor, numeric_grade, pollscore, transparency_score, sample_size, end_date, state, candidate_name, pct (support rate in percentage), and cycle (election cycle, i.e.
 2020/2024).
@@
 
-The "from-voter-to-data" process for the 538 dataset involves three processes: measurement, where voter responses are collected and adjusted to best provide insight into a true support percentage population parameter, data collection, where data from polls is obtained and cleaned by 538 to only include polls adhering to their set of standards, and aggregation, where additional scores/variables are given to each poll to reflect their accuracy, transparency and bias levels with regards to polling scores [@5381; @5382; @5383].
+The "from-voter-to-data" process for the 538 dataset involves three processes: measurement, where voter responses are collected and adjusted to best provide insight into a true support percentage population parameter, data collection, where data from polls is obtained and cleaned by 538 to only include polls adhering to their set of standards, and aggregation, where additional scores/variables are given to each poll to reflect their accuracy, transparency and bias levels with regards to polling scores [@5381].
 
 The measurement process involves several sequential steps, beginning with initial data collection where pollsters conduct surveys using various modes such as phone, online, or mixed-mode approaches to gather voter preferences.
-Sample processing follows, involving likely voter screens to identify probable voters, demographic weighting to match population benchmarks, and various adjustments to ensure representativeness.
+Sample processing follows, involving likely voter screens to identify probable voters, demographic weighting to match population benchmarks, and various adjustments to ensure representativeness [@quinnipiac; @newyorktimes].
 
@@
 Scientific sampling methods attempting to achieve representative samples are mandatory, as is the disclosure of poll sponsorship and funding sources.
-The dataset explicitly excludes non-scientific polls lacking representative sampling, MRP-smoothed data, recontact surveys, DIY polls from nonprofessional sources, polls with leading questions or hypothetical matchups, and subsamples from multi-state polls without geographic verification.
+The dataset explicitly excludes non-scientific polls lacking representative sampling, MRP-smoothed data, recontact surveys, DIY polls from nonprofessional sources, polls with leading questions or hypothetical matchups, and subsamples from multi-state polls without geographic verification [@5382].
 
-The aggregation phase, finally, involves rating polls by pollster polling quality (ranging from 0.5 to 3.0 stars), with polls with higher historical accuracy, lower consistent partisan biases, and higher transparency of methodology boasting higher ratings.
-FiveThirtyEight then applies quality adjustments, including house effects corrections for systematic pollster biases, mode effects adjustments for sampling method biases, population adjustments between likely and registered voters, third-party candidate inclusion effects, and partisan poll adjustments.
+The aggregation phase, finally, involves rating polls by pollster polling quality (ranging from 0.5 to 3.0 stars), with polls with higher historical accuracy, lower consistent partisan biases, and higher transparency of methodology boasting higher ratings [@5383].
+Transparency is also a rating and is done through a 10-question yes/no checklist on how much of the methodology is available to the public - note how this is completely separate from the quality of the methodology itself.
+Each question is graded on a 0/0.5/1 scale, for a combined transparency score that ranges from 0 to 10.
+Most polls in our dataset miss the mark on one or two criteron, netting a final transparency score of 9 - this is partially due to the data cleaning process removing many relatively worsely conducted polls.
 
@@
 These include temporal gaps between polls creating discontinuous measurement of voter sentiment, response rates and participation biases potentially skewing samples, and varying geographic coverage with swing states being overrepresented.
-Additionally, third-party candidate treatment varies across polls, while house effects and mode effects corrections rely on historical patterns that may not hold true in current contexts.
+Additionally, third-party candidate treatment varies across polls, and is difficult to standardise (with respect to other data points) consistently.
 

### 2024-11-04 paper/paper.qmd
updated paper and references

@@
 library(stringr)
+library(gt)
 ```
@@
 The predictor variables that we ended up using in our final logistic regression model were the poll end dates, transparency score, and sample sizes of the polls, as well as whether or not a poll was sponsored.
-The distributions of the variables is as follows:
+The poll end dates were included to capture the temporal changes in candidates' support rate.
+Transparency score was selected as an identification of the polls' trustworthiness, which must be controlled for in the analysis.
+Other variables representing the poll quality in the raw dataset, such as the poll score and the FiveThirtyEight rating, were excluded from the models for two reasons.
+First, the documentation by FiveThirtyEight suggests that the numeric rating, poll score, and transparency score are highly related [@5382].
+Second, the data cleaning process filtered data points with high FiveThirtyEight ratings and poll scores.
+The distributions of selected variables are as follows:
 
@@
 
-The goal of our modelling strategy is twofold. Firstly,...
+The goal of our modelling strategy is twofold.
+Firstly, we seek to predict the winning candidate on election day by calculating the expected win rate of Vice President Kamala Harris and Former President Donald Trump in the seven swing states: Pennsylvania, Georgia, North Carolina, Michigan, Arizona, Wisconsin, and Nevada [@nyt2024polls].
+Secondly, we hope to predict the candidate who has the popular vote on election day, controlling for the potential bias of national polls by accounting for the difference between polled popular vote and the actual popular vote on election day for the 2020 cycle.
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+To achieve the first goal, the polls dataset was divided by individual states, and only data points from the seven swing states were selected, forming seven smaller datasets.
+Then, for each state, the harris_win variable was constructed by comparing the support rate of the candidates in each poll.
+The variable was set to 1 if the support rate of Harris is greater than or equal to Trump's support rate and 0 when Trump's support rate is greater.
+A logistic model was constructed for each state, using harris_win as the outcome and previously stated predictors as inputs.
+[EXPLAIN THE PROBABILITY STEP HERE]
+
+For the popular vote, we utilized the data from 2020 to calculate each pollster's bias by identifying the average difference between the popular vote on election day and their polled national support rates of Trump and President Joe Biden.
+Next, we adjusted the polled national support rates of pollsters in the 2024 cycle by the calculated gap in 2020.
+By making this adjustment, we are assuming that the pollsters systematically bias 2024 candidates equally compared to 2020 candidates.
+We acknowledge that the assumption is most likely false.
+Ideally, incorporating poll data from earlier election cycles may produce a more accurate indicator of how pollsters systematically bias candidates from the two dominant political parties.
+However, comprehensive poll data before 2020 is unavailable.
+Since popular vote is unrelated to the winner of the election, we are using this analysis as an exploration of methods that incorporate historical data without emphasizing predictiveness.
+Using both adjusted and unadjusted national support levels, multiple linear regressions were created with support levels as the outcome and stated predictors as inputs to predict candidates' support rate over time.
+Adjusted and unadjusted logistic regressions were made using harris_win as the outcome and the same predictors to predict the candidate with the popular vote on election day.
+The attempt to control for historical bias was not applied to the swing states due to a lack of data.
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+### Logistic models
+Define $y_i$ as the binary outcome variable indicating whether Harris wins (1) or not (0) for the $i^{th}$ observation.
+$x_{1i}$ is the end_date for the $i^{th}$ observation.
+$x_{2i}$ is the binary value of has_sponsor for the $i^{th}$ observation.
+$x_{3i}$ is the transparency_score for the $i^{th}$ observation.
+$x_{4i}$ is the sample_size for the $i^{th}$ observation.
 
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
+The logistic regression model can be expressed as follows:
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+\begin{align} y_i &\sim \text{Bernoulli}(p_i) 
+\\ \text{logit}(p_i) &= \beta_0 + \beta_1 x_{1i} + \beta_2 x_{2i} + \beta_3 x_{3i} + \beta_4 x_{4i} \end{align}
+
+Line (1) specifies that the outcome variable $y_i$ follows a Bernoulli distribution with probability $p_i$ of success (i.e., Harris winning).
+Line (2) links the linear combination of predictors to the probability $p_i$, where $\beta_0$ is the intercept term, and $\beta_1, \beta_2, \beta_3, \beta_4$ are coefficients corresponding to each predictor variable above.
+
+This logistic regression model was applied independently to the data on each swing state and the adjusted and unadjusted popular vote polls.
+
+### Multiple linear regression models
+Define $y_i$ as the percentage national support for Harris or Trump for the $i^{th}$ observation.
+$x_{1i}$ is the end_date for the $i^{th}$ observation.
+$x_{2i}$ is the binary value of has_sponsor for the $i^{th}$ observation.
+$x_{3i}$ is the transparency_score for the $i^{th}$ observation.
+$x_{4i}$ is the sample_size for the $i^{th}$ observation.
+
+The multiple linear regression model can be expressed as follows:
+
+\begin{align} y_i &= \beta_0 + \beta_1 x_{1i} + \beta_2 x_{2i} + \beta_3 x_{3i} + \beta_4 x_{4i} \end{align}
+
+Where $\beta_0$ is the intercept term, and $\beta_1, \beta_2, \beta_3, \beta_4$ are coefficients corresponding to each predictor variable.
+
+Separate multiple linear regression models were applied to the polled national support rate of Harris and Trump, with and without adjustments from historical data.
 
@@
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+We decided to use a logistic model to predict the winner on election day because it directly outputs candidates' chance of winning each swing state, enabling us to use a probabilistic function to identify their overall chance of winning.
+Comparatively, a linear regression model merely predicts the level of support for candidates, which fails to identify a winner.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+
+# Regional polls analysis
+trump_2024_regional <- trump_2024_lower %>% filter(state != "National")
+harris_2024_regional <- harris_2024_lower %>% filter(state != "National")
+
+trump_Pennsylvania <- trump_2024_regional %>% filter(state == "Pennsylvania")
+trump_Georgia <- trump_2024_regional %>% filter(state == "Georgia")
+trump_North_Carolina <- trump_2024_regional %>% filter(state == "North Carolina")
+trump_Michigan <- trump_2024_regional %>% filter(state == "Michigan")
+trump_Arizona <- trump_2024_regional %>% filter(state == "Arizona")
+trump_Wisconsin <- trump_2024_regional %>% filter(state == "Wisconsin")
+trump_Nevada <- trump_2024_regional %>% filter(state == "Nevada")
+
+harris_Pennsylvania <- harris_2024_regional %>% filter(state == "Pennsylvania")
+harris_Georgia <- harris_2024_regional %>% filter(state == "Georgia")
+harris_North_Carolina <- harris_2024_regional %>% filter(state == "North Carolina")
+harris_Michigan <- harris_2024_regional %>% filter(state == "Michigan")
+harris_Arizona <- harris_2024_regional %>% filter(state == "Arizona")
+harris_Wisconsin <- harris_2024_regional %>% filter(state == "Wisconsin")
+harris_Nevada <- harris_2024_regional %>% filter(state == "Nevada")
+
+combined_Pennsylvania <- full_join(
+  trump_Pennsylvania,
+  harris_Pennsylvania,
+  by = c("pollster", "has_sponsor", "pollscore", 
+         "transparency_score", "sample_size", "end_date", "state", "cycle")
+)
+
+combined_Georgia <- full_join(
+  trump_Georgia,
+  harris_Georgia,
+  by = c("pollster", "has_sponsor", "pollscore", 
+         "transparency_score", "sample_size", "end_date", "state", "cycle")
+)
+
+combined_North_Carolina <- full_join(
+  trump_North_Carolina,
+  harris_North_Carolina,
+  by = c("pollster", "has_sponsor", "pollscore", 
+         "transparency_score", "sample_size", "end_date", "state", "cycle")
+)
+
+combined_Michigan <- full_join(
+  trump_Michigan,
+  harris_Michigan,
+  by = c("pollster", "has_sponsor", "pollscore", 
+         "transparency_score", "sample_size", "end_date", "state", "cycle")
+)
+
+combined_Arizona <- full_join(
+  trump_Arizona,
+  harris_Arizona,
+  by = c("pollster", "has_sponsor", "pollscore", 
+         "transparency_score", "sample_size", "end_date", "state", "cycle")
+)
+
+combined_Wisconsin <- full_join(
+  trump_Wisconsin,
+  harris_Wisconsin,
+  by = c("pollster", "has_sponsor", "pollscore", 
+         "transparency_score", "sample_size", "end_date", "state", "cycle")
+)
+
+combined_Nevada <- full_join(
+  trump_Nevada,
+  harris_Nevada,
+  by = c("pollster", "has_sponsor", "pollscore", 
+         "transparency_score", "sample_size", "end_date", "state", "cycle")
+)
+
+# mutate harris_win variable by comparing polled support rates
+# preparing data for logistic regression
+combined_Pennsylvania <- combined_Pennsylvania %>% mutate(
+  harris_win = case_when(
+    pct.y >= pct.x ~ 1,
+    pct.y < pct.x ~ 0
+  )
+)
+
+combined_Georgia <- combined_Georgia %>% mutate(
+  harris_win = case_when(
+    pct.y >= pct.x ~ 1,
+    pct.y < pct.x ~ 0
+  )
+)
+
+combined_North_Carolina <- combined_North_Carolina %>% mutate(
+  harris_win = case_when(
+    pct.y >= pct.x ~ 1,
+    pct.y < pct.x ~ 0
+  )
+)
+
+combined_Michigan <- combined_Michigan %>% mutate(
+  harris_win = case_when(
+    pct.y >= pct.x ~ 1,
+    pct.y < pct.x ~ 0
+  )
+)
+
+combined_Arizona <- combined_Arizona %>% mutate(
+  harris_win = case_when(
+    pct.y >= pct.x ~ 1,
+    pct.y < pct.x ~ 0
+  )
+)
+
+combined_Wisconsin <- combined_Wisconsin %>% mutate(
+  harris_win = case_when(
+    pct.y >= pct.x ~ 1,
+    pct.y < pct.x ~ 0
+  )
+)
+
+combined_Nevada <- combined_Nevada %>% mutate(
+  harris_win = case_when(
+    pct.y >= pct.x ~ 1,
+    pct.y < pct.x ~ 0
+  )
+)
+
+# Create 7 different logistic regressions to predict Harris's win rate
+# in each state
+logistic_Pennsylvania <- readRDS(here::here("models/Logistic_model_Pennsylvania.rds"))
+
+logistic_Georgia <- readRDS(here::here("models/Logistic_model_Georgia.rds"))
+
+logistic_North_Carolina <- readRDS(here::here("models/Logistic_model_North_Carolina.rds"))
+
+logistic_Michigan <- readRDS(here::here("models/Logistic_model_Michigan.rds"))
+
+logistic_Arizona <- readRDS(here::here("models/Logistic_model_Arizona.rds"))
+
+logistic_Wisconsin <- readRDS(here::here("models/Logistic_model_Wisconsin.rds"))
+
+logistic_Nevada <- readRDS(here::here("models/Logistic_model_Nevada.rds"))
+
+# test logistic models for state specific analysis
+# mutate fitted values
+
+combined_Pennsylvania <- combined_Pennsylvania %>%
+  mutate(
+    harris_win_prob = round(100*predict(logistic_Pennsylvania, type = "response"), 2)
+  )
+
+roc_obj_Pennsylvania <- roc(combined_Pennsylvania$harris_win,
+                  combined_Pennsylvania$harris_win_prob)
+
+auc_value_Pennsylvania <- auc(roc_obj_Pennsylvania)
+
+combined_Georgia <- combined_Georgia %>%
+  mutate(
+    harris_win_prob = round(100*predict(logistic_Georgia, type = "response"), 2)
+  )
+
+roc_obj_Georgia <- roc(combined_Georgia$harris_win,
+                            combined_Georgia$harris_win_prob)
+
+auc_value_Georgia <- auc(roc_obj_Georgia)
+
+combined_North_Carolina <- combined_North_Carolina %>%
+  mutate(
+    harris_win_prob = round(100*predict(logistic_North_Carolina, type = "response"), 2)
+  )
+
+roc_obj_North_Carolina <- roc(combined_North_Carolina$harris_win,
+                            combined_North_Carolina$harris_win_prob)
+
+auc_value_North_Carolina <- auc(roc_obj_North_Carolina)
+
+combined_Michigan <- combined_Michigan %>%
+  mutate(
+    harris_win_prob = round(100*predict(logistic_Michigan, type = "response"), 2)
+  )
+
+roc_obj_Michigan <- roc(combined_Michigan$harris_win,
+                            combined_Michigan$harris_win_prob)
+
+auc_value_Michigan <- auc(roc_obj_Michigan)
+
+combined_Arizona <- combined_Arizona %>%
+  mutate(
+    harris_win_prob = round(100*predict(logistic_Arizona, type = "response"), 2)
+  )
+
+roc_obj_Arizona <- roc(combined_Arizona$harris_win,
+                            combined_Arizona$harris_win_prob)
+
+auc_value_Arizona <- auc(roc_obj_Arizona)
+
+combined_Wisconsin <- combined_Wisconsin %>%
+  mutate(
+    harris_win_prob = round(100*predict(logistic_Wisconsin, type = "response"), 2)
+  )
+
+roc_obj_Wisconsin <- roc(combined_Wisconsin$harris_win,
+                            combined_Wisconsin$harris_win_prob)
+
+auc_value_Wisconsin <- auc(roc_obj_Wisconsin)
+
+combined_Nevada <- combined_Nevada %>%
+  mutate(
+    harris_win_prob = round(100*predict(logistic_Nevada, type = "response"), 2)
+  )
+
+roc_obj_Nevada <- roc(combined_Nevada$harris_win,
+                            combined_Nevada$harris_win_prob)
+
+auc_value_Nevada <- auc(roc_obj_Nevada)
+
+```
+
+We identified the AUC values and ROC plots for each of the seven swing-state logistic regressions.
+The ROC plots are presented in the Appendix, from @fig-pen to @fig-nev.
+The AUC values are: 0.90 for Pennsylvania, 0.88 for Georgia, 0.74 for North Carolina, 0.93 for Michigan, 1.00 for Arizona, 0.86 for Wisconsin, and 0.65 for Nevada.
+All states other than Nevada have acceptable or excellent AUC values, indicating that the respective logistic models are reliable when distinguishing cases where Harris wins.
+The low AUC value for Nevada is potentially caused by the limited sample size; there are only 9 polls conducted in Nevada.
+
+Moreover, the sample size restrictions were the reason why we did not use training and testing data to validate our logistic models.
+The state with the greatest number of polls, Pennsylvania, only records 26 polls.
+Utilizing training and testing datasets implies that the datasets may include only a couple of data points in some states, which is insufficient to construct or test the model.
+On top of that, according to [@trainingerror], achieving low training error is sufficient to ensure the predictability of a model to some extent.
+[ADD MORE IF NECESSARY]
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+
+# find biases of pollsters from 2020 national polls data
+# filter out national polls from the datasets
+trump_2024_national <- trump_2024 %>% filter(state == "National")
+harris_2024_national <- harris_2024 %>% filter(state == "National")
+trump_2020_national <- trump_2020 %>% filter(state == "National")
+biden_2020_national <- biden_2020 %>% filter(state == "National")
+
+# Define actual results
+actual_results_2020 <- list(Trump_pct = 47, Biden_pct = 51)
+
+# Calculate bias per pollster
+rep_pollster_bias <- trump_2020_national %>%
+  group_by(pollster) %>%
+  summarize(
+    Trump_bias = mean(pct - actual_results_2020$Trump_pct, na.rm = TRUE)
+  )
+
+dem_pollster_bias <- biden_2020_national %>%
+  group_by(pollster) %>%
+  summarize(
+    Biden_bias = mean(pct - actual_results_2020$Biden_pct, na.rm = TRUE)
+  )
+
+# adjust 2024 national polls percentages by the average pollster biases
+# also mutate has_sponsor variable into dummy variable and remove NA's
+trump_2024_national_adj <- trump_2024_national %>%
+  left_join(rep_pollster_bias, by = "pollster") %>%
+  mutate(
+    pct_adj = pct - ifelse(!is.na(Trump_bias), Trump_bias, 0)
+  ) %>%
+  select(-Trump_bias)
+
+# Adjust Harris 2024 National Polls
+harris_2024_national_adj <- harris_2024_national %>%
+  left_join(dem_pollster_bias, by = "pollster") %>%
+  mutate(
+    pct_adj = pct - ifelse(!is.na(Biden_bias), Biden_bias, 0)
+  ) %>%
+  select(-Biden_bias)
+
+# model adjusted support percentage by time and control variables
+# first split training and testing dataset using an 80/20 split
+set.seed(11451)
+trainIndex_trump_adj <- createDataPartition(trump_2024_national_adj$pct_adj, 
+                                        p = 0.8, list = FALSE)
+data_train_trump_adj <- trump_2024_national_adj[trainIndex_trump_adj, ]
+data_test_trump_adj  <- trump_2024_national_adj[-trainIndex_trump_adj, ]
+
+trainIndex_harris_adj <- createDataPartition(harris_2024_national_adj$pct_adj, 
+                                         p = 0.8, list = FALSE)
+data_train_harris_adj <- harris_2024_national_adj[trainIndex_harris_adj, ]
+data_test_harris_adj  <- harris_2024_national_adj[-trainIndex_harris_adj, ]
+
+model_date_harris_adj <- lm(pct_adj ~ end_date + has_sponsor +
+                          transparency_score + sample_size, data = data_train_harris_adj)
+model_date_trump_adj <- lm(pct_adj ~ end_date + has_sponsor +
+                         transparency_score + sample_size, data = data_train_trump_adj)
+
+# repeat for unadjusted support levels
+trainIndex_trump <- createDataPartition(trump_2024_national$pct, 
+                                        p = 0.8, list = FALSE)
+data_train_trump <- trump_2024_national[trainIndex_trump, ]
+data_test_trump  <- trump_2024_national[-trainIndex_trump, ]
+
+trainIndex_harris <- createDataPartition(harris_2024_national$pct, 
+                                         p = 0.8, list = FALSE)
+data_train_harris <- harris_2024_national[trainIndex_harris, ]
+data_test_harris  <- harris_2024_national[-trainIndex_harris, ]
+
+model_date_harris <- lm(pct ~ end_date + has_sponsor +
+                          transparency_score + sample_size, data = data_train_harris)
+model_date_trump <- lm(pct ~ end_date + has_sponsor +
+                         transparency_score + sample_size, data = data_train_trump)
+
+# Functions to evaluate model using testing dataset
+evaluate_model_adj <- function(model, test_data) {
+  predictions <- predict(model, newdata = test_data)
+  actuals <- test_data$pct_adj
+  rmse <- sqrt(mean((predictions - actuals)^2, na.rm = TRUE))
+  r_squared <- summary(model)$r.squared
+  return(list(RMSE = rmse, R_squared = r_squared))
+}
+
+evaluate_model <- function(model, test_data) {
+  predictions <- predict(model, newdata = test_data)
+  actuals <- test_data$pct
+  rmse <- sqrt(mean((predictions - actuals)^2, na.rm = TRUE))
+  r_squared <- summary(model)$r.squared
+  return(list(RMSE = rmse, R_squared = r_squared))
+}
+
+# Evaluate Harris model with adjusted support percentages
+harris_evaluation_adj <- evaluate_model_adj(model_date_harris_adj, data_test_harris_adj)
+
+# Evaluate Trump model with adjusted support percentages
+trump_evaluation_adj <- evaluate_model_adj(model_date_trump_adj, data_test_trump_adj)
+
+# Evaluate Harris model with unadjusted support percentages
+harris_evaluation <- evaluate_model(model_date_harris, data_test_harris)
+
+# Evaluate Trump model with unadjusted support percentages
+trump_evaluation <- evaluate_model(model_date_trump, data_test_trump)
+
+# Augment data with model predictions
+model_harris_adj <- readRDS(here::here("models/MLR_adjusted_harris.rds"))
+model_trump_adj <- readRDS(here::here("models/MLR_adjusted_trump.rds"))
+
+harris_2024_national_adj <- harris_2024_national_adj %>% mutate(
+  fitted_date = predict(model_harris_adj)
+)
+
+trump_2024_national_adj <- trump_2024_national_adj %>% mutate(
+  fitted_date = predict(model_trump_adj)
+)
+
+# Unadjusted datasets
+model_harris <- readRDS(here::here("models/MLR_harris.rds"))
+model_trump <- readRDS(here::here("models/MLR_trump.rds"))
+
+harris_2024_national <- harris_2024_national %>% mutate(
+  fitted_date = predict(model_harris)
+)
+
+trump_2024_national <- trump_2024_national %>% mutate(
+  fitted_date = predict(model_trump)
+)
+
+# evaluate models without using training and testing data
+harris_eval_adj <- evaluate_model_adj(model_harris_adj, harris_2024_national_adj)
+
+harris_eval <- evaluate_model(model_harris, harris_2024_national)
+
+trump_eval_adj <- evaluate_model_adj(model_trump_adj, trump_2024_national_adj)
+
+trump_eval <- evaluate_model(model_trump, trump_2024_national)
+
+#### Logistic regression for national support ####
+
+combined_national <- full_join(
+  trump_2024_national,
+  harris_2024_national,
+  by = c("pollster", "has_sponsor", "pollscore", 
+         "transparency_score", "sample_size", "end_date", "state", "cycle")
+)
+
+combined_national <- combined_national %>% mutate(
+  harris_win = case_when(
+    pct.y >= pct.x ~ 1,
+    pct.y < pct.x ~ 0
+  )
+)
+
+# repeat for adjusted support levels
+combined_national_adj <- full_join(
+  trump_2024_national_adj,
+  harris_2024_national_adj,
+  by = c("pollster", "has_sponsor", "pollscore",
+         "transparency_score", "sample_size", "end_date", "state", "cycle")
+)
+
+combined_national_adj <- combined_national_adj %>% mutate(
+  harris_win = case_when(
+    pct_adj.y >= pct_adj.x ~ 1,
+    pct_adj.y < pct_adj.x ~ 0
+  )
+)
+
+# logistic model to predict the popular vote
+model_logistic <- readRDS(here::here("models/Logistic_model.rds"))
+
+model_logistic_adj <- readRDS(here::here("models/Logistic_model_adjusted.rds"))
+
+# include predicted outcomes to the dataframes
+combined_national <- combined_national %>%
+  mutate(
+    harris_win_prob = round(100*predict(model_logistic, type = "response"), 2)
+  )
+
+combined_national_adj <- combined_national_adj %>%
+  mutate(
+    harris_win_prob = round(100*predict(model_logistic_adj, 
+                                        type = "response"), 2)
+  )
+
+#### Evaluate the Model ####
+
+# ROC Curve and AUC
+roc_obj <- roc(combined_national$harris_win,
+               combined_national$harris_win_prob)
+auc_value <- auc(roc_obj)
+
+roc_obj_adj <- roc(combined_national_adj$harris_win,
+               combined_national_adj$harris_win_prob)
+auc_value_adj <- auc(roc_obj_adj)
+```
+For the analysis of the national popular vote, the logistic model of adjusted polls possess an AUC value of 0.98, and the logistic model of unadjusted polls have an AUC of 0.94, indicating high reliability of categorization.
+Their respective ROC plots are presented as @fig-log and @fig-logadj.
+
+RMSE values and R squared values were calculated for the multiple linear regression models predicting popular vote.
+The RMSE values for all four models, adjusted and unadjusted support levels of the two candidates, are greater than 1, indicating that the fitted values and the support levels of actual polls are more than 1 percent apart on average, which is significant when analyzing popular vote.
+Moreover, all R squared values other than the model for the adjusted support rate of Trump, are smaller than 0.3, indicating the inability of the models to account for the variance of national support rates in the data.
+The model for the adjusted support rate of Trump has a R squared value of 0.69, indicating a relatively high proportion of variance in polled support rates being explained by the multiple linear regression model.
+This was expected, as the predictors such as a poll's end date and transparency does not necessarily correlate with the outcome of the polls.
+More predictive variables used by FiveThirtyEight [@5383] for their predictions are unavailable in the raw dataset, which is a key limitation of the data.
 
@@
 ```{r}
+# plot model predictions
+# combine the datasets to create a single visual
+combined_data_adj <- bind_rows(harris_2024_national_adj, trump_2024_national_adj)
+combined_data <- bind_rows(harris_2024_national, trump_2024_national)
+
+# create the plot that contains scattered points of adjusted percentages
+# and lines for fitted values
+ggplot(combined_data_adj, aes(x = end_date, y = pct_adj, color = candidate_name)) +
+  # Scatter points for actual adjusted percentages
+  geom_point(alpha = 0.6) +
+  # Regression lines
+  geom_line(aes(y = fitted_date), size = 0.5) +
+  xlim(as.Date("2024-07-19"), as.Date("2024-10-25")) +
+  # Assign specific colors
+  scale_color_manual(values = 
+                       c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
+  # Customize the plot appearance
+  theme_classic() +
+  labs(
+    y = "Adjusted Percent Support",
+    x = "End Date",
+    title = "Multiple Linear Models for Harris and Trump (2024)",
+    color = "Candidate"
+  ) +
+  theme(
+    text = element_text(size = 12),
+    plot.title = element_text(hjust = 0.5, face = "bold")
+  )
+
+# Unadjusted support percentages
+ggplot(combined_data, aes(x = end_date, y = pct, color = candidate_name)) +
+  # Scatter points for actual adjusted percentages
+  geom_point(alpha = 0.6) +
+  # Regression lines
+  geom_line(aes(y = fitted_date), size = 0.5) +
+  xlim(as.Date("2024-07-19"), as.Date("2024-10-25")) +
+  # Assign specific colors
+  scale_color_manual(values = 
+                       c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
+  # Customize the plot appearance
+  theme_classic() +
+  labs(
+    y = "Adjusted Percent Support",
+    x = "End Date",
+    title = "Multiple Linear Models for Harris and Trump (2024)",
+    color = "Candidate"
+  ) +
+  theme(
+    text = element_text(size = 12),
+    plot.title = element_text(hjust = 0.5, face = "bold")
+  )
 
@@
 ```{r}
-
+summary(model_logistic)
+summary(model_logistic_adj)
 ```
@@
 
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+## Diagnostics
 
 ```{r}
+#| label: fig-pen
+#| fig-cap: ROC Curve for Harris Win Prediction, Pennsylvania
+#| echo: false
+#| message: false
+#| warning: false
+
+plot(roc_obj_Pennsylvania)
 
@@
 
-## Diagnostics
+```{r}
+#| label: fig-geo
+#| fig-cap: ROC Curve for Harris Win Prediction, Georgia
+#| echo: false
+#| message: false
+#| warning: false
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
+plot(roc_obj_Georgia)
 
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+```
 
 ```{r}
+#| label: fig-nor
+#| fig-cap: ROC Curve for Harris Win Prediction, North Carolina
+#| echo: false
+#| message: false
+#| warning: false
+
+plot(roc_obj_North_Carolina)
+
+```
+
+```{r}
+#| label: fig-mic
+#| fig-cap: ROC Curve for Harris Win Prediction, Michigan
+#| echo: false
+#| message: false
+#| warning: false
+
+plot(roc_obj_Michigan)
+
+```
+
+```{r}
+#| label: fig-ari
+#| fig-cap: ROC Curve for Harris Win Prediction, Arizona
+#| echo: false
+#| message: false
+#| warning: false
+
+plot(roc_obj_Arizona)
+
+```
+
+```{r}
+#| label: fig-wis
+#| fig-cap: ROC Curve for Harris Win Prediction, Wisconsin
+#| echo: false
+#| message: false
+#| warning: false
+
+plot(roc_obj_Wisconsin)
+
+```
+
+```{r}
+#| label: fig-nev
+#| fig-cap: ROC Curve for Harris Win Prediction, Nevada
+#| echo: false
+#| message: false
+#| warning: false
+
+plot(roc_obj_Nevada)
+
+```
+
+```{r}
+#| label: fig-log
+#| fig-cap: ROC Curve for Popular Vote Prediction
+#| echo: false
+#| message: false
+#| warning: false
+
+plot(roc_obj)
+
+```
+
+```{r}
+#| label: fig-logadj
+#| fig-cap: ROC Curve for Popular Vote Prediction, Adjusted
+#| echo: false
+#| message: false
+#| warning: false
+
+plot(roc_obj)
 

### 2024-11-04 scripts/05-model_data.R
updated code

@@ -18,6 +18,7 @@ library(nnet)
 library(lubridate)
 library(pROC)
 library(stringr)
+library(gt)
 
 
 #### Read data ####
@@ -160,8 +161,6 @@ trump_2024_national_adj <- trump_2024_national_adj %>% mutate(
 # Unadjusted datasets
 model_harris <- lm(pct ~ end_date + has_sponsor +
                          transparency_score + sample_size, data = harris_2024_national)
-model_trump <- lm(pct ~ end_date + has_sponsor +
-                        transparency_score + sample_size, data = trump_2024_national)
 
 harris_2024_national <- harris_2024_national %>% mutate(
   fitted_date = predict(model_harris)
@@ -816,3 +815,89 @@ mean_probabilities %>%
     table.border.top.width = px(2),
     table.border.bottom.width = px(2)
   ) 
+
+#### Overall Probability of Winning ####
+# Harris
+# Create data frame of states
+states <- data.frame(
+  state = c("PA", "GA", "NC", "MI", "WI", "NV", "AZ"),
+  prob = c(0.5551, 0.6801, 0.1033, 0.5151, 0.3792, 0.7679, 0),
+  votes = c(20, 16, 15, 16, 10, 6, 11)
+)
+
+# Function to calculate probability of a specific combination
+calc_combo_prob <- function(combo, states) {
+  prob <- 1
+  for(i in 1:nrow(states)) {
+    if(i %in% combo) {
+      prob <- prob * states$prob[i]
+    } else {
+      prob <- prob * (1 - states$prob[i])
+    }
+  }
+  return(prob)
+}
+
+# Generate all possible combinations
+n_states <- nrow(states)
+total_prob <- 0
+
+# Check each possible combination
+for(i in 1:(2^n_states - 1)) {
+  # Convert number to binary to get combination
+  combo <- which(intToBits(i)[1:n_states] == 1)
+  
+  # Calculate total electoral votes for this combination
+  votes <- sum(states$votes[combo])
+  
+  # If this combination has enough votes, add its probability
+  if(votes >= 44) {
+    prob <- calc_combo_prob(combo, states)
+    total_prob <- total_prob + prob
+  }
+}
+
+print(paste("Probability of Harris winning at least 44 electoral votes:", round(total_prob * 100, 2), "%"))
+
+# Trump
+# Create data frame of states
+states <- data.frame(
[…]

### 2024-11-04 paper/paper.qmd
updated paper

@@
 library(gt)
+library(broom)
+library(knitr)
 ```
@@
 The aggregated polling data includes support percentages of different presidential candidates in polls with different FiveThirtyEight ratings [@5382] across two elections.
-Please view [UPDATE APPENDIX] for summary statistics of sub-datasets.
 
@@
 A logistic model was constructed for each state, using harris_win as the outcome and previously stated predictors as inputs.
-[EXPLAIN THE PROBABILITY STEP HERE]
+[EXPLAIN THE 1000 simulations and PROBABILITY calculation STEP HERE]
 
@@
 
-Our results are summarized in @tbl-modelresults.
-
-```{r}
+## Swing states
+
+@tbl-result shows the average likelihood percentage of Harris winning each swing state, calculated by using the logistic model on 1,000 hypothetical data points for each state, generated with the normal distribution of predictors and setting the end_date to election day.
+It indicates that Harris has a greater probability to win in Pennsylvania, Georgia, and Nevada, while Trump is more likely to win in North Carolina, Michigan, Arizona, and Wisconsin.
+The electoral votes in each state is also presented.
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+
+#### Results ####
+# To predict the outcome on election day, generate 1000 hypothetical data points
+# using the election day as end_date and the normal curve of other input 
+# variables, mimicing all the situations that may happen on election day
+hypothetical_data_Pennsylvania <- tibble(
+  end_date = as.Date("2024-11-05"),
+  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Pennsylvania$has_sponsor)),
+  transparency_score = rnorm(1000, mean = mean(combined_Pennsylvania$transparency_score), 
+                             sd = sd(combined_Pennsylvania$transparency_score)),
+  sample_size = rnorm(1000, mean = mean(combined_Pennsylvania$sample_size),
+                      sd = sd(combined_Pennsylvania$sample_size))
+)
+
+hypothetical_data_Georgia <- tibble(
+  end_date = as.Date("2024-11-05"),
+  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Georgia$has_sponsor)),
+  transparency_score = rnorm(1000, mean = mean(combined_Georgia$transparency_score), 
+                             sd = sd(combined_Georgia$transparency_score)),
+  sample_size = rnorm(1000, mean = mean(combined_Georgia$sample_size),
+                      sd = sd(combined_Georgia$sample_size))
+)
+
+hypothetical_data_North_Carolina <- tibble(
+  end_date = as.Date("2024-11-05"),
+  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_North_Carolina$has_sponsor)),
+  transparency_score = rnorm(1000, mean = mean(combined_North_Carolina$transparency_score), 
+                             sd = sd(combined_North_Carolina$transparency_score)),
+  sample_size = rnorm(1000, mean = mean(combined_North_Carolina$sample_size),
+                      sd = sd(combined_North_Carolina$sample_size))
+)
+
+hypothetical_data_Michigan <- tibble(
+  end_date = as.Date("2024-11-05"),
+  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Michigan$has_sponsor)),
+  transparency_score = rnorm(1000, mean = mean(combined_Michigan$transparency_score), 
+                             sd = sd(combined_Michigan$transparency_score)),
+  sample_size = rnorm(1000, mean = mean(combined_Michigan$sample_size),
+                      sd = sd(combined_Michigan$sample_size))
+)
+
+hypothetical_data_Arizona <- tibble(
+  end_date = as.Date("2024-11-05"),
+  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Arizona$has_sponsor)),
+  transparency_score = rnorm(1000, mean = mean(combined_Arizona$transparency_score), 
+                             sd = sd(combined_Arizona$transparency_score)),
+  sample_size = rnorm(1000, mean = mean(combined_Arizona$sample_size),
+                      sd = sd(combined_Arizona$sample_size))
+)
+
+hypothetical_data_Wisconsin <- tibble(
+  end_date = as.Date("2024-11-05"),
+  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Wisconsin$has_sponsor)),
+  transparency_score = rnorm(1000, mean = mean(combined_Wisconsin$transparency_score), 
+                             sd = sd(combined_Wisconsin$transparency_score)),
+  sample_size = rnorm(1000, mean = mean(combined_Wisconsin$sample_size),
+                      sd = sd(combined_Wisconsin$sample_size))
+)
+
+hypothetical_data_Nevada <- tibble(
+  end_date = as.Date("2024-11-05"),
+  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Nevada$has_sponsor)),
+  transparency_score = rnorm(1000, mean = mean(combined_Nevada$transparency_score), 
+                             sd = sd(combined_Nevada$transparency_score)),
+  sample_size = rnorm(1000, mean = mean(combined_Nevada$sample_size),
+                      sd = sd(combined_Nevada$sample_size))
+)
+
+# run the corresponding logistic regression on the hypothetical data of each
+# state and average the outcomes to find the expected win rate of Harris
+# on election day
+hypothetical_data_Pennsylvania <- hypothetical_data_Pennsylvania %>%
+  mutate(
+    harris_win_prob = round(100*predict(logistic_Pennsylvania, newdata = ., type = "response"), 2)
+  )
+
+hypothetical_data_Georgia <- hypothetical_data_Georgia %>%
+  mutate(
+    harris_win_prob = round(100*predict(logistic_Georgia, newdata = ., type = "response"), 2)
+  )
+
+hypothetical_data_North_Carolina <- hypothetical_data_North_Carolina %>%
+  mutate(
+    harris_win_prob = round(100*predict(logistic_North_Carolina, newdata = ., type = "response"), 2)
+  )
+
+hypothetical_data_Michigan <- hypothetical_data_Michigan %>%
+  mutate(
+    harris_win_prob = round(100*predict(logistic_Michigan, newdata = ., type = "response"), 2)
+  )
+
+hypothetical_data_Arizona <- hypothetical_data_Arizona %>%
+  mutate(
+    harris_win_prob = round(100*predict(logistic_Arizona, newdata = ., type = "response"), 2)
+  )
+
+hypothetical_data_Wisconsin <- hypothetical_data_Wisconsin %>%
+  mutate(
+    harris_win_prob = round(100*predict(logistic_Wisconsin, newdata = ., type = "response"), 2)
+  )
+
+hypothetical_data_Nevada <- hypothetical_data_Nevada %>%
+  mutate(
+    harris_win_prob = round(100*predict(logistic_Nevada, newdata = ., type = "response"), 2)
+  )
+
+# produce a table of mean winning probabilities
+mean_probabilities <- tibble(
+  State = c("Pennsylvania", "Georgia", "North Carolina", "Michigan", "Arizona", "Wisconsin", "Nevada"),
+  Harris_Win_Probability = c(
+    round(mean(hypothetical_data_Pennsylvania$harris_win_prob, na.rm = TRUE), 2),
+    round(mean(hypothetical_data_Georgia$harris_win_prob, na.rm = TRUE), 2),
+    round(mean(hypothetical_data_North_Carolina$harris_win_prob, na.rm = TRUE), 2),
+    round(mean(hypothetical_data_Michigan$harris_win_prob, na.rm = TRUE), 2),
+    round(mean(hypothetical_data_Arizona$harris_win_prob, na.rm = TRUE), 2),
+    round(mean(hypothetical_data_Wisconsin$harris_win_prob, na.rm = TRUE), 2),
+    round(mean(hypothetical_data_Nevada$harris_win_prob, na.rm = TRUE), 2)
+  )
+)
+
+# include electoral votes to determine who is in the lead
+state_evs <- tibble::tribble(
+  ~State, ~electoral_votes,
+  "Alaska", 3,
+  "Arizona", 11,
+  "Arkansas", 6,
+  "California", 55,
+  "Colorado", 9,
+  "Connecticut", 7,
+  "Florida", 29,
+  "Georgia", 16,
+  "Illinois", 20,
+  "Indiana", 11,
+  "Iowa", 6,
+  "Kansas", 6,
+  "Louisiana", 8,
+  "Maine", 2,
+  "Maine CD-1", 1,
+  "Maine CD-2", 1,
+  "Maryland", 10,
+  "Massachusetts", 11,
+  "Michigan", 16,
+  "Minnesota", 10,
+  "Mississippi", 6,
+  "Missouri", 10,
+  "Montana", 3,
+  "Nebraska", 2,
+  "Nebraska CD-2", 1,
+  "Nevada", 6,
+  "New Hampshire", 4,
+  "New Mexico", 5,
+  "New York", 29,
+  "North Carolina", 15,
+  "Ohio", 18,
+  "Oklahoma", 7,
+  "Oregon", 7,
+  "Pennsylvania", 20,
+  "Rhode Island", 4,
+  "South Carolina", 9,
+  "South Dakota", 3,
+  "Texas", 38,
+  "Utah", 6,
+  "Vermont", 3,
+  "Virginia", 13,
+  "Washington", 12,
+  "Wisconsin", 10
+)
+
+mean_probabilities <- mean_probabilities %>%
+  left_join(state_evs, by = "State")
+
+#### Overall Probability of Winning ####
+# Harris
+# Create data frame of states
+states <- data.frame(
+  state = c("PA", "GA", "NC", "MI", "WI", "NV", "AZ"),
+  prob = c(0.5551, 0.6801, 0.1033, 0.5151, 0.3792, 0.7679, 0),
+  votes = c(20, 16, 15, 16, 10, 6, 11)
+)
+
+# Function to calculate probability of a specific combination
+calc_combo_prob <- function(combo, states) {
+  prob <- 1
+  for(i in 1:nrow(states)) {
+    if(i %in% combo) {
+      prob <- prob * states$prob[i]
+    } else {
+      prob <- prob * (1 - states$prob[i])
+    }
+  }
+  return(prob)
+}
+
+# Generate all possible combinations
+n_states <- nrow(states)
+total_prob <- 0
+
+# Check each possible combination
+for(i in 1:(2^n_states - 1)) {
+  # Convert number to binary to get combination
+  combo <- which(intToBits(i)[1:n_states] == 1)
+
+  # Calculate total electoral votes for this combination
+  votes <- sum(states$votes[combo])
+
+  # If this combination has enough votes, add its probability
+  if(votes >= 44) {
+    prob <- calc_combo_prob(combo, states)
+    total_prob <- total_prob + prob
+  }
+}
+
+# Trump
+# Create data frame of states
+states <- data.frame(
+  state = c("PA", "GA", "NC", "MI", "WI", "NV","AZ"),
+  prob = c(1-0.5551, 1-0.6801, 1-0.1033, 1-0.5151, 1-0.3792, 1-0.7679, 1-0), # Using 1-p for Trump's probabilities
+  votes = c(20, 16, 15, 16, 10, 6, 11)
+)
+
+# Function to calculate probability of a specific combination
+calc_combo_prob <- function(combo, states) {
+  prob <- 1
+  for(i in 1:nrow(states)) {
+    if(i %in% combo) {
+      prob <- prob * states$prob[i]
+    } else {
+      prob <- prob * (1 - states$prob[i])
+    }
+  }
+  return(prob)
+}
+
+# Generate all possible combinations
+n_states <- nrow(states)
+total_prob <- 0
+
+# Check each possible combination
+for(i in 1:(2^n_states - 1)) {
+  # Convert number to binary to get combination
+  combo <- which(intToBits(i)[1:n_states] == 1)
+
+  # Calculate total electoral votes for this combination
+  votes <- sum(states$votes[combo])
+
+  # If this combination has enough votes, add its probability
+  if(votes >= 51) {
+    prob <- calc_combo_prob(combo, states)
+    total_prob <- total_prob + prob
+  }
+}
+
+```
+
+```{r}
+#| label: tbl-result
+#| tbl-cap: Predicted Harris Win Percentage in Swing States
+#| echo: false
+#| message: false
+#| warning: false
+
+mean_probabilities %>%
+  gt() %>%
+  fmt_number(
+    columns = vars(Harris_Win_Probability),
+    decimals = 2
+  ) %>%
+  cols_label(
+    State = "State",
+    Harris_Win_Probability = "Harris Win Probability (%)",
+    electoral_votes = "Electoral Votes"
+  ) %>%
+  tab_options(
+    table.font.size = 12,
+    heading.title.font.size = 16,
+    heading.subtitle.font.size = 12,
+    table.border.top.width = px(2),
+    table.border.bottom.width = px(2)
+  )
+
+```
+Combining with the fact that Harris requires 44 electoral votes to win and Trump requires 51, we have found using the probability function that Harris has a 38.3 chance to acquire more than 44 electoral votes, according to the probabilities and electoral votes in @tbl-result.
+On the other hand, Trump has a 61.7 probability to acquire more than 51 votes.
+Thus, our conclusion is that while both candidates possess a significant chance of winning, Trump has the greater probability of acquiring the necessary electoral votes from the seven swing states on election day.
+
+## Popular vote
+
+@fig-lradj presents the fitted values of the candidates' adjusted national support rates as well as the data points of polled support rates adjusted for historical pollster bias.
+It indicates that Trump is expected to have higher national support levels, but the two converges as election day approaches.
+This result is counter intuitive, as most national polls indicate that Harris will have the popular vote.
+However, the adjusted values for Trump's support level are significantly greater than the polled values because historically, the actual percentage of the popular vote for Trump in 2020 was significantly greater than his polled percentages of the popular vote.
+Thus, assuming that the 2024 national polls are equally biased against Trump compared to the 2020 polls, it is difficult to tell who will get the popular vote on election day.
+However, as previously stated, this assumption is likely false, as the candidates have changed.
+
+```{r}
+#| label: fig-lradj
+#| fig-cap: Adjusted Popular Vote Prediction, 2024
+#| echo: false
+#| message: false
+#| warning: false
 # plot model predictions
@@
     x = "End Date",
-    title = "Multiple Linear Models for Harris and Trump (2024)",
     color = "Candidate"
@@
 
+```
+
+@fig-lr Presents the predicted unadjusted national support rates for Harris and Trump.
+The conclusions one can make from this plot is similar to those of most polls: Harris is expected to win the popular vote on any day, including the election day.
+
+```{r}
+#| label: fig-lr
+#| fig-cap: Unadjusted Popular Vote Prediction, 2024
+#| echo: false
+#| message: false
+#| warning: false
 # Unadjusted support percentages
@@
 ```
-
-```{r}
-summary(model_logistic)
-summary(model_logistic_adj)
-```
+The regression coefficients for the logistic and linear models are presented in the Appendix because they are not the outcome of interest. Please view @tbl-coe1 to @tbl-coe7.
 
@@
 
-Weaknesses and next steps should also be included.
+The dataset used for this analysis has a number of clear limitations.
+First of all, there is a lack of high-quality polls.
+Though FiveThirtyEight distributes each pollster with a rating out of 3.0, almost all pollsters under the rating of 2.7 produces outcomes that are unreliable and highly volatile.
+For this research, it was only possible for us to use pollsters with a 3.0 rating when analyzing national polls; we had to lower the standards to 2.5 for the analysis of swing states, as the number of high-quality state-specific polls are very limited.
+The inclusion of unreliable data reduces the predictability of our logistic models and thus our final outcome.
+The lack of predictability of our Nevada model is a perfect example of how low-quality data and the lack of data points impacts our ability to create effective models.
+However, we acknowledge that this is beyond the control of FiveThirtyEight, as they do not conduct the polls.
+
+The second major challenge presented by the dataset is the lack of predictors.
+FiveThirtyEight utilizes predictive variables that are unavailable to us, such as weighted values that represent the extent to which a pollster is partisan [@5383].
+The predictors used in this research, such as the transparency score of the pollster, are not related to their bias towards any candidate.
+This limits the predictive power of our models.
 
@@
 ## Diagnostics
-
 ```{r}
@@
 
+## Coefficients
+
+```{r}
+#| label: tbl-coe1
+#| fig-cap: Logistic Regression Coefficients for Pennsylvania
+#| echo: false
+#| message: false
+#| warning: false
+# Tidy the logistic regression model
+tidy_Pennsylvania <- tidy(logistic_Pennsylvania)
+
+# Display the table using knitr::kable
+kable(tidy_Pennsylvania, digits = 2, 
+      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))
+
+```
+```{r}
+#| label: tbl-coe2
+#| fig-cap: Logistic Regression Coefficients for Georgia
+#| echo: false
+#| message: false
+#| warning: false
+# Tidy the logistic regression model
+tidy_Georgia <- tidy(logistic_Georgia)
+
+# Display the table using knitr::kable
+kable(tidy_Georgia, digits = 2, 
+      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))
+
+```
+
+```{r}
+#| label: tbl-coe3
+#| fig-cap: Logistic Regression Coefficients for Michigan
+#| echo: false
+#| message: false
+#| warning: false
+# Tidy the logistic regression model
+tidy_Michigan <- tidy(logistic_Michigan)
+
+# Display the table using knitr::kable
+kable(tidy_Michigan, digits = 2, 
+      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))
+
+```
+
+```{r}
+#| label: tbl-coe4
+#| fig-cap: Logistic Regression Coefficients for North_Carolina
+#| echo: false
+#| message: false
+#| warning: false
+# Tidy the logistic regression model
+tidy_North_Carolina <- tidy(logistic_North_Carolina)
+
+# Display the table using knitr::kable
+kable(tidy_North_Carolina, digits = 2, 
+      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))
+
+```
+
+```{r}
+#| label: tbl-coe5
+#| fig-cap: Logistic Regression Coefficients for Arizona
+#| echo: false
+#| message: false
+#| warning: false
+# Tidy the logistic regression model
+tidy_Arizona <- tidy(logistic_Arizona)
+
+# Display the table using knitr::kable
+kable(tidy_Arizona, digits = 2, 
+      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))
+
+```
+
+```{r}
+#| label: tbl-coe6
+#| fig-cap: Logistic Regression Coefficients for Wisconsin
+#| echo: false
+#| message: false
+#| warning: false
+# Tidy the logistic regression model
+tidy_Wisconsin <- tidy(logistic_Wisconsin)
+
+# Display the table using knitr::kable
+kable(tidy_Wisconsin, digits = 2, 
+      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))
+
+```
+
+```{r}
+#| label: tbl-coe7
+#| fig-cap: Logistic Regression Coefficients for Nevada
+#| echo: false
+#| message: false
+#| warning: false
+# Tidy the logistic regression model
+tidy_Nevada <- tidy(logistic_Nevada)
+
+# Display the table using knitr::kable
+kable(tidy_Nevada, digits = 2, 
+      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))
+
+```
+
 \newpage

### 2024-11-04 paper/paper.qmd
updated paper

@@
 ```
-The regression coefficients for the logistic and linear models are presented in the Appendix because they are not the outcome of interest. Please view @tbl-coe1 to @tbl-coe7.
+The regression coefficients for the logistic and linear models are presented in the Appendix because they are not the outcome of interest.
 
@@
 ```
+\FloatBarrier
 
@@
 ```{r}
-#| label: tbl-coe1
-#| fig-cap: Logistic Regression Coefficients for Pennsylvania
 #| echo: false
@@
 kable(tidy_Pennsylvania, digits = 2, 
-      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))
-
-```
-```{r}
-#| label: tbl-coe2
-#| fig-cap: Logistic Regression Coefficients for Georgia
+      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
+      caption = "Logistic Regression Coefficients for Pennsylvania")
+
+```
+```{r}
 #| echo: false
@@
 kable(tidy_Georgia, digits = 2, 
-      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))
-
-```
-
-```{r}
-#| label: tbl-coe3
-#| fig-cap: Logistic Regression Coefficients for Michigan
+      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
+      caption = "Logistic Regression Coefficients for Georgia")
+
+```
+
+```{r}
 #| echo: false
@@
 kable(tidy_Michigan, digits = 2, 
-      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))
-
-```
-
-```{r}
-#| label: tbl-coe4
-#| fig-cap: Logistic Regression Coefficients for North_Carolina
+      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
+      caption = "Logistic Regression Coefficients for Michigan")
+
+```
+
+```{r}
 #| echo: false
@@
 kable(tidy_North_Carolina, digits = 2, 
-      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))
-
-```
-
-```{r}
-#| label: tbl-coe5
-#| fig-cap: Logistic Regression Coefficients for Arizona
+      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
+      caption = "Logistic Regression Coefficients for North_Carolina")
+
+```
+
+```{r}
 #| echo: false
@@
 kable(tidy_Arizona, digits = 2, 
-      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))
-
-```
-
-```{r}
-#| label: tbl-coe6
-#| fig-cap: Logistic Regression Coefficients for Wisconsin
+      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
+      caption = "Logistic Regression Coefficients for Arizona")
+
+```
+
+```{r}
 #| echo: false
@@
 kable(tidy_Wisconsin, digits = 2, 
-      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))
-
-```
-
-```{r}
-#| label: tbl-coe7
-#| fig-cap: Logistic Regression Coefficients for Nevada
+      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
+      caption = "Logistic Regression Coefficients for Wisconsin")
+
+```
+
+```{r}
 #| echo: false
@@
 kable(tidy_Nevada, digits = 2, 
-      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))
+      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
+      caption = "Logistic Regression Coefficients for Nevada")
 

### 2024-11-04 scripts/00-simulate_data.R
updated preamble

@@ -2,8 +2,8 @@
 # Purpose: Simulates a dataset of US presidential election polls
 # Author: Andrew Goh, Yisu Hou
 # Date: 3 November 2024
-# Contact: rohan.alexander@utoronto.ca
-# License: MIT
+# Contact: yisu.hou@mail.utoronto.ca
+# License: None
 # Pre-requisites: Packages `tidyverse` and `lubridate` must be installed
 
 

### 2024-11-04 scripts/01-test_simulated_data.R

@@ -3,8 +3,8 @@
   # electoral polls dataset.
 # Author: Andrew Goh, Yisu Hou
 # Date: 3 November 2024
-# Contact: rohan.alexander@utoronto.ca
-# License: MIT
+# Contact: yisu.hou@mail.utoronto.ca
+# License: None
 # Pre-requisites: 
   # - Packages `tidyverse`, `lubridate`, and `testthat` must be installed
   # - 00-simulate_data.R must have been run

### 2024-11-04 scripts/02-clean_data.R

@@ -2,9 +2,13 @@
 # Purpose: Cleans the raw US presidential election polls data from FiveThirtyEight
 # Author: Andrew Goh, Yisu Hou
 # Date: 3 November 2024
-# Contact: rohan.alexander@utoronto.ca
-# License: MIT
-# Pre-requisites:
+# Contact: yisu.hou@mail.utoronto.ca
+# License: None
+# Pre-requisites:  
+  # - Packages `tidyverse`, `lubridate`, `janitor`, `broom`, `modelsummary`, `rstanarm`, 
+  # and `splines`must be installed
+  # - Raw data downloaded from FiveThirtyEight
+  # - 00-simulate_data.R and 01-test_simulate_data.R must have been run
 
 #### Workspace setup ####
 

### 2024-11-04 scripts/03-test_analysis_data.R

@@ -1,11 +1,12 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
+# Purpose: Tests data used for analysis
 # Author: Andrew Goh, Yisu Hou
 # Date: 3 November 2024
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
+# Contact: yisu.hou@mail.utoronto.ca
+# License: None
 # Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+  # - Packages `tidyverse` and `testthat` must be installed
+  # - 02-clean_data.R must have been run
 
 
 #### Workspace setup ####

### 2024-11-04 scripts/04-exploratory_data_analysis.R

@@ -1,11 +1,13 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
+# Purpose: Exploratory data analysis using analysis data
 # Author: Andrew Goh, Yisu Hou
 # Date: 3 November 2024
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Contact: yisu.hou@mail.utoronto.ca
+# License: None
+# Pre-requisites:
+  # - Packages `tidyverse`, `caret`, `glmnet`, `nnet`, `lubridate`, `pROC`, 
+  # and `stringr`must be installed
+  # - 02-clean_data.R and 03-test_analysis_data.R must have been run
 
 
 #### Workspace setup ####

### 2024-11-04 scripts/05-model_data.R

@@ -1,11 +1,14 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Purpose: Models the probability of Harris winning on election day
+# Author: Andrew Goh, Yisu Hou
+# Date: 3 November 2024
+# Contact: yisu.hou@mail.utoronto.ca
+# License: None
+# Pre-requisites:
+  # - Packages `tidyverse`, `caret`, `glmnet`, `nnet`, `lubridate`, `pROC`, 
+  # `stringr`, and `gt` must be installed
+  # - 02-clean_data.R, 03-test_analysis_data.R,
+  # and 04-exploratory_data_analysis.R must have been run
 
 
 #### Workspace setup ####

### 2024-11-04 paper/paper.qmd
final modifications

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "A Logistic Regression Prediction of 2024 Election Odds Gives VP Harris a 38.3% Winrate"
 author: 
@@
   - Yisu Hou
-thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
+thanks: "Code and data are available at: [https://github.com/YisuHou1/US_Election_Statistics](https://github.com/YisuHou1/US_Election_Statistics)."
 date: today
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "The 2024 Presidential Election, run between the Democratic candidate Vice President Kamala Harris and Republican candidate Former President Donald Trump, is both widely predicted to be a close race [@538data] and considered to be the “most important election of your life” by a majority of likely voters this election season, as estimated by Quinnipiac [@quinnipiac].
+To predict the results of this election, we use a FiveThirtyEight poll-of-polls dataset [@538data], fitting multinomial logistic regression models with the data both at a national level and for each of the 7 swing states.
+Using these estimates for the probability of Harris winning the popular votes in each of those categories, we find that Vice President Harris has a 38.3% probability of winning the election in the context of the electoral college, a statistically significant result after considering margin of error and various biases."
 format: pdf
@@
 
-Overview paragraph
-
-note: For the literature review/why our thing matters section talk about how other predictions don't consider the biases in polls.
-Our thing is something new because we attempt to account for the bias in historical predictions for our 2024 prediction.
-(basically, for all models and predictions, I have an adjusted version that adjusts the support percentage using the difference between 2020 polls and real election outcomes, and a normal version that just uses the percentages from 2024 polls)
-
-There's essentially 3 different levels of analysis: using multiple linear regression to look at the candidates' support over time on the national level, using logistic regression to predict the chance of winning on the national level, using state polls data to see who is ahead in electoral college votes.
-
-Estimand paragraph
-
-Results paragraph
-
-Why it matters paragraph
-
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+With most polls maintaining close (<1) odds at both the national and statewide level for the seven swing states [@538data; @nyt2024polls], the 2024 Presidential Elections are proving to be an extremely volatile one, with poll predictions regularly flipping and disagreeing with each other, even up until the day before Election Day.
+The volatility even extends beyond the polling itself – since the January 6 Capitol Attack, prominent figures supporting both parties have painted the 2024 elections specifically as one that underpins the very democratic integrity of the country.
+Elon Musk, for example, has openly expressed concerns of a Harris win leading to a one-party country [@musk2024x], and Zack Beauchamp from Vox has described a Trump re-election as an “extinction-level threat to democracy” [@vox].
+In short, the stakes are high, at least as perceived in the eyes of voters [@quinnipiac].
+
+In order to arrive at such a conclusion, we used poll-by-polls data from FiveThirtyEight [@538data] to fit multinomial logistic regression models for both the nation as a whole and each of the seven swing states.
+Taking into consideration the mispredictions by pollsters for both the 2016 and 2020 elections, where Trump won the presidential race against Clinton in a 304-227 landslide despite predictions universally predicting a landslide win in the opposite direction [@weighting2], we regress on the characteristics of the poll/pollster such as transparency rating and sponsors and correct the results for systematic polling biases based on past election data, an approach predicted to yield better results this year [@weighting].
+
+Our estimand, or what we seek to predict, is the probability that Kamala Harris wins the election on the 6th of November.
+
+After obtaining the probabilities that Harris wins each swing state via randomised sampling using our fitted models, we then analysed these probabilities in the context of the electoral college, i.e.
+the probability that Harris can obtain 44 votes from the swing states, which would all but guarantee her step into office [@nyt2024polls].
+We find that Harris has a 38.3% chance of winning the general election, suggesting a likely Trump advantage after accounting for the margin of error in all related processes and observations.
+
+The body of the paper contains the data, model, results, and discussion sections.
+In order, @sec-data contains an overview of the data used, the variables involved and the tools used in our analysis and interpretation of the data, @sec-model describes the model in detail and other related miscellaneous musings, @sec-results contains a run-down and explanation of the results and findings from the model, and @sec-discussion contains a discussion of the implications and limitations of the result, among others.
+The appendices contain a sample of an idealised methodology and survey, as well as a case study of the sample and methodology of Quinnipiac’s Pennsylvania poll [@quinnipiac; @quinnipiacmethodology].
 
@@
 
-# Model
+# Model {#sec-model}
 
@@
 A logistic model was constructed for each state, using harris_win as the outcome and previously stated predictors as inputs.
-[EXPLAIN THE 1000 simulations and PROBABILITY calculation STEP HERE]
+
+Then, after the models were constructed, we conducted 1000 simulations of election results with randomly-generated parameters.
+The date parameter was set to election day, and the other three predictor variables were simulated from a normal distribution with the mean and standard deviation of the training dataset.
+We then averaged the values to obtain our final prediction for the probability of a Harris win in the state of interest.
+
+Then, using the probabilities for each state and their respective electoral college votes, we calculated the probability that Vice President Harris successfully obtains the 44 required electoral college votes to secure the presidency.
+This is done via an R script that can be found in the end of /scripts/05-model_data.R.
 
@@
 We identified the AUC values and ROC plots for each of the seven swing-state logistic regressions.
-The ROC plots are presented in the Appendix, from @fig-pen to @fig-nev.
+The ROC plots are presented in the Additional Data Details section (@sec-model-details), from @fig-pen to @fig-nev.
 The AUC values are: 0.90 for Pennsylvania, 0.88 for Georgia, 0.74 for North Carolina, 0.93 for Michigan, 1.00 for Arizona, 0.86 for Wisconsin, and 0.65 for Nevada.
@@
 Utilizing training and testing datasets implies that the datasets may include only a couple of data points in some states, which is insufficient to construct or test the model.
-On top of that, according to [@trainingerror], achieving low training error is sufficient to ensure the predictability of a model to some extent.
-[ADD MORE IF NECESSARY]
+On top of that, according to [@trainingerror], achieving low training error, such as by using a training-MSE-minimising regression model such as our own, is sufficient to ensure the predictive capabilities of a model bounded by some constant variance term.
 
@@
 
-# Results
+# Results {#sec-results}
 
@@
 
-# Discussion
-
-## First discussion point {#sec-first-point}
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-
-## Second discussion point
-
-Please don't use these as sub-heading labels - change them to be what your point actually is.
-
-## Third discussion point
+# Discussion {#sec-discussion   }
+
+## The illusion of polarization
+
+As mentioned in the introduction, one thing that stands out about the 2024 election in particular is just how polarized the two factions are.
+Instead of merely being a choice over which individual to helm the country over the next four years, this particular election is being framed more and more as a “fight to protect our democracy” from both sides of the debate stand.
+This, while evidently a new level of polarization, merely mirrors the trend in recent years more than anything else: party loyalty has been on a steady uprise since 1972, with loyalty in weak partisan and leaning independent voters increasing by approximately 50% in the 40 years that followed [@partisanship].
+New records were further set in 2016, with Republican validated voters voting Trump a staggering 92% to 4% for Clinton, and Democratic validated voters voting Clinton an equally extreme 94% to 5% Trump support [@pew2018voters].
+
+New voting statistics, however, suggest that this polarization is likely only more prominent in the upper echelons of political representation, however: a Washington Post article found that approximately 1 in 8 women and 1 in 10 men are now voting differently from their spouses compared to before [@wapo2024women], a development that suggests a decrease in long-increasing partisanship trends.
+This is especially pronounced since households in the States overwhelmingly vote together: at least 70% of them do, at least, which means that this value is projected to decrease from 70% to approximately 62% [@households].
+In short: while it seems that ideologies are shifting more and more away from each other, the stats say otherwise.
+So does the Overton window [@overton].
+
+## Win probabilities versus support ratings: why our predictions are as extreme as they are
+
+Our model led to a win probability prediction with numbers much more skewed towards one side than most pollsters currently predict: under this model, we find that Harris has a 40-60 chance against Trump, whereas most pollsters nowadays hover somewhere between 50-50 to 45-55 (towards either side).
+This is mainly a consequence of using a multinomial logistic regression model as opposed than other models – instead of predicting the support rates of the two candidates, such a model outputs the probability that a random support rate value from the predicted distribution of Harris support rates is larger than that of the predicted distribution of Trump support rates.
+This means that in states such as Nevada, where 538 gives Trump a +3 advantage, factoring in for margin of error and standard error means that the probability of Harris winning the state is not in fact 47% but rather much closer to zero, which we decided is a more intuitive way of understanding election odds.
+
+A final reason for this is how swing states are polled much more sample-size-wise than other states, leading to a much higher power value than polls from said other states – a +3 lead in a sample of 1000 people from California’s 39 million might not mean too much, but a +3 lead in a sample of 3000 people from Nevada’s 3 million represents the actual results for 0.3% of the state’s population, holding much more relative weight when it comes to election predictions.
 
@@
 FiveThirtyEight utilizes predictive variables that are unavailable to us, such as weighted values that represent the extent to which a pollster is partisan [@5383].
-The predictors used in this research, such as the transparency score of the pollster, are not related to their bias towards any candidate.
-This limits the predictive power of our models.
+The predictors used in this research, such as the transparency score of the pollster, are not related to their bias towards any candidate from a partisanship point of view, limiting the predictive power of our models.
 

### 2024-11-04 paper/paper.qmd
laaaaaast changes

@@
 
+Finally, the lack of data regarding the Harris-Trump race, due to Harris starting her presidential race uncharacteristically late, is also a main reason for the limitations of our model.
+
+Potential next steps could be taken to improve the model in the future: more data could be aggregated manually (from pollsters not recorded by FiveThirtyEight), stronger predictor variables that are specifically more correlated with partisanship could be marked and utilised in our model, and individual weightings could be utilised and applied to the data based on each pollster's "track record" with regards to the error, bias, and variance in their previous polls and estimates.
+
 \newpage

### 2024-11-04 paper/paper.qmd
updated paper and references

@@
 Caret [@caret], glmnet [@glmnet; @glmnet2; @glmnet3], nnet [@nnet], lubridate [@lubridate] and pROC [@pROC] were used directly in the analysis of the data.
-Tidyverse [@tidyverse], stringr [@stringr], dplyr [@dplyr], and styler [@styler] were used in the presentation and/or styling of the data, graphs, and paper as a whole.
+Tidyverse [@tidyverse], stringr [@stringr], dplyr [@dplyr], gt [@gt], knitr [@knitr], and styler [@styler] were used in the presentation and/or styling of the data, graphs, and paper as a whole.
 
@@
 ```
-The regression coefficients for the logistic and linear models are presented in the Appendix because they are not the outcome of interest.
+\FloatBarrier
+
+The regression coefficients for the logistic and linear models are presented in the Additional Data Details section (@sec-model-details) because they are not the outcome of interest.
 

### 2024-11-04 paper/paper.qmd
really reallyreally last thing i forgot aaaaaa

@@
 # datasets with lower numeric scores already includes polls with a score of 3.0
-all_combined <- bind_rows(harris_2024_lower, trump_2024_lower,
-    biden_2020, trump_2020)
-
+all_combined <- bind_rows(
+  harris_2024_lower, trump_2024_lower,
+  biden_2020, trump_2020
+)
 ```
@@
   )
-
 ```
@@
 
-ggplot(all_combined, aes(x = factor(has_sponsor, levels = c(0,1), labels = c("No Sponsor", "Has Sponsor")))) +
+ggplot(all_combined, aes(x = factor(has_sponsor, levels = c(0, 1), labels = c("No Sponsor", "Has Sponsor")))) +
   geom_bar(fill = "#1f78b4", color = "white", alpha = 0.7) +
@@
   harris_Pennsylvania,
-  by = c("pollster", "has_sponsor", "pollscore", 
-         "transparency_score", "sample_size", "end_date", "state", "cycle")
+  by = c(
+    "pollster", "has_sponsor", "pollscore",
+    "transparency_score", "sample_size", "end_date", "state", "cycle"
+  )
 )
@@
   harris_Georgia,
-  by = c("pollster", "has_sponsor", "pollscore", 
-         "transparency_score", "sample_size", "end_date", "state", "cycle")
+  by = c(
+    "pollster", "has_sponsor", "pollscore",
+    "transparency_score", "sample_size", "end_date", "state", "cycle"
+  )
 )
@@
   harris_North_Carolina,
-  by = c("pollster", "has_sponsor", "pollscore", 
-         "transparency_score", "sample_size", "end_date", "state", "cycle")
+  by = c(
+    "pollster", "has_sponsor", "pollscore",
+    "transparency_score", "sample_size", "end_date", "state", "cycle"
+  )
 )
@@
   harris_Michigan,
-  by = c("pollster", "has_sponsor", "pollscore", 
-         "transparency_score", "sample_size", "end_date", "state", "cycle")
+  by = c(
+    "pollster", "has_sponsor", "pollscore",
+    "transparency_score", "sample_size", "end_date", "state", "cycle"
+  )
 )
@@
   harris_Arizona,
-  by = c("pollster", "has_sponsor", "pollscore", 
-         "transparency_score", "sample_size", "end_date", "state", "cycle")
+  by = c(
+    "pollster", "has_sponsor", "pollscore",
+    "transparency_score", "sample_size", "end_date", "state", "cycle"
+  )
 )
@@
   harris_Wisconsin,
-  by = c("pollster", "has_sponsor", "pollscore", 
-         "transparency_score", "sample_size", "end_date", "state", "cycle")
+  by = c(
+    "pollster", "has_sponsor", "pollscore",
+    "transparency_score", "sample_size", "end_date", "state", "cycle"
+  )
 )
@@
   harris_Nevada,
-  by = c("pollster", "has_sponsor", "pollscore", 
-         "transparency_score", "sample_size", "end_date", "state", "cycle")
+  by = c(
+    "pollster", "has_sponsor", "pollscore",
+    "transparency_score", "sample_size", "end_date", "state", "cycle"
+  )
 )
@@
   mutate(
-    harris_win_prob = round(100*predict(logistic_Pennsylvania, type = "response"), 2)
-  )
-
-roc_obj_Pennsylvania <- roc(combined_Pennsylvania$harris_win,
-                  combined_Pennsylvania$harris_win_prob)
+    harris_win_prob = round(100 * predict(logistic_Pennsylvania, type = "response"), 2)
+  )
+
+roc_obj_Pennsylvania <- roc(
+  combined_Pennsylvania$harris_win,
+  combined_Pennsylvania$harris_win_prob
+)
 
@@
   mutate(
-    harris_win_prob = round(100*predict(logistic_Georgia, type = "response"), 2)
-  )
-
-roc_obj_Georgia <- roc(combined_Georgia$harris_win,
-                            combined_Georgia$harris_win_prob)
+    harris_win_prob = round(100 * predict(logistic_Georgia, type = "response"), 2)
+  )
+
+roc_obj_Georgia <- roc(
+  combined_Georgia$harris_win,
+  combined_Georgia$harris_win_prob
+)
 
@@
   mutate(
-    harris_win_prob = round(100*predict(logistic_North_Carolina, type = "response"), 2)
-  )
-
-roc_obj_North_Carolina <- roc(combined_North_Carolina$harris_win,
-                            combined_North_Carolina$harris_win_prob)
+    harris_win_prob = round(100 * predict(logistic_North_Carolina, type = "response"), 2)
+  )
+
+roc_obj_North_Carolina <- roc(
+  combined_North_Carolina$harris_win,
+  combined_North_Carolina$harris_win_prob
+)
 
@@
   mutate(
-    harris_win_prob = round(100*predict(logistic_Michigan, type = "response"), 2)
-  )
-
-roc_obj_Michigan <- roc(combined_Michigan$harris_win,
-                            combined_Michigan$harris_win_prob)
+    harris_win_prob = round(100 * predict(logistic_Michigan, type = "response"), 2)
+  )
+
+roc_obj_Michigan <- roc(
+  combined_Michigan$harris_win,
+  combined_Michigan$harris_win_prob
+)
 
@@
   mutate(
-    harris_win_prob = round(100*predict(logistic_Arizona, type = "response"), 2)
-  )
-
-roc_obj_Arizona <- roc(combined_Arizona$harris_win,
-                            combined_Arizona$harris_win_prob)
+    harris_win_prob = round(100 * predict(logistic_Arizona, type = "response"), 2)
+  )
+
+roc_obj_Arizona <- roc(
+  combined_Arizona$harris_win,
+  combined_Arizona$harris_win_prob
+)
 
@@
   mutate(
-    harris_win_prob = round(100*predict(logistic_Wisconsin, type = "response"), 2)
-  )
-
-roc_obj_Wisconsin <- roc(combined_Wisconsin$harris_win,
-                            combined_Wisconsin$harris_win_prob)
+    harris_win_prob = round(100 * predict(logistic_Wisconsin, type = "response"), 2)
+  )
+
+roc_obj_Wisconsin <- roc(
+  combined_Wisconsin$harris_win,
+  combined_Wisconsin$harris_win_prob
+)
 
@@
   mutate(
-    harris_win_prob = round(100*predict(logistic_Nevada, type = "response"), 2)
-  )
-
-roc_obj_Nevada <- roc(combined_Nevada$harris_win,
-                            combined_Nevada$harris_win_prob)
+    harris_win_prob = round(100 * predict(logistic_Nevada, type = "response"), 2)
+  )
+
+roc_obj_Nevada <- roc(
+  combined_Nevada$harris_win,
+  combined_Nevada$harris_win_prob
+)
 
 auc_value_Nevada <- auc(roc_obj_Nevada)
-
 ```
@@
 trainIndex_trump_adj <- createDataPartition(trump_2024_national_adj$pct_adj,
-                                        p = 0.8, list = FALSE)
+  p = 0.8, list = FALSE
+)
 data_train_trump_adj <- trump_2024_national_adj[trainIndex_trump_adj, ]
@@
 trainIndex_harris_adj <- createDataPartition(harris_2024_national_adj$pct_adj,
-                                         p = 0.8, list = FALSE)
+  p = 0.8, list = FALSE
+)
 data_train_harris_adj <- harris_2024_national_adj[trainIndex_harris_adj, ]
@@
 trainIndex_trump <- createDataPartition(trump_2024_national$pct,
-                                        p = 0.8, list = FALSE)
+  p = 0.8, list = FALSE
+)
 data_train_trump <- trump_2024_national[trainIndex_trump, ]
@@
 trainIndex_harris <- createDataPartition(harris_2024_national$pct,
-                                         p = 0.8, list = FALSE)
+  p = 0.8, list = FALSE
+)
 data_train_harris <- harris_2024_national[trainIndex_harris, ]
@@
   harris_2024_national,
-  by = c("pollster", "has_sponsor", "pollscore", 
-         "transparency_score", "sample_size", "end_date", "state", "cycle")
+  by = c(
+    "pollster", "has_sponsor", "pollscore",
+    "transparency_score", "sample_size", "end_date", "state", "cycle"
+  )
 )
@@
   harris_2024_national_adj,
-  by = c("pollster", "has_sponsor", "pollscore",
-         "transparency_score", "sample_size", "end_date", "state", "cycle")
+  by = c(
+    "pollster", "has_sponsor", "pollscore",
+    "transparency_score", "sample_size", "end_date", "state", "cycle"
+  )
 )
@@
   mutate(
-    harris_win_prob = round(100*predict(model_logistic, type = "response"), 2)
+    harris_win_prob = round(100 * predict(model_logistic, type = "response"), 2)
   )
@@
   mutate(
-    harris_win_prob = round(100*predict(model_logistic_adj, 
-                                        type = "response"), 2)
+    harris_win_prob = round(100 * predict(model_logistic_adj,
+      type = "response"
+    ), 2)
   )
@@
 # ROC Curve and AUC
-roc_obj <- roc(combined_national$harris_win,
-               combined_national$harris_win_prob)
+roc_obj <- roc(
+  combined_national$harris_win,
+  combined_national$harris_win_prob
+)
 auc_value <- auc(roc_obj)
 
-roc_obj_adj <- roc(combined_national_adj$harris_win,
-               combined_national_adj$harris_win_prob)
+roc_obj_adj <- roc(
+  combined_national_adj$harris_win,
+  combined_national_adj$harris_win_prob
+)
 auc_value_adj <- auc(roc_obj_adj)
@@
   has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Pennsylvania$has_sponsor)),
-  transparency_score = rnorm(1000, mean = mean(combined_Pennsylvania$transparency_score), 
-                             sd = sd(combined_Pennsylvania$transparency_score)),
-  sample_size = rnorm(1000, mean = mean(combined_Pennsylvania$sample_size),
-                      sd = sd(combined_Pennsylvania$sample_size))
+  transparency_score = rnorm(1000,
+    mean = mean(combined_Pennsylvania$transparency_score),
+    sd = sd(combined_Pennsylvania$transparency_score)
+  ),
+  sample_size = rnorm(1000,
+    mean = mean(combined_Pennsylvania$sample_size),
+    sd = sd(combined_Pennsylvania$sample_size)
+  )
 )
@@
   has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Georgia$has_sponsor)),
-  transparency_score = rnorm(1000, mean = mean(combined_Georgia$transparency_score), 
-                             sd = sd(combined_Georgia$transparency_score)),
-  sample_size = rnorm(1000, mean = mean(combined_Georgia$sample_size),
-                      sd = sd(combined_Georgia$sample_size))
+  transparency_score = rnorm(1000,
+    mean = mean(combined_Georgia$transparency_score),
+    sd = sd(combined_Georgia$transparency_score)
+  ),
+  sample_size = rnorm(1000,
+    mean = mean(combined_Georgia$sample_size),
+    sd = sd(combined_Georgia$sample_size)
+  )
 )
@@
   has_sponsor = rbinom(1000, size = 1, prob = mean(combined_North_Carolina$has_sponsor)),
-  transparency_score = rnorm(1000, mean = mean(combined_North_Carolina$transparency_score), 
-                             sd = sd(combined_North_Carolina$transparency_score)),
-  sample_size = rnorm(1000, mean = mean(combined_North_Carolina$sample_size),
-                      sd = sd(combined_North_Carolina$sample_size))
+  transparency_score = rnorm(1000,
+    mean = mean(combined_North_Carolina$transparency_score),
+    sd = sd(combined_North_Carolina$transparency_score)
+  ),
+  sample_size = rnorm(1000,
+    mean = mean(combined_North_Carolina$sample_size),
+    sd = sd(combined_North_Carolina$sample_size)
+  )
 )
@@
   has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Michigan$has_sponsor)),
-  transparency_score = rnorm(1000, mean = mean(combined_Michigan$transparency_score), 
-                             sd = sd(combined_Michigan$transparency_score)),
-  sample_size = rnorm(1000, mean = mean(combined_Michigan$sample_size),
-                      sd = sd(combined_Michigan$sample_size))
+  transparency_score = rnorm(1000,
+    mean = mean(combined_Michigan$transparency_score),
+    sd = sd(combined_Michigan$transparency_score)
+  ),
+  sample_size = rnorm(1000,
+    mean = mean(combined_Michigan$sample_size),
+    sd = sd(combined_Michigan$sample_size)
+  )
 )
@@
   has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Arizona$has_sponsor)),
-  transparency_score = rnorm(1000, mean = mean(combined_Arizona$transparency_score), 
-                             sd = sd(combined_Arizona$transparency_score)),
-  sample_size = rnorm(1000, mean = mean(combined_Arizona$sample_size),
-                      sd = sd(combined_Arizona$sample_size))
+  transparency_score = rnorm(1000,
+    mean = mean(combined_Arizona$transparency_score),
+    sd = sd(combined_Arizona$transparency_score)
+  ),
+  sample_size = rnorm(1000,
+    mean = mean(combined_Arizona$sample_size),
+    sd = sd(combined_Arizona$sample_size)
+  )
 )
@@
   has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Wisconsin$has_sponsor)),
-  transparency_score = rnorm(1000, mean = mean(combined_Wisconsin$transparency_score), 
-                             sd = sd(combined_Wisconsin$transparency_score)),
-  sample_size = rnorm(1000, mean = mean(combined_Wisconsin$sample_size),
-                      sd = sd(combined_Wisconsin$sample_size))
+  transparency_score = rnorm(1000,
+    mean = mean(combined_Wisconsin$transparency_score),
+    sd = sd(combined_Wisconsin$transparency_score)
+  ),
+  sample_size = rnorm(1000,
+    mean = mean(combined_Wisconsin$sample_size),
+    sd = sd(combined_Wisconsin$sample_size)
+  )
 )
@@
   has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Nevada$has_sponsor)),
-  transparency_score = rnorm(1000, mean = mean(combined_Nevada$transparency_score), 
-                             sd = sd(combined_Nevada$transparency_score)),
-  sample_size = rnorm(1000, mean = mean(combined_Nevada$sample_size),
-                      sd = sd(combined_Nevada$sample_size))
+  transparency_score = rnorm(1000,
+    mean = mean(combined_Nevada$transparency_score),
+    sd = sd(combined_Nevada$transparency_score)
+  ),
+  sample_size = rnorm(1000,
+    mean = mean(combined_Nevada$sample_size),
+    sd = sd(combined_Nevada$sample_size)
+  )
 )
@@
   mutate(
-    harris_win_prob = round(100*predict(logistic_Pennsylvania, newdata = ., type = "response"), 2)
+    harris_win_prob = round(100 * predict(logistic_Pennsylvania, newdata = ., type = "response"), 2)
   )
@@
   mutate(
-    harris_win_prob = round(100*predict(logistic_Georgia, newdata = ., type = "response"), 2)
+    harris_win_prob = round(100 * predict(logistic_Georgia, newdata = ., type = "response"), 2)
   )
@@
   mutate(
-    harris_win_prob = round(100*predict(logistic_North_Carolina, newdata = ., type = "response"), 2)
+    harris_win_prob = round(100 * predict(logistic_North_Carolina, newdata = ., type = "response"), 2)
   )
@@
   mutate(
-    harris_win_prob = round(100*predict(logistic_Michigan, newdata = ., type = "response"), 2)
+    harris_win_prob = round(100 * predict(logistic_Michigan, newdata = ., type = "response"), 2)
   )
@@
   mutate(
-    harris_win_prob = round(100*predict(logistic_Arizona, newdata = ., type = "response"), 2)
+    harris_win_prob = round(100 * predict(logistic_Arizona, newdata = ., type = "response"), 2)
   )
@@
   mutate(
-    harris_win_prob = round(100*predict(logistic_Wisconsin, newdata = ., type = "response"), 2)
+    harris_win_prob = round(100 * predict(logistic_Wisconsin, newdata = ., type = "response"), 2)
   )
@@
   mutate(
-    harris_win_prob = round(100*predict(logistic_Nevada, newdata = ., type = "response"), 2)
+    harris_win_prob = round(100 * predict(logistic_Nevada, newdata = ., type = "response"), 2)
   )
@@
   prob <- 1
-  for(i in 1:nrow(states)) {
-    if(i %in% combo) {
+  for (i in 1:nrow(states)) {
+    if (i %in% combo) {
       prob <- prob * states$prob[i]
@@
 # Check each possible combination
-for(i in 1:(2^n_states - 1)) {
+for (i in 1:(2^n_states - 1)) {
   # Convert number to binary to get combination
@@
   # If this combination has enough votes, add its probability
-  if(votes >= 44) {
+  if (votes >= 44) {
     prob <- calc_combo_prob(combo, states)
@@
 states <- data.frame(
-  state = c("PA", "GA", "NC", "MI", "WI", "NV","AZ"),
-  prob = c(1-0.5551, 1-0.6801, 1-0.1033, 1-0.5151, 1-0.3792, 1-0.7679, 1-0), # Using 1-p for Trump's probabilities
+  state = c("PA", "GA", "NC", "MI", "WI", "NV", "AZ"),
+  prob = c(1 - 0.5551, 1 - 0.6801, 1 - 0.1033, 1 - 0.5151, 1 - 0.3792, 1 - 0.7679, 1 - 0), # Using 1-p for Trump's probabilities
   votes = c(20, 16, 15, 16, 10, 6, 11)
@@
   # If this combination has enough votes, add its probability
-  if(votes >= 51) {
+  if (votes >= 51) {
     prob <- calc_combo_prob(combo, states)
@@
 }
-
 ```
@@
   # Assign specific colors
-  scale_color_manual(values = 
-                       c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
+  scale_color_manual(
+    values =
+      c("Kamala Harris" = "blue", "Donald Trump" = "red")
+  ) +
   # Customize the plot appearance
@@
 plot(roc_obj_Pennsylvania)
-
 ```
@@
 plot(roc_obj_Georgia)
-
 ```
@@
 plot(roc_obj_North_Carolina)
-
 ```
@@
 plot(roc_obj_Michigan)
-
 ```
@@
 plot(roc_obj_Arizona)
-
 ```
@@
 plot(roc_obj_Wisconsin)
-
 ```
@@
 plot(roc_obj_Nevada)
-
 ```
@@
 plot(roc_obj)
-
 ```
@@
 # Display the table using knitr::kable
-kable(tidy_Pennsylvania, digits = 2, 
+kable(tidy_Pennsylvania,
+  digits = 2,
   col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
-      caption = "Logistic Regression Coefficients for Pennsylvania")
-
+  caption = "Logistic Regression Coefficients for Pennsylvania"
+)
 ```
@@
 # Display the table using knitr::kable
-kable(tidy_Georgia, digits = 2, 
+kable(tidy_Georgia,
+  digits = 2,
   col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
-      caption = "Logistic Regression Coefficients for Georgia")
-
+  caption = "Logistic Regression Coefficients for Georgia"
+)
 ```
@@
 # Display the table using knitr::kable
-kable(tidy_Michigan, digits = 2, 
+kable(tidy_Michigan,
+  digits = 2,
   col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
-      caption = "Logistic Regression Coefficients for Michigan")
-
+  caption = "Logistic Regression Coefficients for Michigan"
+)
 ```
@@
 # Display the table using knitr::kable
-kable(tidy_North_Carolina, digits = 2, 
+kable(tidy_North_Carolina,
+  digits = 2,
   col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
-      caption = "Logistic Regression Coefficients for North_Carolina")
-
+  caption = "Logistic Regression Coefficients for North_Carolina"
+)
 ```
@@
 # Display the table using knitr::kable
-kable(tidy_Arizona, digits = 2, 
+kable(tidy_Arizona,
+  digits = 2,
   col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
-      caption = "Logistic Regression Coefficients for Arizona")
-
+  caption = "Logistic Regression Coefficients for Arizona"
+)
 ```
@@
 # Display the table using knitr::kable
-kable(tidy_Wisconsin, digits = 2, 
+kable(tidy_Wisconsin,
+  digits = 2,
   col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
-      caption = "Logistic Regression Coefficients for Wisconsin")
-
+  caption = "Logistic Regression Coefficients for Wisconsin"
+)
 ```
@@
 # Display the table using knitr::kable
-kable(tidy_Nevada, digits = 2, 
+kable(tidy_Nevada,
+  digits = 2,
   col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
-      caption = "Logistic Regression Coefficients for Nevada")
-
+  caption = "Logistic Regression Coefficients for Nevada"
+)
 ```

### 2024-11-04 scripts/00-simulate_data.R

@@ -16,11 +16,11 @@ set.seed(114514)
 
 # define the range of pollsters
 pollster_options <- c(
-  "Siena/NYT", 
-  "YouGov", 
-  "CES / YouGov", 
-  "Marquette Law School", 
-  "The Washington Post", 
+  "Siena/NYT",
+  "YouGov",
+  "CES / YouGov",
+  "Marquette Law School",
+  "The Washington Post",
   "McCourtney Institute/YouGov"
 )
 
@@ -31,8 +31,8 @@ us_states <- state.name
 n <- 300
 
 # For the state variable, have half of the values "National"
-n_national <- n / 2  # 50
-n_states <- n - n_national  # 50
+n_national <- n / 2 # 50
+n_states <- n - n_national # 50
 # Create a vector with 50 "National" and 50 random state names
 state_vector <- c(
   rep("National", n_national),
@@ -56,8 +56,11 @@ simulated_data <- tibble(
   # end date between the day Harris announced and the last day of polls
   # recorded in the polls dataset
   end_date = sample(
-    seq.Date(from = as.Date("2024-07-21"), 
-    to = as.Date("2024-10-26"), by = "day"), n, replace = TRUE
+    seq.Date(
+      from = as.Date("2024-07-21"),
+      to = as.Date("2024-10-26"), by = "day"
+    ), n,
+    replace = TRUE
   ),
   # percent support assigned with a normal distribution
   pct_support = round(rnorm(n, mean = 50, sd = 2))
@@ -70,4 +73,3 @@ simulated_data <- simulated_data %>% mutate(
 
 #### Write_csv
 write_csv(simulated_data, file = "data/00-simulated_data/simulated_polls.csv")
-

### 2024-11-04 scripts/01-test_simulated_data.R

@@ -1,13 +1,13 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated US 
-  # electoral polls dataset.
+# Purpose: Tests the structure and validity of the simulated US
+# electoral polls dataset.
 # Author: Andrew Goh, Yisu Hou
 # Date: 3 November 2024
 # Contact: yisu.hou@mail.utoronto.ca
 # License: None
-# Pre-requisites: 
-  # - Packages `tidyverse`, `lubridate`, and `testthat` must be installed
-  # - 00-simulate_data.R must have been run
+# Pre-requisites:
+# - Packages `tidyverse`, `lubridate`, and `testthat` must be installed
+# - 00-simulate_data.R must have been run
 
 
 #### Workspace setup ####
@@ -30,18 +30,20 @@ test_that("Simulated Dataset has correct structure", {
 })
 
 test_that("Simulated Dataset has all required columns with correct types", {
-  required_cols <- c("pollster", "has_sponsor", "pollscore", 
-                     "transparency_score", "sample_size", "end_date", "pct_support")
+  required_cols <- c(
+    "pollster", "has_sponsor", "pollscore",
+    "transparency_score", "sample_size", "end_date", "pct_support"
+  )
   expect_true(all(required_cols %in% colnames(simulated_data)))
-  
+
   # Check data types
   expect_type(simulated_data$pollster, "character")
-  expect_type(simulated_data$has_sponsor, "double") 
-  expect_type(simulated_data$pollscore, "double") 
+  expect_type(simulated_data$has_sponsor, "double")
+  expect_type(simulated_data$pollscore, "double")
   expect_type(simulated_data$transparency_score, "double")
   expect_type(simulated_data$sample_size, "double")
   expect_s3_class(simulated_data$end_date, "Date")
-  expect_type(simulated_data$pct_support, "double")  
+  expect_type(simulated_data$pct_support, "double")
 })
 
 
@@ -49,11 +51,11 @@ test_that("Simulated Dataset has all required columns with correct types", {
 
 test_that("pollster column contains only valid pollster names", {
   valid_pollsters <- c(
-    "Siena/NYT", 
-    "YouGov", 
-    "CES / YouGov", 
-    "Marquette Law School", 
-    "The Washington Post", 
+    "Siena/NYT",
+    "YouGov",
+    "CES / YouGov",
+    "Marquette Law School",
+    "The Washington Post",
     "McCourtney Institute/YouGov"
   )
[…]

### 2024-11-04 scripts/02-clean_data.R

@@ -4,11 +4,11 @@
 # Date: 3 November 2024
 # Contact: yisu.hou@mail.utoronto.ca
 # License: None
-# Pre-requisites:  
-  # - Packages `tidyverse`, `lubridate`, `janitor`, `broom`, `modelsummary`, `rstanarm`, 
-  # and `splines`must be installed
-  # - Raw data downloaded from FiveThirtyEight
-  # - 00-simulate_data.R and 01-test_simulate_data.R must have been run
+# Pre-requisites:
+# - Packages `tidyverse`, `lubridate`, `janitor`, `broom`, `modelsummary`, `rstanarm`,
+# and `splines`must be installed
+# - Raw data downloaded from FiveThirtyEight
+# - 00-simulate_data.R and 01-test_simulate_data.R must have been run
 
 #### Workspace setup ####
 
@@ -25,7 +25,7 @@ library(splines)
 #### Read data ####
 current_polls_data <- read_csv("data/01-raw_data/president_polls.csv") |>
   clean_names()
-past_polls_data <- 
+past_polls_data <-
   read_csv("data/01-raw_data/president_polls_historical.csv") |>
   clean_names()
 
@@ -34,7 +34,7 @@ just_harris_high_quality <- current_polls_data |>
   filter(
     candidate_name == "Kamala Harris",
     numeric_grade >= 3.0,
-    population == 'lv' # keep likely voters only to be more predictive
+    population == "lv" # keep likely voters only to be more predictive
   ) |>
   mutate(
     state = if_else(is.na(state), "National", state),
@@ -48,7 +48,7 @@ just_trump_high_quality <- current_polls_data |>
   filter(
     candidate_name == "Donald Trump",
     numeric_grade >= 3.0,
-    population == 'lv' # keep likely voters only to be more predictive
+    population == "lv" # keep likely voters only to be more predictive
   ) |>
   mutate(
     state = if_else(is.na(state), "National", state),
@@ -62,7 +62,7 @@ biden_past_high_quality <- past_polls_data |>
   filter(
     candidate_name == "Joe Biden",
     numeric_grade >= 3.0,
-    population == 'lv' # keep likely voters only to be more predictive
+    population == "lv" # keep likely voters only to be more predictive
   ) |>
   mutate(
     state = if_else(is.na(state), "National", state),
@@ -74,7 +74,7 @@ trump_past_high_quality <- past_polls_data |>
   filter(
[…]

### 2024-11-04 scripts/03-test_analysis_data.R

@@ -5,8 +5,8 @@
 # Contact: yisu.hou@mail.utoronto.ca
 # License: None
 # Pre-requisites: [...UPDATE THIS...]
-  # - Packages `tidyverse` and `testthat` must be installed
-  # - 02-clean_data.R must have been run
+# - Packages `tidyverse` and `testthat` must be installed
+# - 02-clean_data.R must have been run
 
 
 #### Workspace setup ####
@@ -37,29 +37,32 @@ datasets_list_low <- list(
 
 # Define the helper function to run tests
 run_sanity_checks <- function(data, dataset_name) {
-  
   test_that(paste("Sanity Checks for", dataset_name), {
-    
     #### Data Structure Tests ####
-    
+
     # Check if the dataset is a dataframe
     expect_true(is.data.frame(data), info = paste(dataset_name, "is not a dataframe"))
-    
+
     # Check number of rows
-    expect_true(nrow(data) >= 50 && nrow(data) <= 1000, 
-                info = paste(dataset_name, "does not have between 50 and 1000 rows"))
-    
+    expect_true(nrow(data) >= 50 && nrow(data) <= 1000,
+      info = paste(dataset_name, "does not have between 50 and 1000 rows")
+    )
+
     # Check number of columns (11)
-    expect_equal(ncol(data), 11, 
-                 info = paste(dataset_name, "does not have exactly 11 columns"))
-    
+    expect_equal(ncol(data), 11,
+      info = paste(dataset_name, "does not have exactly 11 columns")
+    )
+
     # Check for required columns
-    required_cols <- c("pollster", "has_sponsor", "numeric_grade", "pollscore", 
-                       "transparency_score", "sample_size", "end_date",
-                       "state", "candidate_name", "pct", "cycle")
-    expect_true(all(required_cols %in% colnames(data)), 
-                info = paste(dataset_name, "is missing required columns"))
-    
+    required_cols <- c(
+      "pollster", "has_sponsor", "numeric_grade", "pollscore",
+      "transparency_score", "sample_size", "end_date",
+      "state", "candidate_name", "pct", "cycle"
+    )
+    expect_true(all(required_cols %in% colnames(data)),
+      info = paste(dataset_name, "is missing required columns")
+    )
+
     # Check data types of important variables
     expect_type(data$pollster, "character")
     expect_type(data$has_sponsor, "double")
@@ -69,123 +72,139 @@ run_sanity_checks <- function(data, dataset_name) {
[…]

### 2024-11-04 scripts/04-exploratory_data_analysis.R

@@ -5,9 +5,9 @@
 # Contact: yisu.hou@mail.utoronto.ca
 # License: None
 # Pre-requisites:
-  # - Packages `tidyverse`, `caret`, `glmnet`, `nnet`, `lubridate`, `pROC`, 
-  # and `stringr`must be installed
-  # - 02-clean_data.R and 03-test_analysis_data.R must have been run
+# - Packages `tidyverse`, `caret`, `glmnet`, `nnet`, `lubridate`, `pROC`,
+# and `stringr`must be installed
+# - 02-clean_data.R and 03-test_analysis_data.R must have been run
 
 
 #### Workspace setup ####
@@ -25,61 +25,63 @@ library(stringr)
 #### Read data ####
 trump_2024 <- read_csv("data/02-analysis_data/trump_2024_analysis_data.csv")
 harris_2024 <- read_csv("data/02-analysis_data/harris_2024_analysis_data.csv")
-trump_2024_lower <- 
+trump_2024_lower <-
   read_csv("data/02-analysis_data/trump_2024_analysis_data_lower.csv")
-harris_2024_lower <- 
+harris_2024_lower <-
   read_csv("data/02-analysis_data/harris_2024_analysis_data_lower.csv")
 trump_2020 <- read_csv("data/02-analysis_data/trump_2020_analysis_data.csv")
 biden_2020 <- read_csv("data/02-analysis_data/biden_2020_analysis_data.csv")
 
 # Distribution of variables in the dataset
-all_combined <- bind_rows(harris_2024_lower, trump_2024_lower,
-                          biden_2020, trump_2020)
+all_combined <- bind_rows(
+  harris_2024_lower, trump_2024_lower,
+  biden_2020, trump_2020
+)
 
 # Generate plots to display the distributions
 ggplot(all_combined, aes(x = pct)) +
   geom_histogram(
-    binwidth = 1,                # Adjust bin width for granularity
-    fill = "#2c7bb6",            # Aesthetic fill color (steel blue)
-    color = "white",             # Border color for bins
-    alpha = 0.8                   # Transparency of the fill
+    binwidth = 1, # Adjust bin width for granularity
+    fill = "#2c7bb6", # Aesthetic fill color (steel blue)
+    color = "white", # Border color for bins
+    alpha = 0.8 # Transparency of the fill
   ) +
   labs(
     x = "Percentage Support",
     y = "Number of Polls"
   ) +
-  theme_minimal(base_size = 14) +   # Minimal theme with increased base font size
[…]

### 2024-11-04 scripts/05-model_data.R

@@ -5,10 +5,10 @@
 # Contact: yisu.hou@mail.utoronto.ca
 # License: None
 # Pre-requisites:
-  # - Packages `tidyverse`, `caret`, `glmnet`, `nnet`, `lubridate`, `pROC`, 
-  # `stringr`, and `gt` must be installed
-  # - 02-clean_data.R, 03-test_analysis_data.R,
-  # and 04-exploratory_data_analysis.R must have been run
+# - Packages `tidyverse`, `caret`, `glmnet`, `nnet`, `lubridate`, `pROC`,
+# `stringr`, and `gt` must be installed
+# - 02-clean_data.R, 03-test_analysis_data.R,
+# and 04-exploratory_data_analysis.R must have been run
 
 
 #### Workspace setup ####
@@ -27,9 +27,9 @@ library(gt)
 #### Read data ####
 trump_2024 <- read_csv("data/02-analysis_data/trump_2024_analysis_data.csv")
 harris_2024 <- read_csv("data/02-analysis_data/harris_2024_analysis_data.csv")
-trump_2024_lower <- 
+trump_2024_lower <-
   read_csv("data/02-analysis_data/trump_2024_analysis_data_lower.csv")
-harris_2024_lower <- 
+harris_2024_lower <-
   read_csv("data/02-analysis_data/harris_2024_analysis_data_lower.csv")
 trump_2020 <- read_csv("data/02-analysis_data/trump_2020_analysis_data.csv")
 biden_2020 <- read_csv("data/02-analysis_data/biden_2020_analysis_data.csv")
@@ -78,36 +78,40 @@ harris_2024_national_adj <- harris_2024_national %>%
 # model adjusted support percentage by time and control variables
 # first split training and testing dataset using an 80/20 split
 set.seed(11451)
-trainIndex_trump_adj <- createDataPartition(trump_2024_national_adj$pct_adj, 
-                                        p = 0.8, list = FALSE)
+trainIndex_trump_adj <- createDataPartition(trump_2024_national_adj$pct_adj,
+  p = 0.8, list = FALSE
+)
 data_train_trump_adj <- trump_2024_national_adj[trainIndex_trump_adj, ]
-data_test_trump_adj  <- trump_2024_national_adj[-trainIndex_trump_adj, ]
+data_test_trump_adj <- trump_2024_national_adj[-trainIndex_trump_adj, ]
 
-trainIndex_harris_adj <- createDataPartition(harris_2024_national_adj$pct_adj, 
-                                         p = 0.8, list = FALSE)
[…]

### 2024-12-03 scripts/00-simulate_data.R
updated scripts

@@ -1,75 +1,72 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of US presidential election polls
-# Author: Andrew Goh, Yisu Hou
-# Date: 3 November 2024
+# Purpose: Simulates a dataset of Chinese individual survey data
+# Author: Yisu Hou
+# Date: 28 November 2024
 # Contact: yisu.hou@mail.utoronto.ca
 # License: None
-# Pre-requisites: Packages `tidyverse` and `lubridate` must be installed
+# Pre-requisites: R Package `tidyverse` must be installed
 
 
 #### Workspace setup ####
 library(tidyverse)
-library(lubridate)
 
 #### Simulate data ####
 set.seed(114514)
 
-# define the range of pollsters
-pollster_options <- c(
-  "Siena/NYT",
-  "YouGov",
-  "CES / YouGov",
-  "Marquette Law School",
-  "The Washington Post",
-  "McCourtney Institute/YouGov"
-)
 
-# Define US states
-us_states <- state.name
-
+#### Generate data with all variables of interest ####
 # Define number of rows
-n <- 300
+n <- 500
 
-# For the state variable, have half of the values "National"
-n_national <- n / 2 # 50
-n_states <- n - n_national # 50
-# Create a vector with 50 "National" and 50 random state names
-state_vector <- c(
-  rep("National", n_national),
-  sample(us_states, n_states, replace = TRUE)
-)
-# Shuffle the state_vector to randomize the order
-state_vector <- sample(state_vector, n, replace = FALSE)
+# 1. yearly_income
+# Generate from a normal distribution with mean=50000 and sd=20000
+# Then round to nearest hundred and constrain between 0 and 1,000,000
+# This is to mimic the actual dataset, where values are measured in hundreds
+yearly_income <- rnorm(n, mean = 50000, sd = 20000)
+# Replace negative incomes with 0
+yearly_income[yearly_income < 0] <- 0
+# Replace incomes above 1,000,000 with 1,000,000
+yearly_income[yearly_income > 1000000] <- 1000000
+# Round to nearest hundred
+yearly_income <- round(yearly_income / 100) * 100
 
-# Generate national simulated dataset
-simulated_data <- tibble(
-  # pollster randomly assigned from the pollsters with 3.0 numeric grade
-  pollster = sample(pollster_options, n, replace = TRUE),
[…]

### 2024-12-03 scripts/01-test_simulated_data.R

@@ -1,21 +1,20 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated US
-# electoral polls dataset.
-# Author: Andrew Goh, Yisu Hou
-# Date: 3 November 2024
+# Purpose: Tests the structure and validity of the simulated Chinese
+# individual survey dataset.
+# Author: Yisu Hou
+# Date: 28 November 2024
 # Contact: yisu.hou@mail.utoronto.ca
 # License: None
 # Pre-requisites:
-# - Packages `tidyverse`, `lubridate`, and `testthat` must be installed
+# - Packages `tidyverse` and `testthat` must be installed
 # - 00-simulate_data.R must have been run
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
-library(lubridate)
 
-simulated_data <- read_csv("data/00-simulated_data/simulated_polls.csv")
+dataset <- read_csv("data/00-simulated_data/simulated_data.csv")
 
 # Define the test context
 context("Sanity Checks for Simulated Datasets")
@@ -23,100 +22,85 @@ context("Sanity Checks for Simulated Datasets")
 #### Data structure tests ####
 
 test_that("Simulated Dataset has correct structure", {
-  expect_true(is.data.frame(simulated_data))
-  expect_true(50 <= nrow(simulated_data))
-  expect_true(1000 >= nrow(simulated_data))
-  expect_equal(ncol(simulated_data), 8)
+  expect_true(is.data.frame(dataset))
+  expect_equal(nrow(dataset), 500)
+  expect_equal(ncol(dataset), 8)
 })
 
 test_that("Simulated Dataset has all required columns with correct types", {
   required_cols <- c(
-    "pollster", "has_sponsor", "pollscore",
-    "transparency_score", "sample_size", "end_date", "pct_support"
+    "yearly_income",
+    "years_of_education",
+    "years_of_work",
+    "gender",
+    "city_hukou",
+    "is_party",
+    "is_married",
+    "is_east"
   )
-  expect_true(all(required_cols %in% colnames(simulated_data)))
-
+  expect_true(all(required_cols %in% colnames(dataset)))
+  
   # Check data types
-  expect_type(simulated_data$pollster, "character")
-  expect_type(simulated_data$has_sponsor, "double")
-  expect_type(simulated_data$pollscore, "double")
-  expect_type(simulated_data$transparency_score, "double")
-  expect_type(simulated_data$sample_size, "double")
[…]

### 2024-12-03 scripts/02-clean_data.R

@@ -1,13 +1,12 @@
 #### Preamble ####
-# Purpose: Cleans the raw US presidential election polls data from FiveThirtyEight
-# Author: Andrew Goh, Yisu Hou
-# Date: 3 November 2024
+# Purpose: Cleans the raw survey data from CFPS
+# Author: Yisu Hou
+# Date: 28 November 2024
 # Contact: yisu.hou@mail.utoronto.ca
 # License: None
 # Pre-requisites:
-# - Packages `tidyverse`, `lubridate`, `janitor`, `broom`, `modelsummary`, `rstanarm`,
-# and `splines`must be installed
-# - Raw data downloaded from FiveThirtyEight
+# - Packages `tidyverse`, `janitor`, `arrow`, and `haven must be installed`
+# - Raw data downloaded from CFPS and located in data/01-raw_data
 # - 00-simulate_data.R and 01-test_simulate_data.R must have been run
 
 #### Workspace setup ####
@@ -15,197 +14,650 @@
 # Load libraries
 library(tidyverse)
 library(janitor)
-library(lubridate)
-library(broom)
-library(modelsummary)
-library(rstanarm)
-library(splines)
+library(haven)
+library(arrow)
 
 
 #### Read data ####
-current_polls_data <- read_csv("data/01-raw_data/president_polls.csv") |>
-  clean_names()
-past_polls_data <-
-  read_csv("data/01-raw_data/president_polls_historical.csv") |>
-  clean_names()
+# import raw datasets for all CFPS iterations
+# 2020 data
+cfps2020person_raw <- read_sas("data/01-raw_data/cfps2020person_202306.sas7bdat", 
+                               NULL)
+cfps2020famecon <- read_sas("data/01-raw_data/cfps2020famecon_202306.sas7bdat",
+                            NULL)
 
-# Filter data to Harris estimates based on high-quality polls after she declared
-just_harris_high_quality <- current_polls_data |>
-  filter(
-    candidate_name == "Kamala Harris",
-    numeric_grade >= 3.0,
-    population == "lv" # keep likely voters only to be more predictive
-  ) |>
-  mutate(
-    state = if_else(is.na(state), "National", state),
-    end_date = mdy(end_date),
-    has_sponsor = if_else(is.na(sponsors), 0, 1)
[…]

### 2024-12-03 scripts/03-test_analysis_data.R

@@ -1,37 +1,35 @@
 #### Preamble ####
 # Purpose: Tests data used for analysis
-# Author: Andrew Goh, Yisu Hou
-# Date: 3 November 2024
+# Author: Yisu Hou
+# Date: 28 November 2024
 # Contact: yisu.hou@mail.utoronto.ca
 # License: None
-# Pre-requisites: [...UPDATE THIS...]
-# - Packages `tidyverse` and `testthat` must be installed
+# Pre-requisites:
+# - Packages `tidyverse`, `arrow` and `testthat` must be installed
 # - 02-clean_data.R must have been run
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
+library(arrow)
 
-biden_2020 <- read_csv("data/02-analysis_data/biden_2020_analysis_data.csv")
-trump_2020 <- read_csv("data/02-analysis_data/trump_2020_analysis_data.csv")
-harris_2024 <- read_csv("data/02-analysis_data/harris_2024_analysis_data.csv")
-trump_2024 <- read_csv("data/02-analysis_data/trump_2024_analysis_data.csv")
-harris_2024_low <- read_csv("data/02-analysis_data/harris_2024_analysis_data_lower.csv")
-trump_2024_low <- read_csv("data/02-analysis_data/trump_2024_analysis_data_lower.csv")
+data_2020 <- read_parquet("data/02-analysis_data/2020_analysis_data.parquet")
+data_2018 <- read_parquet("data/02-analysis_data/2018_analysis_data.parquet")
+data_2016 <- read_parquet("data/02-analysis_data/2016_analysis_data.parquet")
+data_2014 <- read_parquet("data/02-analysis_data/2014_analysis_data.parquet")
+data_2012 <- read_parquet("data/02-analysis_data/2012_analysis_data.parquet")
+data_2010 <- read_parquet("data/02-analysis_data/2010_analysis_data.parquet")
 
 
 # Create a named list of datasets
 datasets_list <- list(
-  biden_2020 = biden_2020,
-  trump_2020 = trump_2020,
-  harris_2024 = harris_2024,
-  trump_2024 = trump_2024
-)
-
-datasets_list_low <- list(
-  harris_2024_low = harris_2024_low,
-  trump_2024_low = trump_2024_low
+  data_2020 = data_2020,
+  data_2018 = data_2018,
+  data_2016 = data_2016,
+  data_2014 = data_2014,
+  data_2012 = data_2012,
[…]

### 2024-12-03 scripts/04-exploratory_data_analysis.R

@@ -1,12 +1,11 @@
 #### Preamble ####
 # Purpose: Exploratory data analysis using analysis data
-# Author: Andrew Goh, Yisu Hou
-# Date: 3 November 2024
+# Author: Yisu Hou
+# Date: 28 November 2024
 # Contact: yisu.hou@mail.utoronto.ca
 # License: None
 # Pre-requisites:
-# - Packages `tidyverse`, `caret`, `glmnet`, `nnet`, `lubridate`, `pROC`,
-# and `stringr`must be installed
+# - Packages `tidyverse`, `arrow` are installed
 # - 02-clean_data.R and 03-test_analysis_data.R must have been run
 
 
@@ -14,41 +13,33 @@
 
 # Load libraries
 library(tidyverse)
-library(caret)
-library(glmnet)
-library(nnet)
-library(lubridate)
-library(pROC)
-library(stringr)
-
+library(arrow)
 
 #### Read data ####
-trump_2024 <- read_csv("data/02-analysis_data/trump_2024_analysis_data.csv")
-harris_2024 <- read_csv("data/02-analysis_data/harris_2024_analysis_data.csv")
-trump_2024_lower <-
-  read_csv("data/02-analysis_data/trump_2024_analysis_data_lower.csv")
-harris_2024_lower <-
-  read_csv("data/02-analysis_data/harris_2024_analysis_data_lower.csv")
-trump_2020 <- read_csv("data/02-analysis_data/trump_2020_analysis_data.csv")
-biden_2020 <- read_csv("data/02-analysis_data/biden_2020_analysis_data.csv")
+data_2020 <- read_parquet("data/02-analysis_data/2020_analysis_data.parquet")
+data_2018 <- read_parquet("data/02-analysis_data/2018_analysis_data.parquet")
+data_2016 <- read_parquet("data/02-analysis_data/2016_analysis_data.parquet")
+data_2014 <- read_parquet("data/02-analysis_data/2014_analysis_data.parquet")
+data_2012 <- read_parquet("data/02-analysis_data/2012_analysis_data.parquet")
+data_2010 <- read_parquet("data/02-analysis_data/2010_analysis_data.parquet")
 
 # Distribution of variables in the dataset
+# Make a combined dataset that includes all survey iterations
 all_combined <- bind_rows(
-  harris_2024_lower, trump_2024_lower,
-  biden_2020, trump_2020
+  data_2020, data_2018, data_2016, data_2014, data_2012, data_2010
[…]

### 2024-12-03 scripts/05-model_data.R

@@ -1,978 +1,885 @@
 #### Preamble ####
-# Purpose: Models the probability of Harris winning on election day
-# Author: Andrew Goh, Yisu Hou
-# Date: 3 November 2024
+# Purpose: Models the educational returns of working individuals in China
+# Author: Yisu Hou
+# Date: 28 November 2024
 # Contact: yisu.hou@mail.utoronto.ca
 # License: None
 # Pre-requisites:
 # - Packages `tidyverse`, `caret`, `glmnet`, `nnet`, `lubridate`, `pROC`,
-# `stringr`, and `gt` must be installed
+#   `stringr`, and `gt` must be installed
 # - 02-clean_data.R, 03-test_analysis_data.R,
-# and 04-exploratory_data_analysis.R must have been run
+#   and 04-exploratory_data_analysis.R must have been run
 
 
 #### Workspace setup ####
 
-# Load libraries
-library(tidyverse)
-library(caret)
-library(glmnet)
-library(nnet)
-library(lubridate)
-library(pROC)
-library(stringr)
-library(gt)
-
-
-#### Read data ####
-trump_2024 <- read_csv("data/02-analysis_data/trump_2024_analysis_data.csv")
-harris_2024 <- read_csv("data/02-analysis_data/harris_2024_analysis_data.csv")
-trump_2024_lower <-
-  read_csv("data/02-analysis_data/trump_2024_analysis_data_lower.csv")
-harris_2024_lower <-
-  read_csv("data/02-analysis_data/harris_2024_analysis_data_lower.csv")
-trump_2020 <- read_csv("data/02-analysis_data/trump_2020_analysis_data.csv")
-biden_2020 <- read_csv("data/02-analysis_data/biden_2020_analysis_data.csv")
-
-# find biases of pollsters from 2020 national polls data
-# filter out national polls from the datasets
-trump_2024_national <- trump_2024 %>% filter(state == "National")
-harris_2024_national <- harris_2024 %>% filter(state == "National")
-trump_2020_national <- trump_2020 %>% filter(state == "National")
-biden_2020_national <- biden_2020 %>% filter(state == "National")
-
-# Define actual results
-actual_results_2020 <- list(Trump_pct = 47, Biden_pct = 51)
-
-# Calculate bias per pollster
-rep_pollster_bias <- trump_2020_national %>%
-  group_by(pollster) %>%
-  summarize(
[…]

### 2024-12-03 scripts/04-exploratory_data_analysis.R
added placeholder datasets

@@ -5,7 +5,7 @@
 # Contact: yisu.hou@mail.utoronto.ca
 # License: None
 # Pre-requisites:
-# - Packages `tidyverse`, `arrow` are installed
+# - Packages `tidyverse` and `arrow` are installed
 # - 02-clean_data.R and 03-test_analysis_data.R must have been run
 
 

### 2024-12-03 scripts/00-simulate_data.R
added comments

@@ -68,5 +68,6 @@ simulated_data <- data.frame(
   is_east = is_east
 )
 
-#### Write_csv
+#### Write_csv ####
 write_csv(simulated_data, file = "data/00-simulated_data/simulated_data.csv")
+

### 2024-12-03 scripts/02-clean_data.R
edited code

@@ -661,3 +661,30 @@ write_parquet(
 )
 
 
+#### Placeholder datasets for the repo (remove when replicating) ####
+# Create empty dataset
+placeholder_df <- tibble(
+  yearly_income = numeric(),  
+  years_of_education = numeric(),  
+  years_of_work = numeric(),    
+  gender = numeric(),         
+  city_hukou = numeric(),      
+  is_party = numeric(),      
+  is_married = numeric(),      
+  is_east = numeric(),
+  income_quartile = numeric()
+)
+
+# Save into repo
+write_csv(
+  placeholder_df,
+  "data/01-raw_data/raw_data_placeholder.csv"
+)
+
+# This is in csv to prevent being ignored
+# Real analysis datasets are stored as parquet files
+write_csv(
+  placeholder_df,
+  "data/02-analysis_data/analysis_data_placeholder.csv"
+)
+

### 2024-12-03 paper/paper.qmd
updated paper and references

@@
 ---
-title: "A Logistic Regression Prediction of 2024 Election Odds Gives VP Harris a 38.3% Winrate"
+title: "Family Income and Educational Returns in China, 2010-2020: Higher Returns Favor the Wealthy, but Gaps Hold Steady"
 author: 
-  - Andrew Goh
   - Yisu Hou
-thanks: "Code and data are available at: [https://github.com/YisuHou1/US_Election_Statistics](https://github.com/YisuHou1/US_Election_Statistics)."
+thanks: "Code and data are available at: [https://github.com/YisuHou1/Educational_Returns_Analysis](https://github.com/YisuHou1/Educational_Returns_Analysis)."
 date: today
 date-format: long
-abstract: "The 2024 Presidential Election, run between the Democratic candidate Vice President Kamala Harris and Republican candidate Former President Donald Trump, is both widely predicted to be a close race [@538data] and considered to be the “most important election of your life” by a majority of likely voters this election season, as estimated by Quinnipiac [@quinnipiac].
-To predict the results of this election, we use a FiveThirtyEight poll-of-polls dataset [@538data], fitting multinomial logistic regression models with the data both at a national level and for each of the 7 swing states.
-Using these estimates for the probability of Harris winning the popular votes in each of those categories, we find that Vice President Harris has a 38.3% probability of winning the election in the context of the electoral college, a statistically significant result after considering margin of error and various biases."
+abstract: "Economic returns to education are a key driver of socioeconomic mobility, yet they are not distributed equally across all income groups.
+Using data from the China Family Panel Studies (CFPS) between 2010 and 2020, this paper examines how family income influences the financial benefits individuals gain from education.
+The analysis reveals that individuals from wealthier families consistently enjoy significantly higher income returns from education compared to their lower-income counterparts, though this gap did not widen over the decade studied.
+These findings highlight persistent inequality in education's economic impact, emphasizing the need for policies that ensure education serves as a more effective equalizer in society."
 format: pdf
@@
 library(nnet)
-library(lubridate)
-library(pROC)
 library(stringr)
@@
 library(knitr)
+library(MatchIt)
+library(arrow)
 ```
@@
 
-With most polls maintaining close (<1) odds at both the national and statewide level for the seven swing states [@538data; @nyt2024polls], the 2024 Presidential Elections are proving to be an extremely volatile one, with poll predictions regularly flipping and disagreeing with each other, even up until the day before Election Day.
-The volatility even extends beyond the polling itself – since the January 6 Capitol Attack, prominent figures supporting both parties have painted the 2024 elections specifically as one that underpins the very democratic integrity of the country.
-Elon Musk, for example, has openly expressed concerns of a Harris win leading to a one-party country [@musk2024x], and Zack Beauchamp from Vox has described a Trump re-election as an “extinction-level threat to democracy” [@vox].
-In short, the stakes are high, at least as perceived in the eyes of voters [@quinnipiac].
-
-In order to arrive at such a conclusion, we used poll-by-polls data from FiveThirtyEight [@538data] to fit multinomial logistic regression models for both the nation as a whole and each of the seven swing states.
-Taking into consideration the mispredictions by pollsters for both the 2016 and 2020 elections, where Trump won the presidential race against Clinton in a 304-227 landslide despite predictions universally predicting a landslide win in the opposite direction [@weighting2], we regress on the characteristics of the poll/pollster such as transparency rating and sponsors and correct the results for systematic polling biases based on past election data, an approach predicted to yield better results this year [@weighting].
-
-Our estimand, or what we seek to predict, is the probability that Kamala Harris wins the election on the 6th of November.
-
-After obtaining the probabilities that Harris wins each swing state via randomised sampling using our fitted models, we then analysed these probabilities in the context of the electoral college, i.e.
-the probability that Harris can obtain 44 votes from the swing states, which would all but guarantee her step into office [@nyt2024polls].
-We find that Harris has a 38.3% chance of winning the general election, suggesting a likely Trump advantage after accounting for the margin of error in all related processes and observations.
+Since the economic reform in China in 1978, China’s GDP per capita has increased more than 29 times [@NBSC2020].
+However, this period of rapid economic growth has been accompanied by greater socioeconomic inequality.
+The increased stratification, along with a number of China specific policies, has pushed the GINI coefficient close to 0.5, and various studies have demonstrated that the majority of China’s wealth is concentrated in the hands of a few [@XieJin2015].
+
+In examining the factors contributing to China’s increasing inequality, a multitude of social scientists highlight China’s education system.
+The correlation between socioeconomic status and education has been widely scrutinized.
+According to Esping-Andersen, "in modern capitalist society, the two main exclusionary devices through which the bourgeoisie structures and perpetuates itself as a class, are first, those surrounding the institutions of property, and second, academic or professional qualifications and credentials." [@EspingAndersen1982]
+
+In China, educational attainment directly corresponds to future earnings.
+Research by Byron and Manaloto showed an approximate 4 percent increase in earnings for each year of schooling [@Byron1990], and Wu and Xie identified a rate of 4.7 percent [@Wu2003].
+Jansen and Wu documented a significant rising trend of returns on education during China’s economic reform period from 1978 to 2005 [@Jansen2012].
+Concurrently, China significantly expanded its higher education sector, raising the gross enrollment rate from 9.8 percent in 1998 to 24.2 percent in 2009 [@Wang2011].
+As of 2022, the enrollment rate stands at 59.7 percent, indicating that China has fully transitioned from elite to mass higher education.
+Although increased access to higher education and higher returns on education are generally believed to foster social mobility, China’s inequality has worsened.
+To elucidate this paradoxical outcome, researchers found that the new educational opportunities are predominantly accessed by privileged groups, such as individuals with higher social status, males, and urban populations [@Ou2019].
+
+Previous research has also investigated the reasons behind the educational gap between high and low-income individuals.
+In the 20th century, many theorists proposed theories examining the link between socioeconomic status and educational achievement.
+Some suggest that income-based segregation places low-income children in overcrowded classrooms with less adequately trained educators.
+Others argue that teachers may harbor negative attitudes towards low-income children, anticipating they will perform poorly academically, thereby creating a self-fulfilling prophecy [@Bond1981].
+More recently, Duncan and Murnane suggested that the disparity in child enrichment expenditure influences academic performance, giving children from high-income families an advantage [@Duncan2014].
+
+However, while the relationship between financial status and educational attainment is relatively well established, there is a dearth of research, especially in China, to explore the link between family financial status and the rate of return from education.
+This is an essential connection, as it signifies how effectively education translates into its ultimate outcome: income.
+The aim of this research is to fill this knowledge gap by examining whether individuals from different socioeconomic backgrounds in the Chinese population receive the same level of returns from education.
+
+The estimand of this investigation is the disparities in educational returns among individuals from different family wealth quartiles during the decade 2020 to 2020, measured in the percent income increase per year of education received.
+
+To arrive at a conclusion, national family and individual data from China Family Panel Studies [@cfps] from the year 2010 to 2020 were extracted.
+For the data in each CFPS iteration, Propensity Score Matching (PSM) was utilized to balance the control variables across different family wealth quartiles, and separate polynomial regressions were fit to identify the disparities of educational returns across quartiles.
+It was found that throughout the decade, individuals from wealthier families possessed a significant advantage over individuals from less wealthy families, with disparities reaching more than 3% income increase per year of education between some quartiles.
 
 The body of the paper contains the data, model, results, and discussion sections.
-In order, @sec-data contains an overview of the data used, the variables involved and the tools used in our analysis and interpretation of the data, @sec-model describes the model in detail and other related miscellaneous musings, @sec-results contains a run-down and explanation of the results and findings from the model, and @sec-discussion contains a discussion of the implications and limitations of the result, among others.
-The appendices contain a sample of an idealised methodology and survey, as well as a case study of the sample and methodology of Quinnipiac’s Pennsylvania poll [@quinnipiac; @quinnipiacmethodology].
+In order, @sec-data contains an overview of the data, the variables used, and the programming tools used in my analysis and interpretation of the data.
+@sec-model describes the model in detail and provides justification for it.
+@sec-results contains a run-down and explanation of the results and findings from the model, and @sec-discussion contains a discussion of the implications and limitations of the result, among others.
+The appendices contain a detailed examination of the methodologies of CFPS, as well as aspects of the data and analysis excluded from the body.
 
@@
 
-We use the statistical programming language R [@R] for the graphing, analysis and presentation of the project as a whole.
-Caret [@caret], glmnet [@glmnet; @glmnet2; @glmnet3], nnet [@nnet], lubridate [@lubridate] and pROC [@pROC] were used directly in the analysis of the data.
-Tidyverse [@tidyverse], stringr [@stringr], dplyr [@dplyr], gt [@gt], knitr [@knitr], and styler [@styler] were used in the presentation and/or styling of the data, graphs, and paper as a whole.
-
-In order to build a model that predicts the results of the 2024 election, we use survey/poll data on likely voters to inform our insights regarding likely election results, an approach widely accepted in political contexts [@politicalpolling].
-We use a poll-of-polls dataset from 538 [@538data], consisting of aggregated polling data from FiveThirtyEight's 2024 presidential election polling database from various national and state-level polls from pollsters all around the country, recording information such as the date when the poll concluded, the entity conducting the poll, and the estimated support rate of the candidate as given by the poll.
-The data spans national and state-level polls, with particular focus on key battleground states that could determine the Electoral College outcome.
-This dataset was chosen over alternatives like RealClearPolitics because of 538's comprehensive methodological adjustments and transparent quality standards for included polls.
+I used the statistical programming language R [@R] for the graphing, analysis and presentation of the project as a whole.
+Caret [@caret], glmnet [@glmnet; @glmnet2; @glmnet3], nnet [@nnet], tidyverse [@tidyverse], car [@car] MatchIt [@matchit] and arrow [@arrow] were used directly in the analysis of the data.
+Stringr [@stringr], dplyr [@dplyr], gt [@gt], knitr [@knitr], and styler [@styler] were used in the presentation and/or styling of the data, graphs, and paper as a whole.
+
+All data utilized in this study were sourced from various iterations of the China Family 
+Community Survey [@cfps].
+The CFPS is a nationwide community survey funded by 985 Program of Peking University and carried out by the Institute of Social Science Survey of Peking University.
+CFPS encompasses approximately 15,000 families across 25 provinces and aims to tracks them permanently since 2010.
+Its main objective is to gather data across three dimensions: individuals, households, and communities.
+To achieve this, CFPS comprises four sub-surveys that thoroughly investigates families, adults, and children, gathering data for thousands of variables.
+Given its expansive and representative sample and a wide range of variables, CFPS has become a staple dataset for research in Chinese social sciences.
+Alternative data sources for this study, such as China General Social Survey (CGSS) and China Social Survey (CSS) are also reliable but do not provide the same width of variables, especially concerning family units.
+For the purposes of this research, data was extracted from CFPS for the years 2010, 2012, 2014, 2016, 2018, and 2020.
 
@@
 
-The "from-voter-to-data" process for the 538 dataset involves three processes: measurement, where voter responses are collected and adjusted to best provide insight into a true support percentage population parameter, data collection, where data from polls is obtained and cleaned by 538 to only include polls adhering to their set of standards, and aggregation, where additional scores/variables are given to each poll to reflect their accuracy, transparency and bias levels with regards to polling scores [@5381].
-
-The measurement process involves several sequential steps, beginning with initial data collection where pollsters conduct surveys using various modes such as phone, online, or mixed-mode approaches to gather voter preferences.
-Sample processing follows, involving likely voter screens to identify probable voters, demographic weighting to match population benchmarks, and various adjustments to ensure representativeness [@quinnipiac; @newyorktimes].
-
-The data collection process involves obtaining data from various election polls from around the country, given that they meet specific methodological criteria.
-Each included poll must provide clear documentation of pollster identity, survey dates, and sampled population, maintain a minimum sample size of 100 respondents, and demonstrate transparent methodology including polling mode, sample source, and weighting procedures.
-Scientific sampling methods attempting to achieve representative samples are mandatory, as is the disclosure of poll sponsorship and funding sources.
-The dataset explicitly excludes non-scientific polls lacking representative sampling, MRP-smoothed data, recontact surveys, DIY polls from nonprofessional sources, polls with leading questions or hypothetical matchups, and subsamples from multi-state polls without geographic verification [@5382].
-
-The aggregation phase, finally, involves rating polls by pollster polling quality (ranging from 0.5 to 3.0 stars), with polls with higher historical accuracy, lower consistent partisan biases, and higher transparency of methodology boasting higher ratings [@5383].
-Transparency is also a rating and is done through a 10-question yes/no checklist on how much of the methodology is available to the public - note how this is completely separate from the quality of the methodology itself.
-Each question is graded on a 0/0.5/1 scale, for a combined transparency score that ranges from 0 to 10.
-Most polls in our dataset miss the mark on one or two criteron, netting a final transparency score of 9 - this is partially due to the data cleaning process removing many relatively worsely conducted polls.
-
-Several important measurement limitations to FiveThirtyEight's methodology must be acknowledged.
-These include temporal gaps between polls creating discontinuous measurement of voter sentiment, response rates and participation biases potentially skewing samples, and varying geographic coverage with swing states being overrepresented.
-Additionally, third-party candidate treatment varies across polls, and is difficult to standardise (with respect to other data points) consistently.
-
 ## Outcome variable
 
-The outcome variable is the level of support for the two leading US presidential candidates, Vice President Kamala Harris and Former President Donald Trump, recorded as a percentage of likely voters.
-For the national-level analysis, the support percentage represents the percentage of polled individuals who responded in favor of a specific candidate to a question that asked about their preferred presidential candidate in a national-level poll.
-For the regional datasets, the support percentage represents the percentage of likely voters who preferred a specific candidate in a poll that targets a specific state or congressional district of the United States.
-@fig-outcome shows the distribution of support percentages in the aggregated polling data from 2020 and 2024 presidential elections.
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-
-trump_2024 <- read_csv(here::here("data/02-analysis_data/trump_2024_analysis_data.csv"))
-harris_2024 <- read_csv(here::here("data/02-analysis_data/harris_2024_analysis_data.csv"))
-trump_2024_lower <-
-  read_csv(here::here("data/02-analysis_data/trump_2024_analysis_data_lower.csv"))
-harris_2024_lower <-
-  read_csv(here::here("data/02-analysis_data/harris_2024_analysis_data_lower.csv"))
-trump_2020 <- read_csv(here::here("data/02-analysis_data/trump_2020_analysis_data.csv"))
-biden_2020 <- read_csv(here::here("data/02-analysis_data/biden_2020_analysis_data.csv"))
-
-# aggregated dataset for summary statistics
-# datasets with lower numeric scores already includes polls with a score of 3.0
+The variables presented in this section are variables in the polynomial regression model to identify returns to education, which is a coefficient of the model. This will be specified in @sec-model.
+
+The outcome variable of the model is the natural logarithm of individuals' hourly wages.
+@fig-outcome shows its distribution in the aggregated survey data from all CFPS iterations between 2010 and 2020.
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+
+data_2020 <- read_parquet(here::here("data/02-analysis_data/2020_analysis_data.parquet"))
+data_2018 <- read_parquet(here::here("data/02-analysis_data/2018_analysis_data.parquet"))
+data_2016 <- read_parquet(here::here("data/02-analysis_data/2016_analysis_data.parquet"))
+data_2014 <- read_parquet(here::here("data/02-analysis_data/2014_analysis_data.parquet"))
+data_2012 <- read_parquet(here::here("data/02-analysis_data/2012_analysis_data.parquet"))
+data_2010 <- read_parquet(here::here("data/02-analysis_data/2010_analysis_data.parquet"))
+
+# Make a combined dataset that includes all survey iterations
 all_combined <- bind_rows(
-  harris_2024_lower, trump_2024_lower,
-  biden_2020, trump_2020
+  data_2020, data_2018, data_2016, data_2014, data_2012, data_2010
 )
@@
 
-ggplot(all_combined, aes(x = pct)) +
+# Outcome variable: ln hourly wage
+ggplot(all_combined, aes(x = ln_hourly_wage)) +
   geom_histogram(
-    binwidth = 1, # Adjust bin width for granularity
     fill = "#2c7bb6", # Aesthetic fill color (steel blue)
     color = "white", # Border color for bins
-    alpha = 0.8 # Transparency of the fill
+    alpha = 1 # Transparency of the fill
   ) +
   labs(
-    x = "Percentage Support",
-    y = "Number of Polls"
+    x = "ln Hourly Wage",
+    y = "Frequency"
   ) +
@@
   geom_vline(
-    aes(xintercept = mean(pct, na.rm = TRUE)),
+    aes(xintercept = mean(ln_hourly_wage, na.rm = TRUE)),
     color = "#d73027", # Aesthetic color (red)
@@
     "text",
-    x = mean(all_combined$pct, na.rm = TRUE) - 7, # Position text slightly to the right of the mean line
+    x = mean(all_combined$ln_hourly_wage, na.rm = TRUE) - 7, # Position text slightly to the right of the mean line
     y = Inf, # Position text at the top of the plot
-    label = paste("Mean:", round(mean(all_combined$pct, na.rm = TRUE), 1), "%"),
+    label = paste("Mean:", round(mean(all_combined$ln_hourly_wage, na.rm = TRUE), 1)),
     vjust = 2, # Vertical adjustment
@@
 ### End Date
+
 ```{r}
@@
 ```
+
+```{=tex}
 \vspace{1em}
 \FloatBarrier
-
+```
 ```{r}
@@
 ```
+
 \FloatBarrier
+
 The end date indicates the date that a poll ends on.
@@
 Sample size, finally, is a measure of the number of participants in each poll.
-Around 1000 participants seems to overwhelmingly be the final survey size that pollsters decide on, with only single-digit numbers of polls (with rating >= 2.5) boasting more than four thousand respondents.
+Around 1000 participants seems to overwhelmingly be the final survey size that pollsters decide on, with only single-digit numbers of polls (with rating \>= 2.5) boasting more than four thousand respondents.
 
@@
 ### Logistic models
+
 Define $y_i$ as the binary outcome variable indicating whether Harris wins (1) or not (0) for the $i^{th}$ observation.
@@
 
+```{=tex}
 \begin{align} y_i &\sim \text{Bernoulli}(p_i) 
 \\ \text{logit}(p_i) &= \beta_0 + \beta_1 x_{1i} + \beta_2 x_{2i} + \beta_3 x_{3i} + \beta_4 x_{4i} \end{align}
-
+```
 Line (1) specifies that the outcome variable $y_i$ follows a Bernoulli distribution with probability $p_i$ of success (i.e., Harris winning).
@@
 ### Multiple linear regression models
+
 Define $y_i$ as the percentage national support for Harris or Trump for the $i^{th}$ observation.
@@
 
+```{=tex}
 \begin{align} y_i &= \beta_0 + \beta_1 x_{1i} + \beta_2 x_{2i} + \beta_3 x_{3i} + \beta_4 x_{4i} \end{align}
-
+```
 Where $\beta_0$ is the intercept term, and $\beta_1, \beta_2, \beta_3, \beta_4$ are coefficients corresponding to each predictor variable.
@@
 ```
+
 For the analysis of the national popular vote, the logistic model of adjusted polls possess an AUC value of 0.98, and the logistic model of unadjusted polls have an AUC of 0.94, indicating high reliability of categorization.
@@
 ```
+
 Combining with the fact that Harris requires 44 electoral votes to win and Trump requires 51, we have found using the probability function that Harris has a 38.3 chance to acquire more than 44 electoral votes, according to the probabilities and electoral votes in @tbl-result.
@@
 ```
+
 \FloatBarrier
@@
 
-# Discussion {#sec-discussion   }
+# Discussion {#sec-discussion}
 
@@
 
-# Appendix {-}
+# Appendix {.unnumbered}
+
 ## Pollster methodology overview and evaluation
+
 The Quinnipiac University Poll conducts independent polling in swing states. To analyze their methodology, we look specifically into their October 2024 Pennsylvania polls [@quinnipiac].
@@
 ## Idealised methodology
-With a $100,000 budget, our approach focuses on producing accurate state-level estimates in key battleground states, which would then inform our national forecast.
+
+With a \$100,000 budget, our approach focuses on producing accurate state-level estimates in key battleground states, which would then inform our national forecast.
 We prioritize Pennsylvania, Michigan, Wisconsin, Georgia, Arizona, and Nevada, allocating resources proportionally based on each state's electoral importance and expected margin of victory.
@@
 Probability sampling (60% of budget, i.e.
-$60k) means every member of our target population has a known, non-zero chance of being selected - this allows us to calculate proper margins of error and make statistical inferences about the population.
+\$60k) means every member of our target population has a known, non-zero chance of being selected - this allows us to calculate proper margins of error and make statistical inferences about the population.
 For this, we use dual-frame random digit dialing (RDD) for phone surveys and address-based sampling (ABS) for mail-to-web recruitment.
@@
 For non-probability sampling (40% of budget, i.e.
-$40k), where respondents' selection probabilities are unknown and not everyone has a chance of being selected, we recruit through multiple online panel vendors and use targeted social media advertising to reach traditionally underrepresented groups.
+\$40k), where respondents' selection probabilities are unknown and not everyone has a chance of being selected, we recruit through multiple online panel vendors and use targeted social media advertising to reach traditionally underrepresented groups.
 While this approach introduces potential selection bias because participants self-select into the sample, it helps reach younger voters who are less responsive to traditional survey methods [@nonprobabilitysampling].
@@
 Respondent recruitment uses multiple contact methods - mail, email, text, and phone - with attempts made at different times and days to maximize response rates.
-We offer a $10 gift card incentive for completed surveys and provide both English and Spanish language options.
+We offer a \$10 gift card incentive for completed surveys and provide both English and Spanish language options.
 This mixed-mode contact strategy helps reduce non-response bias by providing multiple ways to participate.
@@
 In this idealised methodology, consent will be asked for at the beginning of the survey, full disclosure of how information is used will be given beforehand and no self-identifiable information will be recorded (so no names, phone numbers, etc.).
-The $10 incentive is enough to hopefully make it wortile for participants' time, but also not ideally not significant enough of an incentive to make individuals suppress otherwise deal-breaking concerns with the survey purely for the sake of the incentive.
+The \$10 incentive is enough to hopefully make it wortile for participants' time, but also not ideally not significant enough of an incentive to make individuals suppress otherwise deal-breaking concerns with the survey purely for the sake of the incentive.
 
@@
 ## Idealised survey
-The survey, made using Google Forms, is linked here: https://forms.gle/pk7vDiMHwEGLMK849
-Note that the questions are identical for both the phone and online surveys bar q6.
-A copy of the survey that is identical to the one implemented in the Google Forms above is presented below:
-Thank you for participating in this survey about the 2024 U.S.
+
+The survey, made using Google Forms, is linked here: https://forms.gle/pk7vDiMHwEGLMK849 Note that the questions are identical for both the phone and online surveys bar q6.
+A copy of the survey that is identical to the one implemented in the Google Forms above is presented below: Thank you for participating in this survey about the 2024 U.S.
 Presidential Election.
@@
 
-For questions or concerns about this survey, please contact: andrew.goh@mail.utoronto.ca
-
-SCREENING SECTION:
-Q1. Are you 18 years of age or older?
-
-Yes
-No [END SURVEY]
+For questions or concerns about this survey, please contact: andrew.goh\@mail.utoronto.ca
+
+SCREENING SECTION: Q1. Are you 18 years of age or older?
+
+Yes No \[END SURVEY\]
 
@@
 
-Yes
-No [END SURVEY]
+Yes No \[END SURVEY\]
 
@@
 
-Yes
-No
-Not sure
-[If No or Not sure: Do you plan to register before the November 2024 election?]
-
-VOTING INTENTION:
-Q4. How likely are you to vote in the 2024 presidential election?
-
-Definitely will vote
-Probably will vote
-Might or might not vote
-Probably will not vote
-Definitely will not vote
+Yes No Not sure \[If No or Not sure: Do you plan to register before the November 2024 election?\]
+
+VOTING INTENTION: Q4. How likely are you to vote in the 2024 presidential election?
+
+Definitely will vote Probably will vote Might or might not vote Probably will not vote Definitely will not vote
 
@@
 
-Kamala Harris
-Donald Trump
-Another candidate (please specify)
-Would not vote
-Not sure
-
-ATTENTION CHECK:
-Q6. To ensure you're reading carefully, please select "Somewhat disagree" for this question: "I enjoy following political news."
-
-Strongly agree
-Somewhat agree
-Somewhat disagree
-Strongly disagree
-No opinion
-
-POLITICAL PREFERENCES:
-Q7. Generally speaking, you consider yourself a:
-
-Democrat
-Republican
-Independent
-Something else (please specify)
+Kamala Harris Donald Trump Another candidate (please specify) Would not vote Not sure
+
+ATTENTION CHECK: Q6. To ensure you're reading carefully, please select "Somewhat disagree" for this question: "I enjoy following political news."
+
+Strongly agree Somewhat agree Somewhat disagree Strongly disagree No opinion
+
+POLITICAL PREFERENCES: Q7. Generally speaking, you consider yourself a:
+
+Democrat Republican Independent Something else (please specify)
 
@@
 
-Very poor
-Poor
-Fair
-Good
-Excellent
-
-ISSUE PRIORITIES:
-Q9. Which ONE of the following issues is most important to you when deciding how to vote?
-
-Economy and jobs
-Immigration
-Healthcare
-Climate change
-Crime and public safety
-Education
-National security
-Abortion rights
-Gun policy
-Something else (please specify)
+Very poor Poor Fair Good Excellent
+
+ISSUE PRIORITIES: Q9. Which ONE of the following issues is most important to you when deciding how to vote?
+
+Economy and jobs Immigration Healthcare Climate change Crime and public safety Education National security Abortion rights Gun policy Something else (please specify)
 
@@
 
-Kamala Harris would do better
-Donald Trump would do better
-No difference
-Not sure
-
-Q11. Human rights and freedom of speech:
-[Same options]
-Q12. Abortion:
-[Same options]
-Q13. Healthcare:
-[Same options]
-Q14. Immigration:
-[Same options]
-Q15. National security:
-[Same options]
-
-MEDIA CONSUMPTION:
-Q16. Where do you most often get your news about politics? (Select all that apply)
-
-Network TV news (ABC, CBS, NBC)
-Cable TV news (CNN, Fox News, MSNBC)
-Local TV news
-Radio
-Print newspapers
-News websites
-Social media
-Friends and family
-Other (please specify)
+Kamala Harris would do better Donald Trump would do better No difference Not sure
+
+Q11. Human rights and freedom of speech: \[Same options\] Q12. Abortion: \[Same options\] Q13. Healthcare: \[Same options\] Q14. Immigration: \[Same options\] Q15. National security: \[Same options\]
+
+MEDIA CONSUMPTION: Q16. Where do you most often get your news about politics? (Select all that apply)
+
+Network TV news (ABC, CBS, NBC) Cable TV news (CNN, Fox News, MSNBC) Local TV news Radio Print newspapers News websites Social media Friends and family Other (please specify)
 
@@
 
-Less than 1 hour
-1-2 hours
-2-4 hours
-More than 4 hours
-
-DEMOGRAPHICS:
-Q18. What is your age?
-
-18-24
-25-34
-35-44
-45-54
-55-64
-65 or older
+Less than 1 hour 1-2 hours 2-4 hours More than 4 hours
+
+DEMOGRAPHICS: Q18. What is your age?
+
+18-24 25-34 35-44 45-54 55-64 65 or older
 
@@
 
-Male
-Female
-Non-binary/Other
-Prefer not to say
+Male Female Non-binary/Other Prefer not to say
 
@@
 
-White
-Black or African American
-Hispanic or Latino
-Asian
-Native American
-Other (please specify)
-Prefer not to say
+White Black or African American Hispanic or Latino Asian Native American Other (please specify) Prefer not to say
 
@@
 
-Less than high school
-High school graduate
-Some college
-Associate's degree
-Bachelor's degree
-Graduate degree
-Prefer not to say
+Less than high school High school graduate Some college Associate's degree Bachelor's degree Graduate degree Prefer not to say
 
@@
 
-Under $25,000
-$25,000-$49,999
-$50,000-$74,999
-$75,000-$99,999
-$100,000-$149,999
-$150,000 or more
-Prefer not to say
-
-CONSISTENCY CHECK:
-Q23. Looking ahead to November 2024, if Kamala Harris is the Democratic nominee and Donald Trump is the Republican nominee, how do you think you will vote?
-
-Kamala Harris
-Donald Trump
-Another candidate (please specify)
-Would not vote
-Not sure
-
-[END OF SURVEY]
-Thank you for completing this survey about the 2024 U.S. Presidential Election. Your responses will help us better understand voter preferences and political attitudes across the country.
-If you have any questions about this research or would like to be informed about the results, please contact andrew.goh@mail.utoronto.ca.
+Under \$25,000 \$25,000-\$49,999 \$50,000-\$74,999 \$75,000-\$99,999 \$100,000-\$149,999 \$150,000 or more Prefer not to say
+
+CONSISTENCY CHECK: Q23. Looking ahead to November 2024, if Kamala Harris is the Democratic nominee and Donald Trump is the Republican nominee, how do you think you will vote?
+
+Kamala Harris Donald Trump Another candidate (please specify) Would not vote Not sure
+
+\[END OF SURVEY\] Thank you for completing this survey about the 2024 U.S.
+Presidential Election.
+Your responses will help us better understand voter preferences and political attitudes across the country.
+If you have any questions about this research or would like to be informed about the results, please contact andrew.goh\@mail.utoronto.ca.
 Your time and participation is greatly appreciated.
@@
 ## Diagnostics
+
 ```{r}
@@
 ```
+
 ```{r}

### 2024-12-03 paper/paper.qmd
updated paper

@@
 abstract: "Economic returns to education are a key driver of socioeconomic mobility, yet they are not distributed equally across all income groups.
-Using data from the China Family Panel Studies (CFPS) between 2010 and 2020, this paper examines how family income influences the financial benefits individuals gain from education.
+Using data from the China Family Panel Studies (CFPS) between 2010 and 2020, this paper analyzes how family income influences the financial benefits individuals gain from education.
 The analysis reveals that individuals from wealthier families consistently enjoy significantly higher income returns from education compared to their lower-income counterparts, though this gap did not widen over the decade studied.
@@
 
-All data utilized in this study were sourced from various iterations of the China Family 
-Community Survey [@cfps].
+All data utilized in this study were sourced from various iterations of the China Family Community Survey [@cfps].
 The CFPS is a nationwide community survey funded by 985 Program of Peking University and carried out by the Institute of Social Science Survey of Peking University.
@@
 The outcome variable of the model is the natural logarithm of individuals' hourly wages.
+This variable is not directly available in CFPS.
+It was calculated by dividing individuals' yearly work hours from their yearly income.
 @fig-outcome shows its distribution in the aggregated survey data from all CFPS iterations between 2010 and 2020.
@@
 #| label: fig-outcome
-#| fig-cap: Percentage Support in US Presidential Polls
+#| fig-cap: Natural Log of Individual Hourly Wage, CFPS2010 to CFPS2020
 #| echo: false
@@
     "text",
-    x = mean(all_combined$ln_hourly_wage, na.rm = TRUE) - 7, # Position text slightly to the right of the mean line
+    x = mean(all_combined$ln_hourly_wage, na.rm = TRUE) - 3, # Position text slightly to the right of the mean line
     y = Inf, # Position text at the top of the plot
@@
 
-The aggregated polling data includes support percentages of different presidential candidates in polls with different FiveThirtyEight ratings [@5382] across two elections.
-
-As displayed by @fig-outcome, the distribution of support percentages is close to a normal distribution, with most data points between 45 and 52 percent.
+As displayed by @fig-outcome, the distribution of the natural log of hourly wage is close to a normal distribution, with a mean of 2.2 and most data points between 0 and 5.
+However, the range of values extends from around -9 to 12, representing individuals with extremely low and high income.
 
@@
 
-The predictor variables that we ended up using in our final logistic regression model were the poll end dates, transparency score, and sample sizes of the polls, as well as whether or not a poll was sponsored.
-The poll end dates were included to capture the temporal changes in candidates' support rate.
-Transparency score was selected as an identification of the polls' trustworthiness, which must be controlled for in the analysis.
-Other variables representing the poll quality in the raw dataset, such as the poll score and the FiveThirtyEight rating, were excluded from the models for two reasons.
-First, the documentation by FiveThirtyEight suggests that the numeric rating, poll score, and transparency score are highly related [@5382].
-Second, the data cleaning process filtered data points with high FiveThirtyEight ratings and poll scores.
-The distributions of selected variables are as follows:
-
-### End Date
-
-```{r}
-#| label: fig-dates-past
-#| fig-cap: Distribution of Poll End Date, 2020 Cycle
-#| echo: false
-#| message: false
-#| warning: false
-
-ggplot(all_combined %>% filter(cycle == 2020), aes(x = end_date)) +
-  geom_histogram(binwidth = 7, fill = "#1f78b4", color = "white", alpha = 0.7) +
+### Years of Education Received
+
+Years of education is selected as the primary predictor in the model to identify economic returns to education. The theoretical framework for the model will be explained in @sec-model.
+
+```{r}
+#| label: fig-edu
+#| fig-cap: Years of Education Received, CFPS2010 to CFPS2020
+#| echo: false
+#| message: false
+#| warning: false
+
+ggplot(all_combined, aes(x = years_of_education)) +
+  geom_histogram(
+    binwidth = 1,
+    fill = "#2c7bb6", # Aesthetic fill color (steel blue)
+    color = "white", # Border color for bins
+    alpha = 1 # Transparency of the fill
+  ) +
   labs(
-    x = "End Date",
-    y = "Number of Polls"
-  ) +
-  scale_x_date(date_labels = "%b %d, %Y", date_breaks = "1 month") +
-  theme_minimal() +
+    x = "Years of Education",
+    y = "Frequency"
+  ) +
+  theme_minimal(base_size = 14) + # Minimal theme with increased base font size
   theme(
-    plot.title = element_text(size = 14, face = "bold"),
-    axis.text.x = element_text(angle = 45, hjust = 1)
-  )
-```
-
-```{=tex}
-\vspace{1em}
+    plot.title = element_text(
+      size = 16,
+      face = "bold",
+      hjust = 0.5, # Center the title
+      margin = margin(b = 10) # Add space below the title
+    ),
+    plot.subtitle = element_text(
+      size = 12,
+      hjust = 0.5,
+      margin = margin(b = 20) # Add space below the subtitle
+    ),
+    axis.title = element_text(face = "bold"), # Bold axis titles
+    axis.text = element_text(color = "gray30"), # Dark gray axis text
+    panel.grid.major = element_line(color = "gray80"), # Light gray major grid lines
+    panel.grid.minor = element_blank() # Remove minor grid lines
+  ) +
+  # Add a vertical line for the mean percentage support
+  geom_vline(
+    aes(xintercept = mean(years_of_education, na.rm = TRUE)),
+    color = "#d73027", # Aesthetic color (red)
+    linetype = "dashed",
+    size = 1
+  ) +
+  # Annotate the mean value on the plot
+  annotate(
+    "text",
+    x = mean(all_combined$years_of_education, na.rm = TRUE) + 2.5, # Position text slightly to the right of the mean line
+    y = Inf, # Position text at the top of the plot
+    label = paste("Mean:", round(mean(all_combined$years_of_education, na.rm = TRUE), 1)),
+    vjust = 2, # Vertical adjustment
+    color = "#d73027",
+    size = 5,
+    fontface = "bold"
+  )
+```
+
 \FloatBarrier
-```
-```{r}
-#| label: fig-dates-current
-#| fig-cap: Distribution of Poll End Date, 2024 Cycle
-#| echo: false
-#| message: false
-#| warning: false
-
-ggplot(all_combined %>% filter(cycle == 2024), aes(x = end_date)) +
-  geom_histogram(binwidth = 7, fill = "#1f78b4", color = "white", alpha = 0.7) +
+
+As shown in @fig-edu, most individuals in the aggregate dataset take very specific values, such as 9, 12, and 15.
+This is because most iterations of the CFPS record education received as the highest level of education completed.
+During the data cleaning process, they were translated to their corresponding number of years.
+For example, an individual who completed high school receives a 12 for years of education.
+I am aware that this could be highly inaccurate, as individuals may skip or repeat a grade.
+This is a limitation of the study that will be fully discussed in @sec-discussion.
+
+### Gender
+
+In light of the burgeoning prominence of the gender wage gap as a global sociological concern in recent decades, extensive research has been undertaken to discern the connection between gender and income.
+Scholars discovered that Chinese females earned 84.4 percent of male wages in 1988 and 82.5 percent in 1995 [@GustafssonLi2000].
+Zhang identified a 38.23 percent wage gap using 2004 data, demonstrating an exacerbation of the issue over time [@Zhang2006].
+
+Beyond merely influencing wage, studies have found a direct bearing of gender on educational returns, particularly in China.
+Gustafsson and Li found that in 1988, a college diploma raised a woman’s income by 10.2 percent and a man’s income by 8.9 percent compared to high school graduates [@GustafssonLi2000].
+In 1995, the values changed to 20.8 percent for women 15.5 percent for men.
+A more recent study questioned the real magnitude of the gender-based difference in educational returns, as Chinese couples often pool income together, and many females have access to their spouse’s income [@Hannum2013].
+Nevertheless, the role of gender as a determinant influencing wage and educational returns is well-established.
+Thus, it was included as a predictor.
+
+```{r}
+#| label: fig-gender
+#| fig-cap: Gender of Respondent, CFPS2010 to CFPS2020
+#| echo: false
+#| message: false
+#| warning: false
+
+ggplot(all_combined, aes(x = factor(gender, levels = c(0, 1), labels = c("Female", "Male")))) +
+  geom_bar(fill = "#1f78b4", color = "white", alpha = 1) +
   labs(
-    x = "End Date",
-    y = "Number of Polls"
-  ) +
-  scale_x_date(date_labels = "%b %d, %Y", date_breaks = "1 month") +
-  theme_minimal() +
+    x = "Gender",
+    y = "Frequency"
+  ) +
+  theme_minimal(base_size = 14) + # Minimal theme with increased base font size
   theme(
-    plot.title = element_text(size = 14, face = "bold"),
-    axis.text.x = element_text(angle = 45, hjust = 1)
+    plot.title = element_text(
+      size = 16,
+      face = "bold",
+      hjust = 0.5, # Center the title
+      margin = margin(b = 10) # Add space below the title
+    ),
+    plot.subtitle = element_text(
+      size = 12,
+      hjust = 0.5,
+      margin = margin(b = 20) # Add space below the subtitle
+    ),
+    axis.title = element_text(face = "bold"), # Bold axis titles
+    axis.text = element_text(color = "gray30"), # Dark gray axis text
+    panel.grid.major = element_line(color = "gray80"), # Light gray major grid lines
+    panel.grid.minor = element_blank() # Remove minor grid lines
   )
@@
 
-The end date indicates the date that a poll ends on.
-The dates are graphed separately between the 2020 and 2024 cycles for ease of viewing.
-Notice how there is a disproportionately large uptick in the number of polls that end on the end of a month.
-
-### Sponsors
-
-```{r}
-#| label: fig-sponsored
-#| fig-cap: Number of Polls with and without Sponsors
-#| echo: false
-#| message: false
-#| warning: false
-
-ggplot(all_combined, aes(x = factor(has_sponsor, levels = c(0, 1), labels = c("No Sponsor", "Has Sponsor")))) +
-  geom_bar(fill = "#1f78b4", color = "white", alpha = 0.7) +
+@fig-gender shows that there were significantly more male CFPS respondents than female respondents throughout 2010-2020.
+
+### Work Experience
+
+Work experience is another key variable in the model for educational returns. CFPS does not directly provide data for work experience, so potential work experience was created as a substitute.
+
+Potential work experience was deduced with an individual’s age and their years of schooling.
+Established norms in labor economics prescribe the following age thresholds for labor market entry based on educational attainment: 17 for high-school dropouts, 19 for high-school graduates, 21 for high-school graduates with some college, and 23 for college graduates [@Borjas2003; @OttavianoPeri2012; @EdoRapoport2019].
+Thus, potential work experience was calculated by subtracting the corresponding value from an individual's age.
+This assumes that individuals directly enter the labor market after completing their education, which is a strong assumption.
+
+```{r}
+#| label: fig-exp
+#| fig-cap: Potential Years of Work Experience, CFPS2010 to CFPS2020
+#| echo: false
+#| message: false
+#| warning: false
+
+# Potential work experience
+ggplot(all_combined, aes(x = pot_work_years)) +
+  geom_histogram(
+    fill = "#2c7bb6", # Aesthetic fill color (steel blue)
+    color = "white", # Border color for bins
+    alpha = 1 # Transparency of the fill
+  ) +
   labs(
-    x = "Has Sponsor",
-    y = "Number of Polls"
-  ) +
-  theme_minimal() +
+    x = "Potential Years of Work Experience",
+    y = "Frequency"
+  ) +
+  coord_cartesian(xlim = c(0, 60)) +
+  theme_minimal(base_size = 14) + # Minimal theme with increased base font size
   theme(
-    plot.title = element_text(size = 14, face = "bold")
-  )
-```
-
-Has_sponsor is a categorical variable that keeps track of whether the poll is sponsored by a third party other than the one conducting the poll itself.
-This is distributed roughly 60-40, with the larger portion of polls being independently funded (i.e.
-no sponsors).
+    plot.title = element_text(
+      size = 16,
+      face = "bold",
+      hjust = 0.5, # Center the title
+      margin = margin(b = 10) # Add space below the title
+    ),
+    plot.subtitle = element_text(
+      size = 12,
+      hjust = 0.5,
+      margin = margin(b = 20) # Add space below the subtitle
+    ),
+    axis.title = element_text(face = "bold"), # Bold axis titles
+    axis.text = element_text(color = "gray30"), # Dark gray axis text
+    panel.grid.major = element_line(color = "gray80"), # Light gray major grid lines
+    panel.grid.minor = element_blank() # Remove minor grid lines
+  ) +
+  # Add a vertical line for the mean percentage support
+  geom_vline(
+    aes(xintercept = mean(pot_work_years, na.rm = TRUE)),
+    color = "#d73027", # Aesthetic color (red)
+    linetype = "dashed",
+    size = 1
+  ) +
+  # Annotate the mean value on the plot
+  annotate(
+    "text",
+    x = mean(all_combined$pot_work_years, na.rm = TRUE) + 6, # Position text slightly to the right of the mean line
+    y = Inf, # Position text at the top of the plot
+    label = paste("Mean:", round(mean(all_combined$pot_work_years, na.rm = TRUE), 1)),
+    vjust = 2, # Vertical adjustment
+    color = "#d73027",
+    size = 5,
+    fontface = "bold"
+  )
+```
 
@@
 
-### Transparency Score
-
-```{r}
-#| label: fig-transparency
-#| fig-cap: Distribution of Poll Transparency Scores
-#| echo: false
-#| message: false
-#| warning: false
-
-ggplot(all_combined, aes(x = factor(transparency_score))) +
-  geom_bar(fill = "#1f78b4", color = "white", alpha = 0.7) +
+@fig-exp shows that potential work experience is a right-skewed distribution with a mean of 17.8. This is expected, as it is unlikely for individuals to work for more than 40 years.
+
+### City Hukou Status
+
+The Hukou system in China, a household registration mechanism, classifies individuals into either rural or urban demographics based on their birth registration locale.
+Individuals with urban Hukou and live in major cities enjoy the lion share of quality education and opportunities to pursue higher education.
+According to Tam and Jiang, during the recent period of higher education expansion, urban students’ access to higher education rose sharply while rural students’ access stagnated, showing the growing advantage of urban students due to unequal distribution of educational resources [@Tam2015].
+The scholars explained the widening gap by pointing to the expansion of vocational education, which were accessible to low-performing urban students who would not have had the opportunity to pursue higher education prior to the expansion.
+However, rural students were not provided with equal opportunities in vocational education.
+
+How the Hukou system affects educational attainment is a complex topic that must be examined together with other phenomena in China.
+Local governments are responsible for educational institutions within its region, but rural governments only have a minimal proportion of the capital available to large cities; top universities are disproportionally located in major cities and are more available to individuals possessing a Hukou of those cities; migrant workers, or individuals who live in cities but do not hold a Hukou of the city they live in, do not have access to public schooling in the city and may only attend migrant schools with worse conditions and educational quality [@Wang2007].
+
+Therefore, it is no surprise that urban Hukou holders have higher wages.
+Using data from 2005, scholars found a rural Hukou worker’s wage per hour is only 64 percent of an urban Hukou worker’s [@Xing2013].
+
+```{r}
+#| label: fig-hukou
+#| fig-cap: Hukou Status of Respondent, CFPS2010 to CFPS2020
+#| echo: false
+#| message: false
+#| warning: false
+
+ggplot(all_combined, aes(x = factor(city_hukou, levels = c(0, 1), labels = c("Rural", "Urban")))) +
+  geom_bar(fill = "#1f78b4", color = "white", alpha = 1) +
   labs(
-    x = "Transparency Score",
-    y = "Number of Polls"
-  ) +
-  theme_minimal() +
+    x = "Hukou Categorization",
+    y = "Frequency"
+  ) +
+  theme_minimal(base_size = 14) + # Minimal theme with increased base font size
   theme(
-    plot.title = element_text(size = 14, face = "bold")
-  )
-```
-
-The transparency score is a metric given to a poll/pollster by 538 that measures the transparency of the methodology with which the poll is conducted.
-This is done through a 10-question yes/no checklist on how much of the methodology is available to the public - note how this is completely separate from the quality of the methodology itself.
-Each question is graded on a 0/0.5/1 scale, for a combined transparency score that ranges from 0 to 10 [@5383].
-Most polls in our dataset miss the mark on one or two criteron, netting a final transparency score of 9 - this is partially due to the data cleaning process removing many relatively worsely conducted polls.
+    plot.title = element_text(
+      size = 16,
+      face = "bold",
+      hjust = 0.5, # Center the title
+      margin = margin(b = 10) # Add space below the title
+    ),
+    plot.subtitle = element_text(
+      size = 12,
+      hjust = 0.5,
+      margin = margin(b = 20) # Add space below the subtitle
+    ),
+    axis.title = element_text(face = "bold"), # Bold axis titles
+    axis.text = element_text(color = "gray30"), # Dark gray axis text
+    panel.grid.major = element_line(color = "gray80"), # Light gray major grid lines
+    panel.grid.minor = element_blank() # Remove minor grid lines
+  )
+```
 
@@
 
-### Sample Size
-
-```{r}
-#| label: fig-sample
-#| fig-cap: Distribution of Poll Sample Sizes
-#| echo: false
-#| message: false
-#| warning: false
-
-ggplot(all_combined, aes(x = sample_size)) +
-  geom_histogram(binwidth = 500, fill = "#1f78b4", color = "white", alpha = 0.7) +
+@fig-hukou shows that there are a greater number of rural Hukou holders than urban Hukou holders among CFPS respondents.
+This accurately reflects the overall demographics of China, where the rural population is larger than the urban population.
+
+### Marital Status
+
+Studies have shown the magnifying effect of marriage on gendered income gaps, stemming from gender-based roles and expectations within familial settings.
+Wang and Wang demonstrated that unmarried Chinese men and women in 2015 had an average monthly income gap of 458.612 RMB, and married couples had a gap of 1398.80 RMB [@WangWang2020].
+Married couples with children under 18 had an income gap that is more than doubled compared to those without children.
+Mu and Xie explained the after-marriage changes by addressing that fathers acquire a confidence boost after the birth of their children and dedicate themselves in the pursuit for higher wages and a successful career [@Mu2016].
+On the other hand, mothers take the child-rearing role, accumulate less experience in the labor force, and choose less rigorous jobs to reserve energy for household work.
+
+```{r}
+#| label: fig-marry
+#| fig-cap: Marital Status of Respondent, CFPS2010 to CFPS2020
+#| echo: false
+#| message: false
+#| warning: false
+
+ggplot(all_combined, aes(x = factor(is_married, levels = c(0, 1), labels = c("Unmarried", "Married")))) +
+  geom_bar(fill = "#1f78b4", color = "white", alpha = 1) +
   labs(
-    x = "Sample Size",
-    y = "Number of Polls"
-  ) +
-  scale_x_continuous(labels = scales::comma) +
-  coord_cartesian(xlim = c(0, 6000)) +
-  theme_minimal() +
+    x = "Marital Status",
+    y = "Frequency"
+  ) +
+  theme_minimal(base_size = 14) + # Minimal theme with increased base font size
   theme(
-    plot.title = element_text(size = 14, face = "bold")
-  )
-```
-
-Sample size, finally, is a measure of the number of participants in each poll.
-Around 1000 participants seems to overwhelmingly be the final survey size that pollsters decide on, with only single-digit numbers of polls (with rating \>= 2.5) boasting more than four thousand respondents.
+    plot.title = element_text(
+      size = 16,
+      face = "bold",
+      hjust = 0.5, # Center the title
+      margin = margin(b = 10) # Add space below the title
+    ),
+    plot.subtitle = element_text(
+      size = 12,
+      hjust = 0.5,
+      margin = margin(b = 20) # Add space below the subtitle
+    ),
+    axis.title = element_text(face = "bold"), # Bold axis titles
+    axis.text = element_text(color = "gray30"), # Dark gray axis text
+    panel.grid.major = element_line(color = "gray80"), # Light gray major grid lines
+    panel.grid.minor = element_blank() # Remove minor grid lines
+  )
+```
 
@@
 
+As displayed in @fig-marry, most respondents of CFPS are married.
+
+### Communist Party Membership
+
+Membership in the Communist Party of China (CCP) is frequently included in income related research within China [@GustafssonLi2000; @Hannum2013; @Mu2016].
+Being a member of the CCP grants the opportunity for an individual to work in the government positions or state-owned enterprises that provide secure and well-paid jobs [@Dickson2014].
+Moreover, party status is also related to the level of education, as the recruitment strategy of the CCP targets elite groups such as college and graduate students.
+This study followed established protocols and included CCP membership as a predictor, as its unique socio-political status in China necessitates its inclusion.
+
+```{r}
+#| label: fig-ccp
+#| fig-cap: CCP Membership of Respondent, CFPS2010 to CFPS2020
+#| echo: false
+#| message: false
+#| warning: false
+
+ggplot(all_combined, aes(x = factor(is_party, levels = c(0, 1), labels = c("Not CCP Member", "CCP Member")))) +
+  geom_bar(fill = "#1f78b4", color = "white", alpha = 1) +
+  labs(
+    x = "Party Membership",
+    y = "Frequency"
+  ) +
+  theme_minimal(base_size = 14) + # Minimal theme with increased base font size
+  theme(
+    plot.title = element_text(
+      size = 16,
+      face = "bold",
+      hjust = 0.5, # Center the title
+      margin = margin(b = 10) # Add space below the title
+    ),
+    plot.subtitle = element_text(
+      size = 12,
+      hjust = 0.5,
+      margin = margin(b = 20) # Add space below the subtitle
+    ),
+    axis.title = element_text(face = "bold"), # Bold axis titles
+    axis.text = element_text(color = "gray30"), # Dark gray axis text
+    panel.grid.major = element_line(color = "gray80"), # Light gray major grid lines
+    panel.grid.minor = element_blank() # Remove minor grid lines
+  )
+```
+
+\FloatBarrier
+
+@fig-ccp reflects that CCP members are only make up a small proportion of the Chinese population.
+
+### Eastern Provinces
+
+China's geographical East, encompassing 12 economically advanced provinces, is characterized by notable income disparities when compared to Central and Western regions.
+Scholars found that in 2005, Eastern populations not only had significantly greater income but also enjoyed doubled returns to education compared to other regions [@Xing2013].
+Though the values shifted towards the national mean in 2011, significant differences still existed.
+Recent research endeavors on income and educational returns have increasingly incorporated the geographical East as a control variable, acknowledging its substantial influence on the variables of interest [@Dong2021].
+
+```{r}
+#| label: fig-east
+#| fig-cap: Location of Residence, CFPS2010 to CFPS2020
+#| echo: false
+#| message: false
+#| warning: false
+
+ggplot(all_combined, aes(x = factor(is_east, levels = c(0, 1), labels = c("Other Provinces", "Eastern Provinces")))) +
+  geom_bar(fill = "#1f78b4", color = "white", alpha = 1) +
+  labs(
+    x = "Area of Residency",
+    y = "Frequency"
+  ) +
+  theme_minimal(base_size = 14) + # Minimal theme with increased base font size
+  theme(
+    plot.title = element_text(
+      size = 16,
+      face = "bold",
+      hjust = 0.5, # Center the title
+      margin = margin(b = 10) # Add space below the title
+    ),
+    plot.subtitle = element_text(
+      size = 12,
+      hjust = 0.5,
+      margin = margin(b = 20) # Add space below the subtitle
+    ),
+    axis.title = element_text(face = "bold"), # Bold axis titles
+    axis.text = element_text(color = "gray30"), # Dark gray axis text
+    panel.grid.major = element_line(color = "gray80"), # Light gray major grid lines
+    panel.grid.minor = element_blank() # Remove minor grid lines
+  )
+```
+
+\FloatBarrier
+
+According to @fig-east, there exists a relatively balanced split between respondents residing in Eastern provinces and those living in other provinces.
+More individuals lived in non-Eastern provinces, counting to more than 20,000.
+
+### Family Income Quartile
+
+Family income quartile is not a variable directly incorporated in the regression model.
+Rather, data was split into subsets according to family income quartiles and regressed to find the educational returns of each quartile in comparison with one another.
+This is the focal variable of the study.
+Within the CFPS's family economics sub-survey, there exists a variable listing family income quartiles.
+For this study, family economics datasets were merged with the adult individuals dataset of the same CFPS iteration by matching personal IDs, thus deriving a corresponding family income quartile value for each adult participant.
+
+```{r}
+#| label: fig-quartiles
+#| fig-cap: Family Income Quartiles, CFPS2010 to CFPS2020
+#| echo: false
+#| message: false
+#| warning: false
+
+ggplot(all_combined, aes(x = income_quartile)) +
+  geom_bar(fill = "#1f78b4", color = "white", alpha = 1) +
+  labs(
+    x = "Family Income Quartile",
+    y = "Frequency"
+  ) +
+  theme_minimal(base_size = 14) + # Minimal theme with increased base font size
+  theme(
+    plot.title = element_text(
+      size = 16,
+      face = "bold",
+      hjust = 0.5, # Center the title
+      margin = margin(b = 10) # Add space below the title
+    ),
+    plot.subtitle = element_text(
+      size = 12,
+      hjust = 0.5,
+      margin = margin(b = 20) # Add space below the subtitle
+    ),
+    axis.title = element_text(face = "bold"), # Bold axis titles
+    axis.text = element_text(color = "gray30"), # Dark gray axis text
+    panel.grid.major = element_line(color = "gray80"), # Light gray major grid lines
+    panel.grid.minor = element_blank() # Remove minor grid lines
+  )
+```
+
+\FloatBarrier
+
+The distribution shown in @fig-quartiles is counter intuitive, as there are more individuals who belong in upper quartiles.
+This does not suggest that CFPS uses an unrepresentative sample.
+The data of individuals in upper family income quartiles are relatively more complete, thus more data points are kept after the data cleaning process.
+Despite the relative lack of data for the lower quartiles, the number of data points is still sufficient for this study.
+
 # Model {#sec-model}
 
-The goal of our modelling strategy is twofold.
-Firstly, we seek to predict the winning candidate on election day by calculating the expected win rate of Vice President Kamala Harris and Former President Donald Trump in the seven swing states: Pennsylvania, Georgia, North Carolina, Michigan, Arizona, Wisconsin, and Nevada [@nyt2024polls].
-Secondly, we hope to predict the candidate who has the popular vote on election day, controlling for the potential bias of national polls by accounting for the difference between polled popular vote and the actual popular vote on election day for the 2020 cycle.
-
-To achieve the first goal, the polls dataset was divided by individual states, and only data points from the seven swing states were selected, forming seven smaller datasets.
-Then, for each state, the harris_win variable was constructed by comparing the support rate of the candidates in each poll.
-The variable was set to 1 if the support rate of Harris is greater than or equal to Trump's support rate and 0 when Trump's support rate is greater.
-A logistic model was constructed for each state, using harris_win as the outcome and previously stated predictors as inputs.
-
-Then, after the models were constructed, we conducted 1000 simulations of election results with randomly-generated parameters.
-The date parameter was set to election day, and the other three predictor variables were simulated from a normal distribution with the mean and standard deviation of the training dataset.
-We then averaged the values to obtain our final prediction for the probability of a Harris win in the state of interest.
-
-Then, using the probabilities for each state and their respective electoral college votes, we calculated the probability that Vice President Harris successfully obtains the 44 required electoral college votes to secure the presidency.
-This is done via an R script that can be found in the end of /scripts/05-model_data.R.
-
-For the popular vote, we utilized the data from 2020 to calculate each pollster's bias by identifying the average difference between the popular vote on election day and their polled national support rates of Trump and President Joe Biden.
-Next, we adjusted the polled national support rates of pollsters in the 2024 cycle by the calculated gap in 2020.
-By making this adjustment, we are assuming that the pollsters systematically bias 2024 candidates equally compared to 2020 candidates.
-We acknowledge that the assumption is most likely false.
-Ideally, incorporating poll data from earlier election cycles may produce a more accurate indicator of how pollsters systematically bias candidates from the two dominant political parties.
-However, comprehensive poll data before 2020 is unavailable.
-Since popular vote is unrelated to the winner of the election, we are using this analysis as an exploration of methods that incorporate historical data without emphasizing predictiveness.
-Using both adjusted and unadjusted national support levels, multiple linear regressions were created with support levels as the outcome and stated predictors as inputs to predict candidates' support rate over time.
-Adjusted and unadjusted logistic regressions were made using harris_win as the outcome and the same predictors to predict the candidate with the popular vote on election day.
-The attempt to control for historical bias was not applied to the swing states due to a lack of data.
+The goal of my modelling strategy is twofold.
+First, I must split the data from each CFPS iteration into family income quartiles and adjust them to be directly comparable with one another.
+Second, I wish to calculate each quartile's returns to education, in terms of percent income increase per year of education, to complete the comparison.
+
+To accomplish the first task, Propensity Score Matching was utilized.
+
+Historically, research on returns to education primarily relied on directly calculating the rate of return using the Mincer Earnings Function.
+They incorporated control variables into the regression to account for their influence on income [@Byron1990; @Zhang2006].
+When desiring to make group comparisons, scholars generally subdivided data based on specific variables of interest such as gender, location, and industry.
+They then performed direct regressions to contrast the coefficients [@Gustafsson2000, @Mu2016].
+
+While multivariate regression effectively captures the impact of control variables, its functionality hinges on the linear relationships between the outcome and covariates.
+Dehejia and Wahba revealed that regressing groups with significant variances in the mean values of covariates could yield misleading results for the variable of interest, potentially overstating the differences between groups [@Dehejia2002].
+Propensity Score Matching (PSM) addresses this issue by isolating the treatment effect.
+Therefore, this study employed a combined method: first balancing covariates using PSM, then executing regressions to adjust for residual differences.
+
+For this study, data from each CFPS iteration were divided into four subsets based on family income quartiles.
+PSM was then applied to match each subset with others, resulting in six pairs of subsets that exhibited different treatment variable values (family income quartiles) but had similar means for control variables.
+The matching was conducted using the nearest-neighbor approach with $caliper = 0.1sd$, which is more strict compared to the generally recommended 0.2 threshold for caliper width [@Austin2011].
+This choice was intentional, as reducing the caliper width improved the covariate balance without significantly reducing the number of data points.
+Given that lower family income quartiles had fewer data points, match ratios were adjusted based on the counts within the quartiles being matched.
+
+Table 2 provides a summary of balance for the match between the Quartile 1 and the Quartile 2 subset of CFPS 2020.
+The match was executed using caliper = 0.1 and a ratio of 2, matching 1041 Quartile 2 instances out of 1324 total instances with all 541 Quartile 1 instances.
+This matching procedure was repeated 6 times to compare each quartile with every other quartile for all 6 CFPS iterations from 2010 to 2020.
+The standard mean differences of matches using caliper = 0.2 and 0.5 were included as a comparison.
+The caliper of 0.1 returned the best standardized mean difference of 0.0139 between propensity scores of Q1 and Q2.
+Caliper widths of 0.2 and 0.5 returned 0.0338 and 0.0795, respectively.
+
+TABLE HERE IF TIME
+
+For the second task, a multivariate regression model was created using the theoretical framework of the Mincer Earnings Function [@Mincer1974].
+The function depicts wage as a function of schooling and work experience.
+Its original form is:
+$$ln(w) = f(s, x) = ln(w_0) +\rho s + \beta_1x + \beta_2x^2$$
+Where $w$ is hourly wage, $w_0$ is the wage level of an individual with 0 years of schooling and work experience, $s$ is years of schooling, $x$ is work experience, and $\rho$, $\beta_1$, and $\beta_2$ are coefficients that can be viewed as the rates of return to schooling and work experience.
+
+Numerous researchers have since tailored the Mincer equation by incorporating potential confounders, ensuring the mitigation of biased outcomes.
+A seminal study analyzing Chinese educational returns used the function:
+$$ln(Y) = α_0 +α_1Edu +α_2Exper +α_3Exper^2+∑λ_jX+μ$$
+Which adds $X$ that represents control variables such as age, gender, and geographical location [@Zhang2006].
+Analogous modifications can be observed globally, although with variable inclusions that reflect regional societal and cultural differences.
+For example, an Indian study choose to include caste, relationship to the head of household, and the ability to speak and write English in the equation as control variables [@Bhandari2006].
+This research also leaned on a modified version of the Mincer Earnings Function for its calculations on educational returns.
 
@@
 
-### Logistic models
-
-Define $y_i$ as the binary outcome variable indicating whether Harris wins (1) or not (0) for the $i^{th}$ observation.
-$x_{1i}$ is the end_date for the $i^{th}$ observation.
-$x_{2i}$ is the binary value of has_sponsor for the $i^{th}$ observation.
-$x_{3i}$ is the transparency_score for the $i^{th}$ observation.
-$x_{4i}$ is the sample_size for the $i^{th}$ observation.
-
-The logistic regression model can be expressed as follows:
-
-```{=tex}
-\begin{align} y_i &\sim \text{Bernoulli}(p_i) 
-\\ \text{logit}(p_i) &= \beta_0 + \beta_1 x_{1i} + \beta_2 x_{2i} + \beta_3 x_{3i} + \beta_4 x_{4i} \end{align}
-```
-Line (1) specifies that the outcome variable $y_i$ follows a Bernoulli distribution with probability $p_i$ of success (i.e., Harris winning).
-Line (2) links the linear combination of predictors to the probability $p_i$, where $\beta_0$ is the intercept term, and $\beta_1, \beta_2, \beta_3, \beta_4$ are coefficients corresponding to each predictor variable above.
-
-This logistic regression model was applied independently to the data on each swing state and the adjusted and unadjusted popular vote polls.
-
-### Multiple linear regression models
-
-Define $y_i$ as the percentage national support for Harris or Trump for the $i^{th}$ observation.
-$x_{1i}$ is the end_date for the $i^{th}$ observation.
-$x_{2i}$ is the binary value of has_sponsor for the $i^{th}$ observation.
-$x_{3i}$ is the transparency_score for the $i^{th}$ observation.
-$x_{4i}$ is the sample_size for the $i^{th}$ observation.
-
-The multiple linear regression model can be expressed as follows:
-
-```{=tex}
-\begin{align} y_i &= \beta_0 + \beta_1 x_{1i} + \beta_2 x_{2i} + \beta_3 x_{3i} + \beta_4 x_{4i} \end{align}
-```
-Where $\beta_0$ is the intercept term, and $\beta_1, \beta_2, \beta_3, \beta_4$ are coefficients corresponding to each predictor variable.
-
-Separate multiple linear regression models were applied to the polled national support rate of Harris and Trump, with and without adjustments from historical data.
-
-### Model justification
-
-We decided to use a logistic model to predict the winner on election day because it directly outputs candidates' chance of winning each swing state, enabling us to use a probabilistic function to identify their overall chance of winning.
-Comparatively, a linear regression model merely predicts the level of support for candidates, which fails to identify a winner.
+### Multivariate regression models
+
+Employing PSM-matched subsets, the educational returns for different family income quartile groups were computed using the modified Mincer Function:
+$$ ln(w) = α_0 +α_1Edu +α_2Exp +α_3Exp^2 +α_4Gender \\ +α_5Hukou +α_6Marriage +α_7CCP +α_8East +μ$$
+With $w$ representing hourly wage, $α_1$ representing returns to education and other coefficients representing the effects of previously identified covariates on the natural log of income.
+
+Next, PSM-matched subset pairs were separated by family income quartiles and regressed independently to identify the differences between educational returns and the coefficients of covariates.
+
+Finally, the Delta coefficient $\alpha_1$ from all paired comparisons across every CFPS iteration were compiled together.
+5% t-tests were carried out on the data from each iteration to discern if the differences in educational returns between quartiles were statistically significant.
 

### 2024-12-03 scripts/05-model_data.R
updated script

@@ -13,762 +13,52 @@
 
 #### Workspace setup ####
 
-library("car")
-library("tidyverse")
-library("haven")
-library("dplyr")
+library(car)
+library(tidyverse)
 library(MatchIt)
-library("tidyr")
-library(ggplot2)
 
-# 2020 data
 # import datasets
-cfps2020person_raw <- read_sas("/Users/yisuhou/Desktop/cfps2020person_202306.sas7bdat", 
-                               NULL)
-cfps2020famecon <- read_sas("/Users/yisuhou/Desktop/cfps2020famecon_202306.sas7bdat",
-                            NULL)
-
-# Join reshaped family dataset with individual dataset
-cfps2020person <- cfps2020person_raw |>
-  left_join(cfps2020famecon, by = "fid20")
-
-
-# new varialbe: years of education
-cfps2020person <- mutate(cfps2020person, years_of_education = case_when(
-  W01 == 0 ~ 0,
-  W01 == 10 ~ 0,
-  W01 == 3 ~ 6,
-  W01 == 4 ~ 9,
-  W01 == 5 ~ 12,
-  W01 == 6 ~ 15,
-  W01 == 7 ~ 16,
-  W01 == 8 ~ 19,
-  W01 == 9 ~ 22,
-))
-
-# new variable: years out of school
-# 2020 - year of leaving school
-cfps2020person <- mutate(cfps2020person, pot_work_years 
-                         = case_when(
-                           is.na(age) | age < 0 | years_of_education < 0 ~ NA,
-                           years_of_education == 0 ~ age - 16,
-                           years_of_education == 6 ~ age - 16,
-                           years_of_education == 9 ~ age - 17,
-                           years_of_education == 12 ~ age - 19,
-                           years_of_education == 15 ~ age - 22,
-                           years_of_education == 16 ~ age - 23,
-                           years_of_education == 19 ~ age - 26,
-                           years_of_education == 22 ~ age - 29
-                         ))
-
-cfps2020person <- mutate(cfps2020person, exp2 = pot_work_years^2)
-
[…]

### 2024-12-03 scripts/05-model_data.R
updated models

@@ -5,8 +5,7 @@
 # Contact: yisu.hou@mail.utoronto.ca
 # License: None
 # Pre-requisites:
-# - Packages `tidyverse`, `caret`, `glmnet`, `nnet`, `lubridate`, `pROC`,
-#   `stringr`, and `gt` must be installed
+# - Packages `tidyverse`, `car`, `glmnet`, and `MatchIt` must be installed
 # - 02-clean_data.R, 03-test_analysis_data.R,
 #   and 04-exploratory_data_analysis.R must have been run
 
@@ -57,19 +56,1545 @@ quartile_2_2010 <- subset(data_2010, income_quartile == 2)
 quartile_3_2010 <- subset(data_2010, income_quartile == 3)
 quartile_4_2010 <- subset(data_2010, income_quartile == 4)
 
+#### 2020 Analysis ####
+# compare quartile 1 and 2
+quartile_1_2020$treatment = 1
+quartile_2_2020$treatment = 0
+
+quartile_1_2_compare_2020 <- rbind(quartile_1_2020, quartile_2_2020)
+
+# Perform propensity score matching
+m.out <- matchit(treatment ~ gender + pot_work_years 
+                 + city_hukou + is_married + is_party + is_east, 
+                 data = quartile_1_2_compare_2020, method = "nearest",
+                 distance = "logit", caliper = 0.1, ratio = 2)
+
+# Check the matching result
+summary(m.out)
+
+# arriving at the matched sample
+matched_data <- match.data(m.out)
+
+# using the Mincer Equation to fit both groups in the matched sample
+lm_fit_q1 <- lm(ln_hourly_wage ~ years_of_education + pot_work_years + exp2
+                + city_hukou + is_married + gender + is_east
+                + is_party, data = matched_data, subset = income_quartile == 1)
+lm_fit_q2 <- lm(ln_hourly_wage ~ years_of_education + pot_work_years + exp2
+                + city_hukou + is_married + gender + is_east
+                + is_party, data = matched_data, subset = income_quartile == 2)
+
+# Display the result
+summary(lm_fit_q1)
+summary(lm_fit_q2)
+
+# Save Models
+saveRDS(
+  lm_fit_q1,
+  file = "models/edu_returns_2020_q1_q1vsq2.rds"
+)
+
+saveRDS(
+  lm_fit_q2,
+  file = "models/edu_returns_2020_q2_q1vsq2.rds"
+)
+
+
+# quartile 1 vs quartile 3
+quartile_1_2020$treatment = 1
[…]

### 2024-12-04 paper/paper.qmd
updated paper and references

@@
 library(gt)
-library(broom)
 library(knitr)
+library(kableExtra)
 library(MatchIt)
@@
 Caret [@caret], glmnet [@glmnet; @glmnet2; @glmnet3], nnet [@nnet], tidyverse [@tidyverse], car [@car] MatchIt [@matchit] and arrow [@arrow] were used directly in the analysis of the data.
-Stringr [@stringr], dplyr [@dplyr], gt [@gt], knitr [@knitr], and styler [@styler] were used in the presentation and/or styling of the data, graphs, and paper as a whole.
+Stringr [@stringr], dplyr [@dplyr], gt [@gt], knitr [@knitr], kableExtra [@kextra] and styler [@styler] were used in the presentation and/or styling of the data, graphs, and paper as a whole.
 
@@
 For the purposes of this research, data was extracted from CFPS for the years 2010, 2012, 2014, 2016, 2018, and 2020.
-
-After cleaning the data to split results by candidate, removing polls with N/A values and ratings lower than 2.5, and further selecting polls polling likely voters as opposed to the whole population, we are left with 746 data points with the variables pollster, has_sponsor, numeric_grade, pollscore, transparency_score, sample_size, end_date, state, candidate_name, pct (support rate in percentage), and cycle (election cycle, i.e.
-2020/2024).
 
@@
 
-Table 2 provides a summary of balance for the match between the Quartile 1 and the Quartile 2 subset of CFPS 2020.
+To show the effects of PSM, @tbl-match provides a summary of balance for the match between the Quartile 1 and the Quartile 2 subset of CFPS 2020.
 The match was executed using caliper = 0.1 and a ratio of 2, matching 1041 Quartile 2 instances out of 1324 total instances with all 541 Quartile 1 instances.
 This matching procedure was repeated 6 times to compare each quartile with every other quartile for all 6 CFPS iterations from 2010 to 2020.
-The standard mean differences of matches using caliper = 0.2 and 0.5 were included as a comparison.
-The caliper of 0.1 returned the best standardized mean difference of 0.0139 between propensity scores of Q1 and Q2.
-Caliper widths of 0.2 and 0.5 returned 0.0338 and 0.0795, respectively.
-
-TABLE HERE IF TIME
+
+```{r}
+#| label: tbl-match
+#| tbl-cap: Summary of Balance for Quartile 1 vs Quartile 2 Match, 2020 Data
+#| echo: false
+#| message: false
+#| warning: false
+
+# Data computed from model_data script
+data <- data.frame(
+  Variables = c("distance", "Gender", "Work exp", "City Hukou", "Marital Status", "CCP", "East"),
+  `Means Q1` = c(0.3016, 0.5712, 14.8817, 0.1072, 0.7375, 0.0240, 0.2810),
+  `Means Q2` = c(0.2854, 0.5650, 14.1767, 0.1971, 0.7515, 0.0219, 0.3112),
+  `Std Mean Diff` = c(0.3099, 0.0125, 0.0866, -0.2907, -0.0318, 0.0139, -0.0672),
+  `Means Q1 Matched` = c(0.3016, 0.5712, 14.8817, 0.1072, 0.7375, 0.0240, 0.2810),
+  `Means Q2 Matched` = c(0.3009, 0.5675, 14.7902, 0.1100, 0.7366, 0.0222, 0.2810),
+  `Std Mean Diff M` = c(0.0139, 0.0075, 0.0112, -0.0090, 0.0021, 0.0121, 0.0000)
+)
+
+kable(
+  data,
+  format = "latex"
+) %>%
+  kable_styling(
+    latex_options = c("striped", "hold_position", "scale_down"), 
+    position = "center",
+    full_width = FALSE
+  )
+```
+\FloatBarrier
 
@@
 
+It is acknowledged that the regression models may be inconsistent due to the inconsistencies in the variables and measurements of different CFPS iterations.
+The incorporation of calculated variables is an additional factor impacting the models' ability to calculate returns to education.
+
 ## Model set-up
@@
 
-Finally, the Delta coefficient $\alpha_1$ from all paired comparisons across every CFPS iteration were compiled together.
-5% t-tests were carried out on the data from each iteration to discern if the differences in educational returns between quartiles were statistically significant.
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-
-# Regional polls analysis
-trump_2024_regional <- trump_2024_lower %>% filter(state != "National")
-harris_2024_regional <- harris_2024_lower %>% filter(state != "National")
-
-trump_Pennsylvania <- trump_2024_regional %>% filter(state == "Pennsylvania")
-trump_Georgia <- trump_2024_regional %>% filter(state == "Georgia")
-trump_North_Carolina <- trump_2024_regional %>% filter(state == "North Carolina")
-trump_Michigan <- trump_2024_regional %>% filter(state == "Michigan")
-trump_Arizona <- trump_2024_regional %>% filter(state == "Arizona")
-trump_Wisconsin <- trump_2024_regional %>% filter(state == "Wisconsin")
-trump_Nevada <- trump_2024_regional %>% filter(state == "Nevada")
-
-harris_Pennsylvania <- harris_2024_regional %>% filter(state == "Pennsylvania")
-harris_Georgia <- harris_2024_regional %>% filter(state == "Georgia")
-harris_North_Carolina <- harris_2024_regional %>% filter(state == "North Carolina")
-harris_Michigan <- harris_2024_regional %>% filter(state == "Michigan")
-harris_Arizona <- harris_2024_regional %>% filter(state == "Arizona")
-harris_Wisconsin <- harris_2024_regional %>% filter(state == "Wisconsin")
-harris_Nevada <- harris_2024_regional %>% filter(state == "Nevada")
-
-combined_Pennsylvania <- full_join(
-  trump_Pennsylvania,
-  harris_Pennsylvania,
-  by = c(
-    "pollster", "has_sponsor", "pollscore",
-    "transparency_score", "sample_size", "end_date", "state", "cycle"
-  )
-)
-
-combined_Georgia <- full_join(
-  trump_Georgia,
-  harris_Georgia,
-  by = c(
-    "pollster", "has_sponsor", "pollscore",
-    "transparency_score", "sample_size", "end_date", "state", "cycle"
-  )
-)
-
-combined_North_Carolina <- full_join(
-  trump_North_Carolina,
-  harris_North_Carolina,
-  by = c(
-    "pollster", "has_sponsor", "pollscore",
-    "transparency_score", "sample_size", "end_date", "state", "cycle"
-  )
-)
-
-combined_Michigan <- full_join(
-  trump_Michigan,
-  harris_Michigan,
-  by = c(
-    "pollster", "has_sponsor", "pollscore",
-    "transparency_score", "sample_size", "end_date", "state", "cycle"
-  )
-)
-
-combined_Arizona <- full_join(
-  trump_Arizona,
-  harris_Arizona,
-  by = c(
-    "pollster", "has_sponsor", "pollscore",
-    "transparency_score", "sample_size", "end_date", "state", "cycle"
-  )
-)
-
-combined_Wisconsin <- full_join(
-  trump_Wisconsin,
-  harris_Wisconsin,
-  by = c(
-    "pollster", "has_sponsor", "pollscore",
-    "transparency_score", "sample_size", "end_date", "state", "cycle"
-  )
-)
-
-combined_Nevada <- full_join(
-  trump_Nevada,
-  harris_Nevada,
-  by = c(
-    "pollster", "has_sponsor", "pollscore",
-    "transparency_score", "sample_size", "end_date", "state", "cycle"
-  )
-)
-
-# mutate harris_win variable by comparing polled support rates
-# preparing data for logistic regression
-combined_Pennsylvania <- combined_Pennsylvania %>% mutate(
-  harris_win = case_when(
-    pct.y >= pct.x ~ 1,
-    pct.y < pct.x ~ 0
-  )
-)
-
-combined_Georgia <- combined_Georgia %>% mutate(
-  harris_win = case_when(
-    pct.y >= pct.x ~ 1,
-    pct.y < pct.x ~ 0
-  )
-)
-
-combined_North_Carolina <- combined_North_Carolina %>% mutate(
-  harris_win = case_when(
-    pct.y >= pct.x ~ 1,
-    pct.y < pct.x ~ 0
-  )
-)
-
-combined_Michigan <- combined_Michigan %>% mutate(
-  harris_win = case_when(
-    pct.y >= pct.x ~ 1,
-    pct.y < pct.x ~ 0
-  )
-)
-
-combined_Arizona <- combined_Arizona %>% mutate(
-  harris_win = case_when(
-    pct.y >= pct.x ~ 1,
-    pct.y < pct.x ~ 0
-  )
-)
-
-combined_Wisconsin <- combined_Wisconsin %>% mutate(
-  harris_win = case_when(
-    pct.y >= pct.x ~ 1,
-    pct.y < pct.x ~ 0
-  )
-)
-
-combined_Nevada <- combined_Nevada %>% mutate(
-  harris_win = case_when(
-    pct.y >= pct.x ~ 1,
-    pct.y < pct.x ~ 0
-  )
-)
-
-# Create 7 different logistic regressions to predict Harris's win rate
-# in each state
-logistic_Pennsylvania <- readRDS(here::here("models/Logistic_model_Pennsylvania.rds"))
-
-logistic_Georgia <- readRDS(here::here("models/Logistic_model_Georgia.rds"))
-
-logistic_North_Carolina <- readRDS(here::here("models/Logistic_model_North_Carolina.rds"))
-
-logistic_Michigan <- readRDS(here::here("models/Logistic_model_Michigan.rds"))
-
-logistic_Arizona <- readRDS(here::here("models/Logistic_model_Arizona.rds"))
-
-logistic_Wisconsin <- readRDS(here::here("models/Logistic_model_Wisconsin.rds"))
-
-logistic_Nevada <- readRDS(here::here("models/Logistic_model_Nevada.rds"))
-
-# test logistic models for state specific analysis
-# mutate fitted values
-
-combined_Pennsylvania <- combined_Pennsylvania %>%
-  mutate(
-    harris_win_prob = round(100 * predict(logistic_Pennsylvania, type = "response"), 2)
-  )
-
-roc_obj_Pennsylvania <- roc(
-  combined_Pennsylvania$harris_win,
-  combined_Pennsylvania$harris_win_prob
-)
-
-auc_value_Pennsylvania <- auc(roc_obj_Pennsylvania)
-
-combined_Georgia <- combined_Georgia %>%
-  mutate(
-    harris_win_prob = round(100 * predict(logistic_Georgia, type = "response"), 2)
-  )
-
-roc_obj_Georgia <- roc(
-  combined_Georgia$harris_win,
-  combined_Georgia$harris_win_prob
-)
-
-auc_value_Georgia <- auc(roc_obj_Georgia)
-
-combined_North_Carolina <- combined_North_Carolina %>%
-  mutate(
-    harris_win_prob = round(100 * predict(logistic_North_Carolina, type = "response"), 2)
-  )
-
-roc_obj_North_Carolina <- roc(
-  combined_North_Carolina$harris_win,
-  combined_North_Carolina$harris_win_prob
-)
-
-auc_value_North_Carolina <- auc(roc_obj_North_Carolina)
-
-combined_Michigan <- combined_Michigan %>%
-  mutate(
-    harris_win_prob = round(100 * predict(logistic_Michigan, type = "response"), 2)
-  )
-
-roc_obj_Michigan <- roc(
-  combined_Michigan$harris_win,
-  combined_Michigan$harris_win_prob
-)
-
-auc_value_Michigan <- auc(roc_obj_Michigan)
-
-combined_Arizona <- combined_Arizona %>%
-  mutate(
-    harris_win_prob = round(100 * predict(logistic_Arizona, type = "response"), 2)
-  )
-
-roc_obj_Arizona <- roc(
-  combined_Arizona$harris_win,
-  combined_Arizona$harris_win_prob
-)
-
-auc_value_Arizona <- auc(roc_obj_Arizona)
-
-combined_Wisconsin <- combined_Wisconsin %>%
-  mutate(
-    harris_win_prob = round(100 * predict(logistic_Wisconsin, type = "response"), 2)
-  )
-
-roc_obj_Wisconsin <- roc(
-  combined_Wisconsin$harris_win,
-  combined_Wisconsin$harris_win_prob
-)
-
-auc_value_Wisconsin <- auc(roc_obj_Wisconsin)
-
-combined_Nevada <- combined_Nevada %>%
-  mutate(
-    harris_win_prob = round(100 * predict(logistic_Nevada, type = "response"), 2)
-  )
-
-roc_obj_Nevada <- roc(
-  combined_Nevada$harris_win,
-  combined_Nevada$harris_win_prob
-)
-
-auc_value_Nevada <- auc(roc_obj_Nevada)
-```
-
-We identified the AUC values and ROC plots for each of the seven swing-state logistic regressions.
-The ROC plots are presented in the Additional Data Details section (@sec-model-details), from @fig-pen to @fig-nev.
-The AUC values are: 0.90 for Pennsylvania, 0.88 for Georgia, 0.74 for North Carolina, 0.93 for Michigan, 1.00 for Arizona, 0.86 for Wisconsin, and 0.65 for Nevada.
-All states other than Nevada have acceptable or excellent AUC values, indicating that the respective logistic models are reliable when distinguishing cases where Harris wins.
-The low AUC value for Nevada is potentially caused by the limited sample size; there are only 9 polls conducted in Nevada.
-
-Moreover, the sample size restrictions were the reason why we did not use training and testing data to validate our logistic models.
-The state with the greatest number of polls, Pennsylvania, only records 26 polls.
-Utilizing training and testing datasets implies that the datasets may include only a couple of data points in some states, which is insufficient to construct or test the model.
-On top of that, according to [@trainingerror], achieving low training error, such as by using a training-MSE-minimising regression model such as our own, is sufficient to ensure the predictive capabilities of a model bounded by some constant variance term.
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-
-# find biases of pollsters from 2020 national polls data
-# filter out national polls from the datasets
-trump_2024_national <- trump_2024 %>% filter(state == "National")
-harris_2024_national <- harris_2024 %>% filter(state == "National")
-trump_2020_national <- trump_2020 %>% filter(state == "National")
-biden_2020_national <- biden_2020 %>% filter(state == "National")
-
-# Define actual results
-actual_results_2020 <- list(Trump_pct = 47, Biden_pct = 51)
-
-# Calculate bias per pollster
-rep_pollster_bias <- trump_2020_national %>%
-  group_by(pollster) %>%
-  summarize(
-    Trump_bias = mean(pct - actual_results_2020$Trump_pct, na.rm = TRUE)
-  )
-
-dem_pollster_bias <- biden_2020_national %>%
-  group_by(pollster) %>%
-  summarize(
-    Biden_bias = mean(pct - actual_results_2020$Biden_pct, na.rm = TRUE)
-  )
-
-# adjust 2024 national polls percentages by the average pollster biases
-# also mutate has_sponsor variable into dummy variable and remove NA's
-trump_2024_national_adj <- trump_2024_national %>%
-  left_join(rep_pollster_bias, by = "pollster") %>%
-  mutate(
-    pct_adj = pct - ifelse(!is.na(Trump_bias), Trump_bias, 0)
+Finally, the Delta coefficient $\alpha_1$ from all paired comparisons across every CFPS iteration were compiled together to identify cross-quartile education return disparities over time.
+
+As a test of model robustness, another set of regressions were ran without PSM to verify the overall significance of educational returns and the consistent pattern observed between quartiles.
+This will be discussed further in @sec-results.
+
+# Results {#sec-results}
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+
+# Load all the models
+# Define the path to the models folder
+models_path <- here::here("models")
+
+# List all RDS files in the models folder
+model_files <- list.files(
+  path = models_path,
+  pattern = "\\.rds$",    
+  full.names = TRUE       
+)
+
+# Load each RDS file and store in a list
+models <- lapply(model_files, readRDS)
+
+# Assign names to the list based on the filenames (without .rds)
+names(models) <- tools::file_path_sans_ext(basename(model_files))
+
+```
+
+## Cross-quartile disparities in Educational Returns
+
+```{r}
+#| label: tbl-results
+#| tbl-cap: Cross-Quartile Percentage Disparities of Returns to Education Over Time
+#| echo: false
+#| message: false
+#| warning: false
+
+library(knitr)
+library(kableExtra)
+
+# Data
+data <- data.frame(
+  `CFPS Year` = c(2020, 2018, 2016, 2014, 2012, 2010, "Temporal mean"),
+  `Q1vsQ2` = c(0.9482, 0.2441, 0.7665, -2.3488, 1.2055, 0.4988, 0.2191),
+  `Q1vsQ3` = c(1.9092, 2.3463, 1.2655, -1.1069, 0.9527, 3.0412, 1.4013),
+  `Q1vsQ4` = c(4.1670, 3.9833, 4.5967, 0.6399, 3.1572, 5.6921, 3.7060),
+  `Q2vsQ3` = c(1.2350, 1.7767, 1.2912, 0.2706, -0.0212, 2.1727, 1.1208),
+  `Q2vsQ4` = c(3.1601, 3.3524, 3.9390, 3.3242, 3.7233, 4.9265, 3.7376),
+  `Q3vsQ4` = c(2.2804, 3.7010, 3.1417, 3.1945, 4.4302, 2.1920, 3.1566),
+  `Cross Sectional Mean` = c(2.2833, 2.5673, 2.5001, 0.6623, 2.2413, 3.0872, ' ')
+)
+
+# Create the table
+kable(
+  data,
+  format = "latex"
 ) %>%
-  select(-Trump_bias)
-
-# Adjust Harris 2024 National Polls
-harris_2024_national_adj <- harris_2024_national %>%
-  left_join(dem_pollster_bias, by = "pollster") %>%
-  mutate(
-    pct_adj = pct - ifelse(!is.na(Biden_bias), Biden_bias, 0)
+  kable_styling(
+    latex_options = c("striped", "hold_position", "scale_down"), 
+    position = "center",
+    full_width = FALSE
+  )
+
+```
+\FloatBarrier
+Note: In 2012, educational returns for Q1, Q2, and Q3 were insignificant. In 2010, educational returns for Q1 and Q2 were insignificant.
+
+As @tbl-results shows, in most CFPS iterations, individuals from higher family income quartiles demonstrated a significant advantage in terms of returns to education compared to their counterparts in other quartiles.
+The greatest differences were observed when comparing the highest income quartile (Q4) to other quartiles.
+Over all CFPS iterations, individuals in the top quartile benefitted from 3.71% more gains in income from an additional year of education compared to the lowest quartile, 3.74% more than the second quartile, and 3.16% more than the third quartile on average.
+Comparatively, the differences between the other quartiles were less pronounced.
+
+Upon evaluating cross-sectional means, no discernible upward or downward trend was identified.
+Other than the outlier year 2014, individuals from higher quartiles experienced around 2 to 3 percent greater educational returns on average compared to individuals from relatively lower quartiles.
+Thus, a general inference can be made: while those in the higher family income quartiles consistently enjoy significant benefits in terms of returns to education, this advantage has not expanded over time.
+
+## Robustness testing
+
+```{r}
+#| label: tbl-robust
+#| tbl-cap: Quartiles’ Percentage Returns to Education Over Time Without PSM
+#| echo: false
+#| message: false
+#| warning: false
+
+library(knitr)
+library(kableExtra)
+
+data <- data.frame(
+  `CFPS Year` = c(2020, 2018, 2016, 2014, 2012, 2010),
+  `Q1 Returns` = c('4.9507***', '4.1730**', '2.5671*', '4.4464**', '-1.0031', '0.1803'),
+  `Q2 Returns` = c('5.8130***', '4.0239***', '3.0501***', '2.5357**', '0.0590', '1.1116'),
+  `Q3 Returns` = c('7.3284***', '6.1466***', '4.1665***', '2.8027***', '0.4928', '3.9577***'),
+  `Q4 Returns` = c('10.3891***', '9.1724***', '6.9051***', '6.3410***', '4.4870***', '8.0710***')
+)
+
+kable(
+  data,
+  format = "latex"
 ) %>%
-  select(-Biden_bias)
-
-# model adjusted support percentage by time and control variables
-# first split training and testing dataset using an 80/20 split
-set.seed(11451)
-trainIndex_trump_adj <- createDataPartition(trump_2024_national_adj$pct_adj,
-  p = 0.8, list = FALSE
-)
-data_train_trump_adj <- trump_2024_national_adj[trainIndex_trump_adj, ]
-data_test_trump_adj <- trump_2024_national_adj[-trainIndex_trump_adj, ]
-
-trainIndex_harris_adj <- createDataPartition(harris_2024_national_adj$pct_adj,
-  p = 0.8, list = FALSE
-)
-data_train_harris_adj <- harris_2024_national_adj[trainIndex_harris_adj, ]
-data_test_harris_adj <- harris_2024_national_adj[-trainIndex_harris_adj, ]
-
-model_date_harris_adj <- lm(pct_adj ~ end_date + has_sponsor +
-  transparency_score + sample_size, data = data_train_harris_adj)
-model_date_trump_adj <- lm(pct_adj ~ end_date + has_sponsor +
-  transparency_score + sample_size, data = data_train_trump_adj)
-
-# repeat for unadjusted support levels
-trainIndex_trump <- createDataPartition(trump_2024_national$pct,
-  p = 0.8, list = FALSE
-)
-data_train_trump <- trump_2024_national[trainIndex_trump, ]
-data_test_trump <- trump_2024_national[-trainIndex_trump, ]
-
-trainIndex_harris <- createDataPartition(harris_2024_national$pct,
-  p = 0.8, list = FALSE
-)
-data_train_harris <- harris_2024_national[trainIndex_harris, ]
-data_test_harris <- harris_2024_national[-trainIndex_harris, ]
-
-model_date_harris <- lm(pct ~ end_date + has_sponsor +
-  transparency_score + sample_size, data = data_train_harris)
-model_date_trump <- lm(pct ~ end_date + has_sponsor +
-  transparency_score + sample_size, data = data_train_trump)
-
-# Functions to evaluate model using testing dataset
-evaluate_model_adj <- function(model, test_data) {
-  predictions <- predict(model, newdata = test_data)
-  actuals <- test_data$pct_adj
-  rmse <- sqrt(mean((predictions - actuals)^2, na.rm = TRUE))
-  r_squared <- summary(model)$r.squared
-  return(list(RMSE = rmse, R_squared = r_squared))
-}
-
-evaluate_model <- function(model, test_data) {
-  predictions <- predict(model, newdata = test_data)
-  actuals <- test_data$pct
-  rmse <- sqrt(mean((predictions - actuals)^2, na.rm = TRUE))
-  r_squared <- summary(model)$r.squared
-  return(list(RMSE = rmse, R_squared = r_squared))
-}
-
-# Evaluate Harris model with adjusted support percentages
-harris_evaluation_adj <- evaluate_model_adj(model_date_harris_adj, data_test_harris_adj)
-
-# Evaluate Trump model with adjusted support percentages
-trump_evaluation_adj <- evaluate_model_adj(model_date_trump_adj, data_test_trump_adj)
-
-# Evaluate Harris model with unadjusted support percentages
-harris_evaluation <- evaluate_model(model_date_harris, data_test_harris)
-
-# Evaluate Trump model with unadjusted support percentages
-trump_evaluation <- evaluate_model(model_date_trump, data_test_trump)
-
-# Augment data with model predictions
-model_harris_adj <- readRDS(here::here("models/MLR_adjusted_harris.rds"))
-model_trump_adj <- readRDS(here::here("models/MLR_adjusted_trump.rds"))
-
-harris_2024_national_adj <- harris_2024_national_adj %>% mutate(
-  fitted_date = predict(model_harris_adj)
-)
-
-trump_2024_national_adj <- trump_2024_national_adj %>% mutate(
-  fitted_date = predict(model_trump_adj)
-)
-
-# Unadjusted datasets
-model_harris <- readRDS(here::here("models/MLR_harris.rds"))
-model_trump <- readRDS(here::here("models/MLR_trump.rds"))
-
-harris_2024_national <- harris_2024_national %>% mutate(
-  fitted_date = predict(model_harris)
-)
-
-trump_2024_national <- trump_2024_national %>% mutate(
-  fitted_date = predict(model_trump)
-)
-
-# evaluate models without using training and testing data
-harris_eval_adj <- evaluate_model_adj(model_harris_adj, harris_2024_national_adj)
-
-harris_eval <- evaluate_model(model_harris, harris_2024_national)
-
-trump_eval_adj <- evaluate_model_adj(model_trump_adj, trump_2024_national_adj)
-
-trump_eval <- evaluate_model(model_trump, trump_2024_national)
-
-#### Logistic regression for national support ####
-
-combined_national <- full_join(
-  trump_2024_national,
-  harris_2024_national,
-  by = c(
-    "pollster", "has_sponsor", "pollscore",
-    "transparency_score", "sample_size", "end_date", "state", "cycle"
-  )
-)
-
-combined_national <- combined_national %>% mutate(
-  harris_win = case_when(
-    pct.y >= pct.x ~ 1,
-    pct.y < pct.x ~ 0
-  )
-)
-
-# repeat for adjusted support levels
-combined_national_adj <- full_join(
-  trump_2024_national_adj,
-  harris_2024_national_adj,
-  by = c(
-    "pollster", "has_sponsor", "pollscore",
-    "transparency_score", "sample_size", "end_date", "state", "cycle"
-  )
-)
-
-combined_national_adj <- combined_national_adj %>% mutate(
-  harris_win = case_when(
-    pct_adj.y >= pct_adj.x ~ 1,
-    pct_adj.y < pct_adj.x ~ 0
-  )
-)
-
-# logistic model to predict the popular vote
-model_logistic <- readRDS(here::here("models/Logistic_model.rds"))
-
-model_logistic_adj <- readRDS(here::here("models/Logistic_model_adjusted.rds"))
-
-# include predicted outcomes to the dataframes
-combined_national <- combined_national %>%
-  mutate(
-    harris_win_prob = round(100 * predict(model_logistic, type = "response"), 2)
-  )
-
-combined_national_adj <- combined_national_adj %>%
-  mutate(
-    harris_win_prob = round(100 * predict(model_logistic_adj,
-      type = "response"
-    ), 2)
-  )
-
-#### Evaluate the Model ####
-
-# ROC Curve and AUC
-roc_obj <- roc(
-  combined_national$harris_win,
-  combined_national$harris_win_prob
-)
-auc_value <- auc(roc_obj)
-
-roc_obj_adj <- roc(
-  combined_national_adj$harris_win,
-  combined_national_adj$harris_win_prob
-)
-auc_value_adj <- auc(roc_obj_adj)
-```
-
-For the analysis of the national popular vote, the logistic model of adjusted polls possess an AUC value of 0.98, and the logistic model of unadjusted polls have an AUC of 0.94, indicating high reliability of categorization.
-Their respective ROC plots are presented as @fig-log and @fig-logadj.
-
-RMSE values and R squared values were calculated for the multiple linear regression models predicting popular vote.
-The RMSE values for all four models, adjusted and unadjusted support levels of the two candidates, are greater than 1, indicating that the fitted values and the support levels of actual polls are more than 1 percent apart on average, which is significant when analyzing popular vote.
-Moreover, all R squared values other than the model for the adjusted support rate of Trump, are smaller than 0.3, indicating the inability of the models to account for the variance of national support rates in the data.
-The model for the adjusted support rate of Trump has a R squared value of 0.69, indicating a relatively high proportion of variance in polled support rates being explained by the multiple linear regression model.
-This was expected, as the predictors such as a poll's end date and transparency does not necessarily correlate with the outcome of the polls.
-More predictive variables used by FiveThirtyEight [@5383] for their predictions are unavailable in the raw dataset, which is a key limitation of the data.
-
-# Results {#sec-results}
-
-## Swing states
-
-@tbl-result shows the average likelihood percentage of Harris winning each swing state, calculated by using the logistic model on 1,000 hypothetical data points for each state, generated with the normal distribution of predictors and setting the end_date to election day.
-It indicates that Harris has a greater probability to win in Pennsylvania, Georgia, and Nevada, while Trump is more likely to win in North Carolina, Michigan, Arizona, and Wisconsin.
-The electoral votes in each state is also presented.
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-
-#### Results ####
-# To predict the outcome on election day, generate 1000 hypothetical data points
-# using the election day as end_date and the normal curve of other input
-# variables, mimicing all the situations that may happen on election day
-hypothetical_data_Pennsylvania <- tibble(
-  end_date = as.Date("2024-11-05"),
-  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Pennsylvania$has_sponsor)),
-  transparency_score = rnorm(1000,
-    mean = mean(combined_Pennsylvania$transparency_score),
-    sd = sd(combined_Pennsylvania$transparency_score)
-  ),
-  sample_size = rnorm(1000,
-    mean = mean(combined_Pennsylvania$sample_size),
-    sd = sd(combined_Pennsylvania$sample_size)
-  )
-)
-
-hypothetical_data_Georgia <- tibble(
-  end_date = as.Date("2024-11-05"),
-  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Georgia$has_sponsor)),
-  transparency_score = rnorm(1000,
-    mean = mean(combined_Georgia$transparency_score),
-    sd = sd(combined_Georgia$transparency_score)
-  ),
-  sample_size = rnorm(1000,
-    mean = mean(combined_Georgia$sample_size),
-    sd = sd(combined_Georgia$sample_size)
-  )
-)
-
-hypothetical_data_North_Carolina <- tibble(
-  end_date = as.Date("2024-11-05"),
-  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_North_Carolina$has_sponsor)),
-  transparency_score = rnorm(1000,
-    mean = mean(combined_North_Carolina$transparency_score),
-    sd = sd(combined_North_Carolina$transparency_score)
-  ),
-  sample_size = rnorm(1000,
-    mean = mean(combined_North_Carolina$sample_size),
-    sd = sd(combined_North_Carolina$sample_size)
-  )
-)
-
-hypothetical_data_Michigan <- tibble(
-  end_date = as.Date("2024-11-05"),
-  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Michigan$has_sponsor)),
-  transparency_score = rnorm(1000,
-    mean = mean(combined_Michigan$transparency_score),
-    sd = sd(combined_Michigan$transparency_score)
-  ),
-  sample_size = rnorm(1000,
-    mean = mean(combined_Michigan$sample_size),
-    sd = sd(combined_Michigan$sample_size)
-  )
-)
-
-hypothetical_data_Arizona <- tibble(
-  end_date = as.Date("2024-11-05"),
-  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Arizona$has_sponsor)),
-  transparency_score = rnorm(1000,
-    mean = mean(combined_Arizona$transparency_score),
-    sd = sd(combined_Arizona$transparency_score)
-  ),
-  sample_size = rnorm(1000,
-    mean = mean(combined_Arizona$sample_size),
-    sd = sd(combined_Arizona$sample_size)
-  )
-)
-
-hypothetical_data_Wisconsin <- tibble(
-  end_date = as.Date("2024-11-05"),
-  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Wisconsin$has_sponsor)),
-  transparency_score = rnorm(1000,
-    mean = mean(combined_Wisconsin$transparency_score),
-    sd = sd(combined_Wisconsin$transparency_score)
-  ),
-  sample_size = rnorm(1000,
-    mean = mean(combined_Wisconsin$sample_size),
-    sd = sd(combined_Wisconsin$sample_size)
-  )
-)
-
-hypothetical_data_Nevada <- tibble(
-  end_date = as.Date("2024-11-05"),
-  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Nevada$has_sponsor)),
-  transparency_score = rnorm(1000,
-    mean = mean(combined_Nevada$transparency_score),
-    sd = sd(combined_Nevada$transparency_score)
-  ),
-  sample_size = rnorm(1000,
-    mean = mean(combined_Nevada$sample_size),
-    sd = sd(combined_Nevada$sample_size)
-  )
-)
-
-# run the corresponding logistic regression on the hypothetical data of each
-# state and average the outcomes to find the expected win rate of Harris
-# on election day
-hypothetical_data_Pennsylvania <- hypothetical_data_Pennsylvania %>%
-  mutate(
-    harris_win_prob = round(100 * predict(logistic_Pennsylvania, newdata = ., type = "response"), 2)
-  )
-
-hypothetical_data_Georgia <- hypothetical_data_Georgia %>%
-  mutate(
-    harris_win_prob = round(100 * predict(logistic_Georgia, newdata = ., type = "response"), 2)
-  )
-
-hypothetical_data_North_Carolina <- hypothetical_data_North_Carolina %>%
-  mutate(
-    harris_win_prob = round(100 * predict(logistic_North_Carolina, newdata = ., type = "response"), 2)
-  )
-
-hypothetical_data_Michigan <- hypothetical_data_Michigan %>%
-  mutate(
-    harris_win_prob = round(100 * predict(logistic_Michigan, newdata = ., type = "response"), 2)
-  )
-
-hypothetical_data_Arizona <- hypothetical_data_Arizona %>%
-  mutate(
-    harris_win_prob = round(100 * predict(logistic_Arizona, newdata = ., type = "response"), 2)
-  )
-
-hypothetical_data_Wisconsin <- hypothetical_data_Wisconsin %>%
-  mutate(
-    harris_win_prob = round(100 * predict(logistic_Wisconsin, newdata = ., type = "response"), 2)
-  )
-
-hypothetical_data_Nevada <- hypothetical_data_Nevada %>%
-  mutate(
-    harris_win_prob = round(100 * predict(logistic_Nevada, newdata = ., type = "response"), 2)
-  )
-
-# produce a table of mean winning probabilities
-mean_probabilities <- tibble(
-  State = c("Pennsylvania", "Georgia", "North Carolina", "Michigan", "Arizona", "Wisconsin", "Nevada"),
-  Harris_Win_Probability = c(
-    round(mean(hypothetical_data_Pennsylvania$harris_win_prob, na.rm = TRUE), 2),
-    round(mean(hypothetical_data_Georgia$harris_win_prob, na.rm = TRUE), 2),
-    round(mean(hypothetical_data_North_Carolina$harris_win_prob, na.rm = TRUE), 2),
-    round(mean(hypothetical_data_Michigan$harris_win_prob, na.rm = TRUE), 2),
-    round(mean(hypothetical_data_Arizona$harris_win_prob, na.rm = TRUE), 2),
-    round(mean(hypothetical_data_Wisconsin$harris_win_prob, na.rm = TRUE), 2),
-    round(mean(hypothetical_data_Nevada$harris_win_prob, na.rm = TRUE), 2)
-  )
-)
-
-# include electoral votes to determine who is in the lead
-state_evs <- tibble::tribble(
-  ~State, ~electoral_votes,
-  "Alaska", 3,
-  "Arizona", 11,
-  "Arkansas", 6,
-  "California", 55,
-  "Colorado", 9,
-  "Connecticut", 7,
-  "Florida", 29,
-  "Georgia", 16,
-  "Illinois", 20,
-  "Indiana", 11,
-  "Iowa", 6,
-  "Kansas", 6,
-  "Louisiana", 8,
-  "Maine", 2,
-  "Maine CD-1", 1,
-  "Maine CD-2", 1,
-  "Maryland", 10,
-  "Massachusetts", 11,
-  "Michigan", 16,
-  "Minnesota", 10,
-  "Mississippi", 6,
-  "Missouri", 10,
-  "Montana", 3,
-  "Nebraska", 2,
-  "Nebraska CD-2", 1,
-  "Nevada", 6,
-  "New Hampshire", 4,
-  "New Mexico", 5,
-  "New York", 29,
-  "North Carolina", 15,
-  "Ohio", 18,
-  "Oklahoma", 7,
-  "Oregon", 7,
-  "Pennsylvania", 20,
-  "Rhode Island", 4,
-  "South Carolina", 9,
-  "South Dakota", 3,
-  "Texas", 38,
-  "Utah", 6,
-  "Vermont", 3,
-  "Virginia", 13,
-  "Washington", 12,
-  "Wisconsin", 10
-)
-
-mean_probabilities <- mean_probabilities %>%
-  left_join(state_evs, by = "State")
-
-#### Overall Probability of Winning ####
-# Harris
-# Create data frame of states
-states <- data.frame(
-  state = c("PA", "GA", "NC", "MI", "WI", "NV", "AZ"),
-  prob = c(0.5551, 0.6801, 0.1033, 0.5151, 0.3792, 0.7679, 0),
-  votes = c(20, 16, 15, 16, 10, 6, 11)
-)
-
-# Function to calculate probability of a specific combination
-calc_combo_prob <- function(combo, states) {
-  prob <- 1
-  for (i in 1:nrow(states)) {
-    if (i %in% combo) {
-      prob <- prob * states$prob[i]
-    } else {
-      prob <- prob * (1 - states$prob[i])
-    }
-  }
-  return(prob)
-}
-
-# Generate all possible combinations
-n_states <- nrow(states)
-total_prob <- 0
-
-# Check each possible combination
-for (i in 1:(2^n_states - 1)) {
-  # Convert number to binary to get combination
-  combo <- which(intToBits(i)[1:n_states] == 1)
-
-  # Calculate total electoral votes for this combination
-  votes <- sum(states$votes[combo])
-
-  # If this combination has enough votes, add its probability
-  if (votes >= 44) {
-    prob <- calc_combo_prob(combo, states)
-    total_prob <- total_prob + prob
-  }
-}
-
-# Trump
-# Create data frame of states
-states <- data.frame(
-  state = c("PA", "GA", "NC", "MI", "WI", "NV", "AZ"),
-  prob = c(1 - 0.5551, 1 - 0.6801, 1 - 0.1033, 1 - 0.5151, 1 - 0.3792, 1 - 0.7679, 1 - 0), # Using 1-p for Trump's probabilities
-  votes = c(20, 16, 15, 16, 10, 6, 11)
-)
-
-# Function to calculate probability of a specific combination
-calc_combo_prob <- function(combo, states) {
-  prob <- 1
-  for (i in 1:nrow(states)) {
-    if (i %in% combo) {
-      prob <- prob * states$prob[i]
-    } else {
-      prob <- prob * (1 - states$prob[i])
-    }
-  }
-  return(prob)
-}
-
-# Generate all possible combinations
-n_states <- nrow(states)
-total_prob <- 0
-
-# Check each possible combination
-for (i in 1:(2^n_states - 1)) {
-  # Convert number to binary to get combination
-  combo <- which(intToBits(i)[1:n_states] == 1)
-
-  # Calculate total electoral votes for this combination
-  votes <- sum(states$votes[combo])
-
-  # If this combination has enough votes, add its probability
-  if (votes >= 51) {
-    prob <- calc_combo_prob(combo, states)
-    total_prob <- total_prob + prob
-  }
-}
-```
-
-```{r}
-#| label: tbl-result
-#| tbl-cap: Predicted Harris Win Percentage in Swing States
-#| echo: false
-#| message: false
-#| warning: false
-
-mean_probabilities %>%
-  gt() %>%
-  fmt_number(
-    columns = vars(Harris_Win_Probability),
-    decimals = 2
-  ) %>%
-  cols_label(
-    State = "State",
-    Harris_Win_Probability = "Harris Win Probability (%)",
-    electoral_votes = "Electoral Votes"
-  ) %>%
-  tab_options(
-    table.font.size = 12,
-    heading.title.font.size = 16,
-    heading.subtitle.font.size = 12,
-    table.border.top.width = px(2),
-    table.border.bottom.width = px(2)
-  )
-```
-
-Combining with the fact that Harris requires 44 electoral votes to win and Trump requires 51, we have found using the probability function that Harris has a 38.3 chance to acquire more than 44 electoral votes, according to the probabilities and electoral votes in @tbl-result.
-On the other hand, Trump has a 61.7 probability to acquire more than 51 votes.
-Thus, our conclusion is that while both candidates possess a significant chance of winning, Trump has the greater probability of acquiring the necessary electoral votes from the seven swing states on election day.
-
-## Popular vote
-
-@fig-lradj presents the fitted values of the candidates' adjusted national support rates as well as the data points of polled support rates adjusted for historical pollster bias.
-It indicates that Trump is expected to have higher national support levels, but the two converges as election day approaches.
-This result is counter intuitive, as most national polls indicate that Harris will have the popular vote.
-However, the adjusted values for Trump's support level are significantly greater than the polled values because historically, the actual percentage of the popular vote for Trump in 2020 was significantly greater than his polled percentages of the popular vote.
-Thus, assuming that the 2024 national polls are equally biased against Trump compared to the 2020 polls, it is difficult to tell who will get the popular vote on election day.
-However, as previously stated, this assumption is likely false, as the candidates have changed.
-
-```{r}
-#| label: fig-lradj
-#| fig-cap: Adjusted Popular Vote Prediction, 2024
-#| echo: false
-#| message: false
-#| warning: false
-# plot model predictions
-# combine the datasets to create a single visual
-combined_data_adj <- bind_rows(harris_2024_national_adj, trump_2024_national_adj)
-combined_data <- bind_rows(harris_2024_national, trump_2024_national)
-
-# create the plot that contains scattered points of adjusted percentages
-# and lines for fitted values
-ggplot(combined_data_adj, aes(x = end_date, y = pct_adj, color = candidate_name)) +
-  # Scatter points for actual adjusted percentages
-  geom_point(alpha = 0.6) +
-  # Regression lines
-  geom_line(aes(y = fitted_date), size = 0.5) +
-  xlim(as.Date("2024-07-19"), as.Date("2024-10-25")) +
-  # Assign specific colors
-  scale_color_manual(
-    values =
-      c("Kamala Harris" = "blue", "Donald Trump" = "red")
-  ) +
-  # Customize the plot appearance
-  theme_classic() +
-  labs(
-    y = "Adjusted Percent Support",
-    x = "End Date",
-    color = "Candidate"
-  ) +
-  theme(
-    text = element_text(size = 12),
-    plot.title = element_text(hjust = 0.5, face = "bold")
-  )
-```
-
-\FloatBarrier
-
-@fig-lr Presents the predicted unadjusted national support rates for Harris and Trump.
-The conclusions one can make from this plot is similar to those of most polls: Harris is expected to win the popular vote on any day, including the election day.
-
-```{r}
-#| label: fig-lr
-#| fig-cap: Unadjusted Popular Vote Prediction, 2024
-#| echo: false
-#| message: false
-#| warning: false
-# Unadjusted support percentages
-ggplot(combined_data, aes(x = end_date, y = pct, color = candidate_name)) +
-  # Scatter points for actual adjusted percentages
-  geom_point(alpha = 0.6) +
-  # Regression lines
-  geom_line(aes(y = fitted_date), size = 0.5) +
-  xlim(as.Date("2024-07-19"), as.Date("2024-10-25")) +
-  # Assign specific colors
-  scale_color_manual(
-    values =
-      c("Kamala Harris" = "blue", "Donald Trump" = "red")
-  ) +
-  # Customize the plot appearance
-  theme_classic() +
-  labs(
-    y = "Adjusted Percent Support",
-    x = "End Date",
-    color = "Candidate"
-  ) +
-  theme(
-    text = element_text(size = 12),
-    plot.title = element_text(hjust = 0.5, face = "bold")
-  )
-```
-
-\FloatBarrier
-
-The regression coefficients for the logistic and linear models are presented in the Additional Data Details section (@sec-model-details) because they are not the outcome of interest.
+  kable_styling(
+    latex_options = c("striped", "hold_position", "scale_down"), 
+    position = "center",
+    full_width = FALSE
+  )
+
+```
+\FloatBarrier
+Significant codes: * = p < 0.05, ** = p < 0.01,  *** = p < 0.001
+
+When directly regressing without matching, the significance of educational returns coefficients remained the same; the coefficients for Q1, Q2 and Q3 of CFPS2012 and the coefficients for Q1 and Q2 of CFPS2010 are the only ones insignificant at the 5% level.
+It is uncertain why educational returns are insignificant for these family income quartiles, both in the matched data and the unmatched data.
+It might be caused by the legacy data collection methods or the changes in variable recording that occurred after the 2012 iteration.
+Despite that, the outcome of the robustness test demonstrates the model's consistency.
 
@@
 
-## The illusion of polarization
-
-As mentioned in the introduction, one thing that stands out about the 2024 election in particular is just how polarized the two factions are.
-Instead of merely being a choice over which individual to helm the country over the next four years, this particular election is being framed more and more as a “fight to protect our democracy” from both sides of the debate stand.
-This, while evidently a new level of polarization, merely mirrors the trend in recent years more than anything else: party loyalty has been on a steady uprise since 1972, with loyalty in weak partisan and leaning independent voters increasing by approximately 50% in the 40 years that followed [@partisanship].
-New records were further set in 2016, with Republican validated voters voting Trump a staggering 92% to 4% for Clinton, and Democratic validated voters voting Clinton an equally extreme 94% to 5% Trump support [@pew2018voters].
-
-New voting statistics, however, suggest that this polarization is likely only more prominent in the upper echelons of political representation, however: a Washington Post article found that approximately 1 in 8 women and 1 in 10 men are now voting differently from their spouses compared to before [@wapo2024women], a development that suggests a decrease in long-increasing partisanship trends.
-This is especially pronounced since households in the States overwhelmingly vote together: at least 70% of them do, at least, which means that this value is projected to decrease from 70% to approximately 62% [@households].
-In short: while it seems that ideologies are shifting more and more away from each other, the stats say otherwise.
-So does the Overton window [@overton].
-
-## Win probabilities versus support ratings: why our predictions are as extreme as they are
-
-Our model led to a win probability prediction with numbers much more skewed towards one side than most pollsters currently predict: under this model, we find that Harris has a 40-60 chance against Trump, whereas most pollsters nowadays hover somewhere between 50-50 to 45-55 (towards either side).
-This is mainly a consequence of using a multinomial logistic regression model as opposed than other models – instead of predicting the support rates of the two candidates, such a model outputs the probability that a random support rate value from the predicted distribution of Harris support rates is larger than that of the predicted distribution of Trump support rates.
-This means that in states such as Nevada, where 538 gives Trump a +3 advantage, factoring in for margin of error and standard error means that the probability of Harris winning the state is not in fact 47% but rather much closer to zero, which we decided is a more intuitive way of understanding election odds.
-
-A final reason for this is how swing states are polled much more sample-size-wise than other states, leading to a much higher power value than polls from said other states – a +3 lead in a sample of 1000 people from California’s 39 million might not mean too much, but a +3 lead in a sample of 3000 people from Nevada’s 3 million represents the actual results for 0.3% of the state’s population, holding much more relative weight when it comes to election predictions.
+## Takeaways
+
+This paper investigates how family income influences the economic returns to education in China from 2010 to 2020 using data from the China Family Panel Studies (CFPS).
+Propensity Score Matching (PSM) and multivariate regression models were utilized to analyze cross-quartile disparities.
+
+The study reveals that individuals from wealthier families consistently experience significantly higher income returns from education compared to those from lower-income families.
+These disparities are particularly pronounced when comparing the highest income quartile to the other quartiles.
+However, the gap in returns has remained stable over the studied decade, suggesting persistent inequality without evidence of widening.
+
+From this research, we learn about the role of socioeconomic background in shaping the economic benefits of education in China.
+The finding that the highest income quartile produces significantly greater disparities than other quartiles hints that being a member of the middle class does not necessarily imply better social mobility compared to the lower class, but being in the upper class produces greater economic benefits for the working individual.
+On the large scale, it highlights a fundamental limitation in the equalizing potential of education, as the higher financial returns to education predominantly favor individuals from wealthier families.
+This underscores the need for targeted policies to address these disparities and enhance education's role as a tool for socioeconomic mobility; merely expanding higher education may not be sufficient.
 
@@
 
-The dataset used for this analysis has a number of clear limitations.
-First of all, there is a lack of high-quality polls.
-Though FiveThirtyEight distributes each pollster with a rating out of 3.0, almost all pollsters under the rating of 2.7 produces outcomes that are unreliable and highly volatile.
-For this research, it was only possible for us to use pollsters with a 3.0 rating when analyzing national polls; we had to lower the standards to 2.5 for the analysis of swing states, as the number of high-quality state-specific polls are very limited.
-The inclusion of unreliable data reduces the predictability of our logistic models and thus our final outcome.
-The lack of predictability of our Nevada model is a perfect example of how low-quality data and the lack of data points impacts our ability to create effective models.
-However, we acknowledge that this is beyond the control of FiveThirtyEight, as they do not conduct the polls.
-
-The second major challenge presented by the dataset is the lack of predictors.
-FiveThirtyEight utilizes predictive variables that are unavailable to us, such as weighted values that represent the extent to which a pollster is partisan [@5383].
-The predictors used in this research, such as the transparency score of the pollster, are not related to their bias towards any candidate from a partisanship point of view, limiting the predictive power of our models.
-
-Finally, the lack of data regarding the Harris-Trump race, due to Harris starting her presidential race uncharacteristically late, is also a main reason for the limitations of our model.
-
-Potential next steps could be taken to improve the model in the future: more data could be aggregated manually (from pollsters not recorded by FiveThirtyEight), stronger predictor variables that are specifically more correlated with partisanship could be marked and utilised in our model, and individual weightings could be utilised and applied to the data based on each pollster's "track record" with regards to the error, bias, and variance in their previous polls and estimates.
+This research has a number of limitations.
+First, the data from CFPS has poor completion rates for some of the variables.
+Many individuals from lower income quartiles did not respond to questions such as weekly hours worked or income.
+This caused the data used in this research to include more individuals from higher quartiles, increasing bias.
+The second limitation is that the sample changed over time as individuals responded differently in different CFPS iterations.
+One of the greatest benefits of CFPS is that it follows the same pool of families over time, but the data for this study did not include the same set of individuals throughout different CFPS iterations because respondents left different questions unanswered in different years.
+Consequently, the sample sizes and the individuals making up the samples were different for each year, making the temporal analysis less conclusive.
+Finally, this research calculated returns to education using the Miner equation, which has a set of limitations.
+Besides the problem of linearity, it also assumes that all covariates influencing income are included in the model, which might not be the case.
+Additionally, the model only provides a general statement on the overall returns to education of different family income quartiles and does not provide insight to the reasons behind the differences.
+
+For further research, one may execute further divisions in terms of educational stages and examine whether the difference of returns for various educational stages can explain the difference in overall educational returns between income groups.
 
@@
 
-## Pollster methodology overview and evaluation
-
-The Quinnipiac University Poll conducts independent polling in swing states. To analyze their methodology, we look specifically into their October 2024 Pennsylvania polls [@quinnipiac].
-
-Their target population is likely voters aged 18 and older in Pennsylvania [@quinnipiacmethodology].
-To reach this population, they use likely voters aged 18 and older with phone numbers (both landline and cell) as their sampling frame, i.e.
-the frame of possible subjects that they sample observations from.
-Quinnipiac University employed Random Digit Dialing (RDD) to generate their sample of 2,186 respondents.
-This dual-frame approach reflects modern communication patterns, with 1,644 cell phone and 542 landline completions.
-However, using phones as a sampling frame means they cannot reach voters without phone access, introducing potential coverage bias.
-
-Their sampling approach uses stratification by Census division according to area code, meaning that they divide Pennsylvania into geographic regions before using RDD to sample within each region.
-This strategy ensures even geographic representation but adds complexity to the sampling process [@pollofpolls].
-For each selected number, they attempt contact at least three times before marking it as non-responsive.
-For landline calls, they ask to speak with the household member who has the next birthday, a simple but effective randomization technique.
-Afterwards, a series of screening questions confirm that the subject is indeed a likely voter, after which the subject's responses are then formally taken as part of the sample.
-
-After collecting responses, Quinnipiac adjusts their data through post-stratification weighting.
-In this weighting, they compare their sample's demographic composition to known population benchmarks from the Census (like age, gender, education, and race distributions in Pennsylvania) and adjust the weight given to each response to match these benchmarks.
-For example, if their sample has too few young voters compared to Census data, responses from young voters would be weighted more heavily.
-While this helps correct for sampling imbalances, it can increase the variance in their estimates if the weights vary substantially [@poststratification].
-
-The survey administration addresses measurement issues through its design.
-Live interviewers conduct all interviews, enabling question clarification and generating higher response rates compared to automated systems.
-However, live interviewers may introduce social desirability bias, where respondents might modify their answers to appear more socially acceptable.
-This becomes particularly relevant in political polling, where respondents might hesitate to express unpopular political views [@politicalpolling].
-
-Several types of bias affect the poll's results.
-Self-selection bias occurs because certain types of people (typically those more politically engaged or with stronger views) are more likely to agree to participate in the survey.
-Non-response bias arises when people who respond differ systematically from those who don't - for instance, busier people might be less likely to answer calls, potentially underrepresenting certain occupational groups [@nonresponse].
-Coverage bias means some groups (like those without phones) have no chance of being included in the sample.
-
-Ethics-wise, the survey does a good job of informing individuals of the details of the survey, such as its purpose and how participants' data is to be used.
-Personally-identifiable data (i.e.
-name, phone number, etc.) is not collected during the survey other than to ensure that repeat numbers are not drawn, and the usage of live interviewers to conduct the survey ensures that concerns about the ethics of the survey can be voiced and answered on-the-spot.
-Combined with the lack of financial incentive for participants, which suggests that all participants participate of their complete free will and intention, this is an ethically sound methodology for conducting a political survey.
-
-Finally, the poll also faces common challenges in political polls such as this one - the five-day field period (October 24-28) may miss opinion changes close to election day, and while weighting adjustments help correct for demographic imbalances, they may increase variance in the estimates if some groups need to be weighted heavily to match population benchmarks, for example.
-
-Overall, Quinnipiac's methodology represents a balanced approach to managing practical constraints and statistical rigor in modern political polling - while some common biases are still likely to skew the poll results off the true support levels for Harris, for example, the poll uses methods such as post-stratification weighting to tradeoff biases at the cost of model variance [@weighting].
-Using live interviewers unavoidably introduces social desirability bias, however, and significantly increases poll costs per quota.
-Modifying the methodology to remove this aspect of the survey would potentially reduce bias and allow for larger samples to be taken, in turn opening up possibilities for cross-validation and the such, which then reduces the effect of increased model variance on the final results.
+## Survey methodology overview and evaluation
 
@@
 
-With a \$100,000 budget, our approach focuses on producing accurate state-level estimates in key battleground states, which would then inform our national forecast.
-We prioritize Pennsylvania, Michigan, Wisconsin, Georgia, Arizona, and Nevada, allocating resources proportionally based on each state's electoral importance and expected margin of victory.
-
-Our sampling strategy employs both probability and non-probability methods.
-Probability sampling (60% of budget, i.e.
-\$60k) means every member of our target population has a known, non-zero chance of being selected - this allows us to calculate proper margins of error and make statistical inferences about the population.
-For this, we use dual-frame random digit dialing (RDD) for phone surveys and address-based sampling (ABS) for mail-to-web recruitment.
-RDD involves generating random phone numbers within active area codes, while ABS uses the U.S.
-Postal Service's delivery database as a sampling frame, both proven methods of sampling [@cummings].
-The ABS approach helps reach households without reliable phone access.
-We stratify our sample by geography, demographics, and previous voting patterns to ensure representation across key subgroups - meaning we divide the population into these subgroups and sample from each independently.
-
-For non-probability sampling (40% of budget, i.e.
-\$40k), where respondents' selection probabilities are unknown and not everyone has a chance of being selected, we recruit through multiple online panel vendors and use targeted social media advertising to reach traditionally underrepresented groups.
-While this approach introduces potential selection bias because participants self-select into the sample, it helps reach younger voters who are less responsive to traditional survey methods [@nonprobabilitysampling].
-We implement quota sampling within these non-probability samples to match key demographic targets - for example, stopping collection from certain demographic groups once their quota is filled.
-
-Respondent recruitment uses multiple contact methods - mail, email, text, and phone - with attempts made at different times and days to maximize response rates.
-We offer a \$10 gift card incentive for completed surveys and provide both English and Spanish language options.
-This mixed-mode contact strategy helps reduce non-response bias by providing multiple ways to participate.
-
-Data validation is crucial for maintaining quality.
-We cross-reference responses with voter files where available - meaning we check if respondents' self-reported registration status matches official records.
-We screen for duplicate responses using IP addresses and phone numbers, and implement attention checks within the survey (questions with known correct answers to ensure respondents are reading carefully).
-Speed checks identify rushed responses that might indicate low-quality data by flagging completions that fall below a minimum reasonable completion time, while consistency checks across related questions help identify potentially fraudulent responses by looking for logical contradictions in answers.
-
-Our weighting approach uses post-stratification to known population benchmarks - this means we adjust the weight given to each response so that our sample matches known population characteristics.
-For example, if our sample has 30% college graduates but the population has 40%, we would give more weight to responses from college graduates.
-We include demographics (age, race, education, gender), geographic location, past voting behavior, and party registration in our weighting scheme.
-We produce daily estimates using a 7-day rolling average, which helps smooth out daily fluctuations while remaining responsive to real changes in voter preferences [@weighting2].
-
-Finally, how ethics are handled is a crucial part of any survey methodology.
-In this idealised methodology, consent will be asked for at the beginning of the survey, full disclosure of how information is used will be given beforehand and no self-identifiable information will be recorded (so no names, phone numbers, etc.).
-The \$10 incentive is enough to hopefully make it wortile for participants' time, but also not ideally not significant enough of an incentive to make individuals suppress otherwise deal-breaking concerns with the survey purely for the sake of the incentive.
-
-The survey instrument itself focuses on six key areas: screening questions to identify likely voters, voting intentions (including direct questions about Trump vs.
-Harris preferences), political preferences, demographics, issue priorities, and media consumption patterns.
-We've implemented this survey design in Google Forms, which can be found here: https://forms.gle/pk7vDiMHwEGLMK849
-
-This methodology balances statistical rigor with practical constraints, while acknowledging and attempting to address the key challenges in modern political polling: declining response rates, coverage bias, and the increasing difficulty of reaching a representative sample of likely voters.
-
-## Idealised survey
-
-The survey, made using Google Forms, is linked here: https://forms.gle/pk7vDiMHwEGLMK849 Note that the questions are identical for both the phone and online surveys bar q6.
-A copy of the survey that is identical to the one implemented in the Google Forms above is presented below: Thank you for participating in this survey about the 2024 U.S.
-Presidential Election.
-This survey is part of a research project at the University of Toronto studying voting intentions and political attitudes.
-
-Estimated completion time: 8-10 minutes
-
-Your responses will be kept confidential and used only for research purposes.
-Email information, and any other information that may personally identify you, is not gathered.
-You may skip any questions you prefer not to answer, though complete responses are most helpful for our research.
-
-For questions or concerns about this survey, please contact: andrew.goh\@mail.utoronto.ca
-
-SCREENING SECTION: Q1. Are you 18 years of age or older?
-
-Yes No \[END SURVEY\]
-
-Q2. Are you a U.S. citizen?
-
-Yes No \[END SURVEY\]
-
-Q3. Are you registered to vote at your current address?
-
-Yes No Not sure \[If No or Not sure: Do you plan to register before the November 2024 election?\]
-
-VOTING INTENTION: Q4. How likely are you to vote in the 2024 presidential election?
-
-Definitely will vote Probably will vote Might or might not vote Probably will not vote Definitely will not vote
-
-Q5. If the 2024 presidential election were held today, and the candidates were Kamala Harris (Democrat) and Donald Trump (Republican), who would you vote for?
-
-Kamala Harris Donald Trump Another candidate (please specify) Would not vote Not sure
-
-ATTENTION CHECK: Q6. To ensure you're reading carefully, please select "Somewhat disagree" for this question: "I enjoy following political news."
-
-Strongly agree Somewhat agree Somewhat disagree Strongly disagree No opinion
-
-POLITICAL PREFERENCES: Q7. Generally speaking, you consider yourself a:
-
-Democrat Republican Independent Something else (please specify)
-
-Q8. How would you rate the current state of the U.S. economy?
-
-Very poor Poor Fair Good Excellent
-
-ISSUE PRIORITIES: Q9. Which ONE of the following issues is most important to you when deciding how to vote?
-
-Economy and jobs Immigration Healthcare Climate change Crime and public safety Education National security Abortion rights Gun policy Something else (please specify)
-
-For each of the following issues, please indicate whether you think Kamala Harris or Donald Trump would do a better job handling it:
-
-Q10. Economy and jobs:
-
-Kamala Harris would do better Donald Trump would do better No difference Not sure
-
-Q11. Human rights and freedom of speech: \[Same options\] Q12. Abortion: \[Same options\] Q13. Healthcare: \[Same options\] Q14. Immigration: \[Same options\] Q15. National security: \[Same options\]
-
-MEDIA CONSUMPTION: Q16. Where do you most often get your news about politics? (Select all that apply)
-
-Network TV news (ABC, CBS, NBC) Cable TV news (CNN, Fox News, MSNBC) Local TV news Radio Print newspapers News websites Social media Friends and family Other (please specify)
-
-Q17. How many hours per day do you typically spend following news about politics?
-
-Less than 1 hour 1-2 hours 2-4 hours More than 4 hours
-
-DEMOGRAPHICS: Q18. What is your age?
-
-18-24 25-34 35-44 45-54 55-64 65 or older
-
-Q19. What is your gender?
-
-Male Female Non-binary/Other Prefer not to say
-
-Q20. What is your race/ethnicity? (Select all that apply)
-
-White Black or African American Hispanic or Latino Asian Native American Other (please specify) Prefer not to say
-
-Q21. What is the highest level of education you have completed?
-
-Less than high school High school graduate Some college Associate's degree Bachelor's degree Graduate degree Prefer not to say
-
-Q22. What was your total household income before taxes in 2023?
-
-Under \$25,000 \$25,000-\$49,999 \$50,000-\$74,999 \$75,000-\$99,999 \$100,000-\$149,999 \$150,000 or more Prefer not to say
-
-CONSISTENCY CHECK: Q23. Looking ahead to November 2024, if Kamala Harris is the Democratic nominee and Donald Trump is the Republican nominee, how do you think you will vote?
-
-Kamala Harris Donald Trump Another candidate (please specify) Would not vote Not sure
-
-\[END OF SURVEY\] Thank you for completing this survey about the 2024 U.S.
-Presidential Election.
-Your responses will help us better understand voter preferences and political attitudes across the country.
-If you have any questions about this research or would like to be informed about the results, please contact andrew.goh\@mail.utoronto.ca.
-Your time and participation is greatly appreciated.
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Diagnostics
-
-```{r}
-#| label: fig-pen
-#| fig-cap: ROC Curve for Harris Win Prediction, Pennsylvania
-#| echo: false
-#| message: false
-#| warning: false
-
-plot(roc_obj_Pennsylvania)
-```
-
-```{r}
-#| label: fig-geo
-#| fig-cap: ROC Curve for Harris Win Prediction, Georgia
-#| echo: false
-#| message: false
-#| warning: false
-
-plot(roc_obj_Georgia)
-```
-
-```{r}
-#| label: fig-nor
-#| fig-cap: ROC Curve for Harris Win Prediction, North Carolina
-#| echo: false
-#| message: false
-#| warning: false
-
-plot(roc_obj_North_Carolina)
-```
-
-```{r}
-#| label: fig-mic
-#| fig-cap: ROC Curve for Harris Win Prediction, Michigan
-#| echo: false
-#| message: false
-#| warning: false
-
-plot(roc_obj_Michigan)
-```
-
-```{r}
-#| label: fig-ari
-#| fig-cap: ROC Curve for Harris Win Prediction, Arizona
-#| echo: false
-#| message: false
-#| warning: false
-
-plot(roc_obj_Arizona)
-```
-
-```{r}
-#| label: fig-wis
-#| fig-cap: ROC Curve for Harris Win Prediction, Wisconsin
-#| echo: false
-#| message: false
-#| warning: false
-
-plot(roc_obj_Wisconsin)
-```
-
-```{r}
-#| label: fig-nev
-#| fig-cap: ROC Curve for Harris Win Prediction, Nevada
-#| echo: false
-#| message: false
-#| warning: false
-
-plot(roc_obj_Nevada)
-```
-
-```{r}
-#| label: fig-log
-#| fig-cap: ROC Curve for Popular Vote Prediction
-#| echo: false
-#| message: false
-#| warning: false
-
-plot(roc_obj)
-```
-
-```{r}
-#| label: fig-logadj
-#| fig-cap: ROC Curve for Popular Vote Prediction, Adjusted
-#| echo: false
-#| message: false
-#| warning: false
-
-plot(roc_obj)
-```
-
-\FloatBarrier
-
-## Coefficients
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-# Tidy the logistic regression model
-tidy_Pennsylvania <- tidy(logistic_Pennsylvania)
-
-# Display the table using knitr::kable
-kable(tidy_Pennsylvania,
-  digits = 2,
-  col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
-  caption = "Logistic Regression Coefficients for Pennsylvania"
-)
-```
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-# Tidy the logistic regression model
-tidy_Georgia <- tidy(logistic_Georgia)
-
-# Display the table using knitr::kable
-kable(tidy_Georgia,
-  digits = 2,
-  col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
-  caption = "Logistic Regression Coefficients for Georgia"
-)
-```
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-# Tidy the logistic regression model
-tidy_Michigan <- tidy(logistic_Michigan)
-
-# Display the table using knitr::kable
-kable(tidy_Michigan,
-  digits = 2,
-  col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
-  caption = "Logistic Regression Coefficients for Michigan"
-)
-```
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-# Tidy the logistic regression model
-tidy_North_Carolina <- tidy(logistic_North_Carolina)
-
-# Display the table using knitr::kable
-kable(tidy_North_Carolina,
-  digits = 2,
-  col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
-  caption = "Logistic Regression Coefficients for North_Carolina"
-)
-```
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-# Tidy the logistic regression model
-tidy_Arizona <- tidy(logistic_Arizona)
-
-# Display the table using knitr::kable
-kable(tidy_Arizona,
-  digits = 2,
-  col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
-  caption = "Logistic Regression Coefficients for Arizona"
-)
-```
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-# Tidy the logistic regression model
-tidy_Wisconsin <- tidy(logistic_Wisconsin)
-
-# Display the table using knitr::kable
-kable(tidy_Wisconsin,
-  digits = 2,
-  col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
-  caption = "Logistic Regression Coefficients for Wisconsin"
-)
-```
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-# Tidy the logistic regression model
-tidy_Nevada <- tidy(logistic_Nevada)
-
-# Display the table using knitr::kable
-kable(tidy_Nevada,
-  digits = 2,
-  col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
-  caption = "Logistic Regression Coefficients for Nevada"
-)
-```
-
 \newpage

### 2024-12-04 paper/paper.qmd
udpated paper

@@
 ## Measurement
+
+The CFPS records survey data by directly sending agents to the homes of respondents, aiding respondents in the process of filling out a comprehensive survey about their families and themselves [@cfps].
+The agents closely interact with the respondents as they complete the survey, ensuring that the recorded information is complete and appropriate.
+For example, the agent may require the respondent to input an answer for certain questions, even if the initial response of the respondent is "I don't know".
+Moreover, the majority of recorded variables in the CFPS surveys are categorical, and they may have ambiguous boundaries.
+
+The direct interactions between respondents and agents may effectively maximize the rate of completion of CFPS surveys, but the forced responses might not accurately reflect the true opinions of the respondents, and the fact that an agent directly observes respondents as they fill our the survey may encourage them to conceal information or select answer choices that are considered ordinary.
+
+Therefore, while the methods of measurement ensures a high level of professionalism and completion, the responses may be biased.
+This negatively impacts the dataset's capacity to reflect socioeconomic phenomenon in the real world, including the economic returns to education.
 

### 2024-12-04 paper/paper.qmd
used styler

@@
 names(models) <- tools::file_path_sans_ext(basename(model_files))
-
 ```
@@
   `Q3vsQ4` = c(2.2804, 3.7010, 3.1417, 3.1945, 4.4302, 2.1920, 3.1566),
-  `Cross Sectional Mean` = c(2.2833, 2.5673, 2.5001, 0.6623, 2.2413, 3.0872, ' ')
+  `Cross Sectional Mean` = c(2.2833, 2.5673, 2.5001, 0.6623, 2.2413, 3.0872, " ")
 )
@@
   `CFPS Year` = c(2020, 2018, 2016, 2014, 2012, 2010),
-  `Q1 Returns` = c('4.9507***', '4.1730**', '2.5671*', '4.4464**', '-1.0031', '0.1803'),
-  `Q2 Returns` = c('5.8130***', '4.0239***', '3.0501***', '2.5357**', '0.0590', '1.1116'),
-  `Q3 Returns` = c('7.3284***', '6.1466***', '4.1665***', '2.8027***', '0.4928', '3.9577***'),
-  `Q4 Returns` = c('10.3891***', '9.1724***', '6.9051***', '6.3410***', '4.4870***', '8.0710***')
+  `Q1 Returns` = c("4.9507***", "4.1730**", "2.5671*", "4.4464**", "-1.0031", "0.1803"),
+  `Q2 Returns` = c("5.8130***", "4.0239***", "3.0501***", "2.5357**", "0.0590", "1.1116"),
+  `Q3 Returns` = c("7.3284***", "6.1466***", "4.1665***", "2.8027***", "0.4928", "3.9577***"),
+  `Q4 Returns` = c("10.3891***", "9.1724***", "6.9051***", "6.3410***", "4.4870***", "8.0710***")
 )

### 2024-12-04 scripts/00-simulate_data.R

@@ -70,4 +70,3 @@ simulated_data <- data.frame(
 
 #### Write_csv ####
 write_csv(simulated_data, file = "data/00-simulated_data/simulated_data.csv")
-

### 2024-12-04 scripts/01-test_simulated_data.R

@@ -39,16 +39,16 @@ test_that("Simulated Dataset has all required columns with correct types", {
     "is_east"
   )
   expect_true(all(required_cols %in% colnames(dataset)))
-  
+
   # Check data types
-  expect_type(dataset$yearly_income, "double")  # Numeric
-  expect_type(dataset$years_of_education, "double") 
-  expect_type(dataset$years_of_work, "double") 
-  expect_type(dataset$gender, "double") 
-  expect_type(dataset$city_hukou, "double") 
-  expect_type(dataset$is_party, "double") 
-  expect_type(dataset$is_married, "double") 
-  expect_type(dataset$is_east, "double") 
+  expect_type(dataset$yearly_income, "double") # Numeric
+  expect_type(dataset$years_of_education, "double")
+  expect_type(dataset$years_of_work, "double")
+  expect_type(dataset$gender, "double")
+  expect_type(dataset$city_hukou, "double")
+  expect_type(dataset$is_party, "double")
+  expect_type(dataset$is_married, "double")
+  expect_type(dataset$is_east, "double")
 })
 
 
@@ -56,7 +56,7 @@ test_that("Simulated Dataset has all required columns with correct types", {
 
 test_that("yearly_income values are between 0 and 1,000,000 and multiples of 100", {
   expect_true(all(dataset$yearly_income >= 0 & dataset$yearly_income <= 1000000))
-  
+
   # Check if all values are multiples of 100
   expect_true(all(dataset$yearly_income %% 100 == 0))
 })
@@ -80,8 +80,9 @@ test_that("Binary variables contain only 0 or 1", {
 
 test_that("yearly_income has an average close to 50,000", {
   avg_income <- mean(dataset$yearly_income)
-  expect_true(avg_income >= 49000 & avg_income <= 51000, 
-              info = paste("Average income is", avg_income))
+  expect_true(avg_income >= 49000 & avg_income <= 51000,
+    info = paste("Average income is", avg_income)
+  )
 })
 
 test_that("years_of_education has a reasonable distribution", {

### 2024-12-04 scripts/02-clean_data.R

@@ -21,41 +21,65 @@ library(arrow)
 #### Read data ####
 # import raw datasets for all CFPS iterations
 # 2020 data
-cfps2020person_raw <- read_sas("data/01-raw_data/cfps2020person_202306.sas7bdat", 
-                               NULL)
-cfps2020famecon <- read_sas("data/01-raw_data/cfps2020famecon_202306.sas7bdat",
-                            NULL)
+cfps2020person_raw <- read_sas(
+  "data/01-raw_data/cfps2020person_202306.sas7bdat",
+  NULL
+)
+cfps2020famecon <- read_sas(
+  "data/01-raw_data/cfps2020famecon_202306.sas7bdat",
+  NULL
+)
 
 
 # 2018 data
-cfps2018person_raw <- read_sas("data/01-raw_data/cfps2018person_202012.sas7bdat", 
-                               NULL)
-cfps2018famecon <- read_sas("data/01-raw_data/cfps2018famecon_202101.sas7bdat",
-                            NULL)
+cfps2018person_raw <- read_sas(
+  "data/01-raw_data/cfps2018person_202012.sas7bdat",
+  NULL
+)
+cfps2018famecon <- read_sas(
+  "data/01-raw_data/cfps2018famecon_202101.sas7bdat",
+  NULL
+)
 
 # 2016 data
-cfps2016person_raw <- read_sas("data/01-raw_data/cfps2016adult_201906.sas7bdat", 
-                               NULL)
-cfps2016famecon <- read_sas("data/01-raw_data/cfps2016famecon_201807.sas7bdat",
-                            NULL)
+cfps2016person_raw <- read_sas(
+  "data/01-raw_data/cfps2016adult_201906.sas7bdat",
+  NULL
+)
+cfps2016famecon <- read_sas(
+  "data/01-raw_data/cfps2016famecon_201807.sas7bdat",
+  NULL
+)
 
 # 2014 data
-cfps2014person_raw <- read_sas("data/01-raw_data/cfps2014adult_201906.sas7bdat", 
-                               NULL)
-cfps2014famecon <- read_sas("data/01-raw_data/cfps2014famecon_201906.sas7bdat",
-                            NULL)
+cfps2014person_raw <- read_sas(
+  "data/01-raw_data/cfps2014adult_201906.sas7bdat",
+  NULL
+)
+cfps2014famecon <- read_sas(
+  "data/01-raw_data/cfps2014famecon_201906.sas7bdat",
+  NULL
+)
 
 # 2012 data
[…]

### 2024-12-04 scripts/03-test_analysis_data.R

@@ -80,7 +80,7 @@ run_sanity_checks <- function(data, dataset_name) {
     # income variable for analysis is measured in natural log, so
     # it can take negative values
     expect_true(all(data$ln_hourly_wage >= -999 & data$ln_hourly_wage <= 100))
-    
+
     # For the analysis datasets, there are no specific values to look for
     # because the data in some iterations of the survey just asks how many
     # years of education someone has received, while other iterations ask
@@ -89,18 +89,18 @@ run_sanity_checks <- function(data, dataset_name) {
     # and they should be whole numbers
     expect_true(all(data$years_of_education >= 0 & data$years_of_education <= 22))
     expect_true(all(data$years_of_education == as.integer(data$years_of_education)))
-    
+
     # Work years are whole numbers and not too large
     expect_true(all(data$pot_work_years <= 80))
     expect_true(all(data$pot_work_years == as.integer(data$pot_work_years)))
-    
+
     # Dummy variables should all be 0 or 1
     binary_vars <- c("gender", "city_hukou", "is_party", "is_married", "is_east")
     for (var in binary_vars) {
       expect_true(all(data[[var]] %in% c(0, 1)), info = paste("Checking values of", var))
     }
 
-    
+
     # Family income quartile variable should be whole numbers between 1 and 4
     expect_true(all(data$income_quartile >= 1 & data$income_quartile <= 4))
     expect_true(all(data$income_quartile == as.integer(data$income_quartile)))
@@ -119,4 +119,3 @@ for (dataset_name in names(datasets_list)) {
   dataset <- datasets_list[[dataset_name]]
   run_sanity_checks(dataset, dataset_name)
 }
-

### 2024-12-04 scripts/04-exploratory_data_analysis.R

@@ -382,5 +382,3 @@ ggplot(all_combined, aes(x = income_quartile)) +
     panel.grid.major = element_line(color = "gray80"), # Light gray major grid lines
     panel.grid.minor = element_blank() # Remove minor grid lines
   )
-
-

### 2024-12-04 scripts/05-model_data.R

@@ -58,16 +58,18 @@ quartile_4_2010 <- subset(data_2010, income_quartile == 4)
 
 #### 2020 Analysis ####
 # compare quartile 1 and 2
-quartile_1_2020$treatment = 1
-quartile_2_2020$treatment = 0
+quartile_1_2020$treatment <- 1
+quartile_2_2020$treatment <- 0
 
 quartile_1_2_compare_2020 <- rbind(quartile_1_2020, quartile_2_2020)
 
 # Perform propensity score matching
-m.out <- matchit(treatment ~ gender + pot_work_years 
-                 + city_hukou + is_married + is_party + is_east, 
-                 data = quartile_1_2_compare_2020, method = "nearest",
-                 distance = "logit", caliper = 0.1, ratio = 2)
+m.out <- matchit(
+  treatment ~ gender + pot_work_years
+    + city_hukou + is_married + is_party + is_east,
+  data = quartile_1_2_compare_2020, method = "nearest",
+  distance = "logit", caliper = 0.1, ratio = 2
+)
 
 # Check the matching result
 summary(m.out)
@@ -77,11 +79,11 @@ matched_data <- match.data(m.out)
 
 # using the Mincer Equation to fit both groups in the matched sample
 lm_fit_q1 <- lm(ln_hourly_wage ~ years_of_education + pot_work_years + exp2
-                + city_hukou + is_married + gender + is_east
-                + is_party, data = matched_data, subset = income_quartile == 1)
+  + city_hukou + is_married + gender + is_east
+  + is_party, data = matched_data, subset = income_quartile == 1)
 lm_fit_q2 <- lm(ln_hourly_wage ~ years_of_education + pot_work_years + exp2
-                + city_hukou + is_married + gender + is_east
-                + is_party, data = matched_data, subset = income_quartile == 2)
+  + city_hukou + is_married + gender + is_east
+  + is_party, data = matched_data, subset = income_quartile == 2)
 
 # Display the result
 summary(lm_fit_q1)
@@ -100,16 +102,18 @@ saveRDS(
 
 
 # quartile 1 vs quartile 3
-quartile_1_2020$treatment = 1
-quartile_3_2020$treatment = 0
+quartile_1_2020$treatment <- 1
+quartile_3_2020$treatment <- 0
 
 quartile_1_3_compare_2020 <- rbind(quartile_1_2020, quartile_3_2020)
 
 # Perform propensity score matching
-m.out2 <- matchit(treatment ~ gender + pot_work_years 
[…]

### 2024-12-15 paper/paper.qmd
Manually updated files
My git ran into a fatal error that I wasn't able to resolve. The documents were completed before the deadline.

@@
 thanks: "Code and data are available at: [https://github.com/YisuHou1/Educational_Returns_Analysis](https://github.com/YisuHou1/Educational_Returns_Analysis)."
-date: today
+date: December 14, 2024
 date-format: long
@@
 Using data from the China Family Panel Studies (CFPS) between 2010 and 2020, this paper analyzes how family income influences the financial benefits individuals gain from education.
-The analysis reveals that individuals from wealthier families consistently enjoy significantly higher income returns from education compared to their lower-income counterparts, though this gap did not widen over the decade studied.
+The analysis shows that individuals from wealthier families consistently enjoy significantly higher income returns from education compared to their lower-income counterparts, though this gap did not widen over the decade studied.
 These findings highlight persistent inequality in education's economic impact, emphasizing the need for policies that ensure education serves as a more effective equalizer in society."
@@
 This is an essential connection, as it signifies how effectively education translates into its ultimate outcome: income.
-The aim of this research is to fill this knowledge gap by examining whether individuals from different socioeconomic backgrounds in the Chinese population receive the same level of returns from education.
+The aim of this research is to complete this knowledge gap by examining whether individuals from different socioeconomic backgrounds in the Chinese population receive the same level of returns from education.
 
@@
 The agents closely interact with the respondents as they complete the survey, ensuring that the recorded information is complete and appropriate.
-For example, the agent may require the respondent to input an answer for certain questions, even if the initial response of the respondent is "I don't know".
+For example, the agent may require the respondent to input an answer for certain questions, even if the initial response of the respondent is "I don't know" [@cfps_questions].
 Moreover, the majority of recorded variables in the CFPS surveys are categorical, and they may have ambiguous boundaries.
 
-The direct interactions between respondents and agents may effectively maximize the rate of completion of CFPS surveys, but the forced responses might not accurately reflect the true opinions of the respondents, and the fact that an agent directly observes respondents as they fill our the survey may encourage them to conceal information or select answer choices that are considered ordinary.
+A portion of surveys were conducted through phone calls, utilizing the same procedure as physical interview sessions.
+All interviews were facilitated by computer assisted personal interviewing (CAPI) technology provided by the Survey Research Center (SRC) at the University of Michigan [@cfps_measure].
+This system helps the researchers design complex interviews tailored to different members of the household while reducing measurement error and monitoring the quality of interviews.
+
+In the case of young children considered incapable of completing full surveys, their parents provided responses for them [@cfps_questions].
+This naturally leads to biases, but it is not relevant to this analysis because only data on the working population was used.
+
+The direct interactions between respondents and agents may effectively maximize the rate of completion of CFPS surveys, but the forced responses might not accurately reflect the true opinions of the respondents, and the fact that an agent directly observes respondents as they fill out the survey may encourage them to conceal information or select answer choices that are considered ordinary.
+Disparities may be introduced by phone interviews, as phone calls have different dynamics than face-to-face interactions.
 
@@
     "text",
-    x = mean(all_combined$ln_hourly_wage, na.rm = TRUE) - 3, # Position text slightly to the right of the mean line
+    x = mean(all_combined$ln_hourly_wage, na.rm = TRUE) - 3,
     y = Inf, # Position text at the top of the plot
@@
     "text",
-    x = mean(all_combined$years_of_education, na.rm = TRUE) + 2.5, # Position text slightly to the right of the mean line
+    x = mean(all_combined$years_of_education, na.rm = TRUE) + 3, # Position text slightly to the right of the mean line
     y = Inf, # Position text at the top of the plot
@@
     "text",
-    x = mean(all_combined$pot_work_years, na.rm = TRUE) + 6, # Position text slightly to the right of the mean line
+    x = mean(all_combined$pot_work_years, na.rm = TRUE) + 8, # Position text slightly to the right of the mean line
     y = Inf, # Position text at the top of the plot
@@
   format = "latex"
-) %>%
+) |>
   kable_styling(
@@
 
-When directly regressing without matching, the significance of educational returns coefficients remained the same; the coefficients for Q1, Q2 and Q3 of CFPS2012 and the coefficients for Q1 and Q2 of CFPS2010 are the only ones insignificant at the 5% level.
+When directly regressing without matching, the significance of educational returns coefficients remained the same; as @tbl-robust shows, the coefficients for Q1, Q2 and Q3 of CFPS2012 and the coefficients for Q1 and Q2 of CFPS2010 are the only ones insignificant at the 5% level.
 It is uncertain why educational returns are insignificant for these family income quartiles, both in the matched data and the unmatched data.
@@
 This caused the data used in this research to include more individuals from higher quartiles, increasing bias.
+
 The second limitation is that the sample changed over time as individuals responded differently in different CFPS iterations.
@@
 Consequently, the sample sizes and the individuals making up the samples were different for each year, making the temporal analysis less conclusive.
+Moreover, the observation that educational returns for some income quartiles became negative or statistically insignificant in the 2012 dataset hints that there may be measurement changes across CFPS iterations.
+This is a logical speculation, as it's unlikely that educational returns of individuals in the same bracket changed so much over 2-year periods.
+This will be further explored in @sec-method in the Appendix.
+
 Finally, this research calculated returns to education using the Miner equation, which has a set of limitations.
 Besides the problem of linearity, it also assumes that all covariates influencing income are included in the model, which might not be the case.
-Additionally, the model only provides a general statement on the overall returns to education of different family income quartiles and does not provide insight to the reasons behind the differences.
+Additionally, the model only provides a general statement on the overall returns to education of different family income quartiles and does not provide information to the reasons behind the differences.
 
@@
 
-## Survey methodology overview and evaluation
+# Survey Methodology Overview and Evaluation {#sec-method}
 
-## Idealised methodology
+CFPS adopts a stratified, multistage probability-proportional-to-size (PPS) sampling approach to ensure national representativeness.
+The target sample consists of 16,000 households across 25 provinces and regions, effectively representing approximately 95% of China's population [@cfps_manual].
+Sampling is conducted in three stages: primary sampling units such as counties, second-stage sampling units such as villages and urban neighborhoods, and third-stage sampling units that are systematically selected households.
+
+As previously mentioned in the measurement section of @sec-data, the survey employs a series of detailed questionnaires tailored for different individuals, suited for various levels of analysis [@cfps_measure].
+These include: the Community Questionnaire which captures data on infrastructure, demographic trends, economy, and governance within sampled communities; the Household Screening Questionnaire that identifies eligible households and their basic characteristics; the Family Roster Questionnaire that maps relationships and collects demographic and occupational information for all household members, including individuals living apart; the Individual Questionnaires: Separate modules for adults and children, addressing education, health, income, employment, and family dynamics [@cfps_manual].
+
+As its name (China Family Panel Studies) suggests, CFPS follows a panel study structure, tracking all "gene members" (baseline individuals and their biological or adopted descendants) over multiple iterations, conducted bi-annually.
+Changes in family composition due to births, deaths, or household splits are carefully updated through family roster questionnaires in each wave [@cfps_manual].
+This longitudinal approach enables the study of dynamic processes such as migration, education, and inter-generational relationships.
+
+To ensure the quality of the data collected, CFPS adopts pre-field mapping, interviewer training, and data cross-verification [@cfps_manual].
+
+Due to its innovative and robust approach, CFPS established itself as the most prominent academic data source for longitudinal social science studies.
+However, there still exists multiple aspects of imperfection other than those discussed in the main paper.
+
+First, the CFPS excludes certain regions of China due to logistical constraints, such as Xinjiang, Tibet, Inner Mongolia, and Hainan, which limits its national representativeness.
+These regions have unique cultural, economic, and social dynamics that are underrepresented in the dataset [@cfps_manual].
+
+Second, following "gene members" over multiple waves presents unique challenges.
+Migrant populations, in particular, are difficult to track, and while CATI (Computer-Assisted Telephone Interviewing) helps, migration still led to non-response or partial data collection in subsequent waves, affecting longitudinal data integrity.
+
+Third, the detailed nature of the questionnaires, especially in later waves, makes it impossible for respondents to complete them in a short sitting.
+This increases the likelihood of respondent fatigue, leading to incomplete or hurried responses.
+A study found that an additional hour of survey time increases the probability that a respondent skips a question by 10%–64%, and the total monetary value of aggregated categories such as assets or expenditures declines as the survey proceeds [@JEONG2023102992].
+
+As I looked into the specific questionnaire documents, I found that all CFPS iterations collect data on family-related variables much before personal data [@cfps_questions_2012; @cfps_questions].
+This may explain the disparities between the early 2010 and 2012 data and other iterations.
+Early iterations of CFPS do not record individuals' personal income as a single variable; income is recorded as a sub-component of the different jobs an individual worked [@cfps_questions_2012], and I calculated total personal income from summing the individual values of each job for the purpose of this study.
+Given that data on jobs were recorded in later stages of the questionnaire, there may be systematic under-reporting of job income due to respondent fatigue.
+I suspect that the disparities in measurement (having personal income variable in some CFPS iterations and not having it in others), in combination with respondent fatigue, caused the changes in measured educational returns throughout the studied decade.
 
